### 2019-09-23 manuscript.Rmd
initial analyses

---
title: "Open Peer Review"
author: "Daniel Lakens"
date: "22-9-2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Accessing Open Peer Reviews

PeerJ assigns all articles a number from 1, increasing consequtively with each published manuscript. Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article). Using text-mining tools in R (cite R, RCurl, XML, stringer) we downloaded all reviews and stored them as individual text files.

The database created from PeerJ uses reviews published from 21 February 2012 till
18 March 2019. These reviews come from 11 different scientific sections and contain a total
of 6800 articles. The reviews of PeerJ are structured differently from The Royal Society and
do not contain individual recommendations of the reviewers. Instead the recommendation of
the academic editor is displayed on the different versions of the manuscript. PeerJ does
publicize all the different versions of the submitted manuscripts opposed to The Royal
Society which only publishes the final accepted manuscript. The reviews of PeerJ do not
contain a set of standard questions, but use 4 different topic on which the reviewers are asked
to comment. These topics are; basic reporting, experimental design, validity of the findings
and comments for the author. The guidelines on which topic has to contain which information
seems not to be strictly defined and it is mainly up to the decision of the reviewer what
information to put in which section. Basic reporting and comments for the author sections
commonly contain the majority of the peer review. In some cases the reviewers refer to
attached documents that assumably were included in the correspondence, but these
documents are not publicized along the reviews. In these cases the data will be regarded
missing in the database.

### 2019-09-23 Corrupted.R

@@ -1,0 +1,48 @@
+library(pdftools)
+library(tm)
+library(stringr)
+
+article_id <- vector()
+article_id_os_open <- vector()
+fix_doc <- vector()
+
+path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\TRS_Open_Biology_id.txt"
+
+conn <- file(path,open="r")
+article_id <- readLines(conn)
+close(conn)
+
+for (r in 1:length(article_id)){
+  article_id[r] <- gsub("10.1098/rsob.", "", article_id[r])
+  fix_doc[1] <- "nope"
+  review_id <- article_id[r]
+  document <- NULL
+
+  path <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", review_id, ".pdf", sep="")  #used for open biology
+  #path <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Science\\review", review_id, ".pdf", sep="") #used for open science
+
+  if (file.exists(path)){
+    open_file <- file(path,open="r")
+    try(read <- readPDF(control = list(text = "-layout")))
+    try(document <- Corpus(URISource(path), readerControl = list(reader = read)))
+    try(fix_doc <- content(document[[1]])) #this fails when if the file is corrupted resulting in the first item on the fix_doc list remaining "nope"
+    
+    if (fix_doc[1] != "nope") {
+      article_id_os_open <- append(article_id_os_open, article_id[r])
+    }
+    
+    close(open_file)
+  }
+}
+
+final_txt_file <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OB_pdf_list.txt" #used for open biology
+#final_txt_file <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OS_pdf_list.txt" #used for open science
+
+#######################Storing the new list of not corrupted pdf files###########################
+sink(final_txt_file)
+for (i in 1:length(article_id_os_open)){
+  cat(article_id_os_open[i])
+  cat("\n")
+}
+sink()
+

### 2019-09-23 PeerJ code.R

@@ -1,0 +1,187 @@
+#install.packages("RCurl")
+#install.packages("XML")
+#install.packages(rvest)
+
+# load packages
+library(RCurl)
+library(XML)
+library(stringr)
+library(here)
+
+here("peerj_text_files")
+
+for (r in 1:7223){ #Uses the reviews 1 to 7240 from PeerJ
+  
+  review_id <- r
+  
+  # download html
+  html <- getURL(paste("https://peerj.com/articles/", review_id, "/reviews/", sep=""), followlocation = TRUE)
+  
+  #parse html
+  PeerJdoc = htmlParse(html, asText=TRUE)
+  plain.text <- xpathSApply(PeerJdoc, "//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)][not(ancestor::form)]", xmlValue)
+  
+  ############################Text cleaning##########################################
+  peerdoc <- paste(plain.text, collapse = "  ")
+  peerdoc <- strsplit(peerdoc, "\n\n")
+  peerdoc <- unlist(peerdoc)
+  peerdoc <- trimws(peerdoc)
+  peerdoc <- str_trim(peerdoc)
+  peerdoc <- gsub("?", "", peerdoc)
+  peerdoc <- gsub("\n", "", peerdoc)
+  peerdoc <- gsub("\t", "", peerdoc)
+  peerdoc <- gsub("\t\t", "", peerdoc)
+  peerdoc <- gsub("\\s+", " ", peerdoc)
+  peerdoc <- peerdoc[peerdoc != ""]
+  
+  ##############################Labeling section#####################################
+  #in this section labels get added to the txt files to mark the locations at which important information is contained
+  
+  version_count <- 1
+  author_count <- 1
+  x = length(peerdoc)     #for the while loop
+  y = 1                   #for the while loop
+  
+  while (y<x){
+    if((str_sub(peerdoc[y], 1, 10) == "Version 0.")){
+      peerdoc <- append(peerdoc, paste("label_version_", version_count , sep=""), after= y - 1)
+      peerdoc <- append(peerdoc, paste("label_recommendation_", version_count, sep="" ), after=y+4)
+      version_count = version_count +1
+      x=x+1
+      y=y+1
+    }
+    if(peerdoc[y] == "Basic reporting"){
+      peerdoc <- append(peerdoc, paste("label_br_", author_count, sep="" ), after=y)
+      peerdoc <- append(peerdoc, paste("label_author_", author_count , sep=""), after= y - 3)
[…]

### 2019-09-23 Report_code.R

@@ -1,0 +1,442 @@
+# install.packages("data.table")
+# install.packages("dplyr")
+# install.packages("formattable")
+# install.packages("tidyr")
+# install.packages("ggplot2")
+
+library(data.table)
+library(dplyr)
+library(formattable)
+library(tidyr)
+library(ggplot2)
+
+options(max.print=9999999)
+
+TRS_data <- read.csv(file = "E:\\Deze folder\\BEP Open Peer Review\\TRS_Dataset.csv")
+#print(TRS_data)
+
+PeerJ_data <- read.csv(file = "E:\\Deze folder\\BEP Open Peer Review\\PeerJ_Dataset.csv")
+#print(PeerJ_data)
+
+###################Variables table###################
+varlist <- c("Link", "Section", "Days", "Version", "Recommendation", "Word count", "Masked", "Positive", "Negative")
+varlist2 <- c("The url of the review","Which journal/field of study the review belongs to", "The time between submitting the initial manuscript and publication in days", "The version for which the review is written", "The recommendation that is given by either the editor(PeerJ) or the reviewer(TRS)", "The amount of words that the review contains", "If the reviewer has signed the review or not", "The amount of positive words per 1000 words", "The amount of negative words per 1000 words")
+df_plot <- data.frame(varlist, varlist2)
+names(df_plot)[names(df_plot) == "varlist"] <- "Variable"
+names(df_plot)[names(df_plot) == "varlist2"] <- "Description"
+formattable(df_plot, align = c("l", rep("l", NCOL(df_plot))), size = 14)
+
+mean(PeerJ_data$df_days, na.rm = TRUE)
+t.test(PeerJ_data$df_days, TRS_data$df_days)
+
+#####How many articles are accepted without the version being reviewed PeerJ#####
+v <- 0 
+for (i in 1:length(PeerJ_data$X)){
+  if ((PeerJ_data$df_version[i] == 1)&(is.na(PeerJ_data$df_version[i])==FALSE)){
+    if (PeerJ_data$df_link[i]!= PeerJ_data$df_link[i-1]){
+    v = v + 1
+    }
+  }
+}
+print(v)
+
[…]

### 2019-09-23 RoyalSociety code.R

@@ -1,0 +1,106 @@
+#install.packages("pdftools")
+#install.packages("stringr")
+#install.packages("tm")
+
+library(pdftools)
+library(stringr)
+library(tm)
+
+#########################list of article id's#####################################
+article_id <- vector()
+
+#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\Article_ID_OB.txt" #used for downloading the pdf's from open biology (list with the open biology ID's)
+#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
+path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OB_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open biology are contained
+#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OS_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open science are contained
+
+conn <- file(path,open="r")
+article_id <- readLines(conn)
+close(conn)
+
+########################downloading the pdf's#####################################
+##this section is used for downloading the pdf files.
+# sleep <- function() { Sys.sleep(20) } #needed to prevent an IP block from the royal society website
+# 
+#  for (i in 1:length(article_id)) {
+#    sleep()
+#    article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
+#    #article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
+#    
+#    url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="")
+#    destfile1 <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", article_id[i], ".pdf", sep="")
+#    download.file(url, destfile=destfile1 , mode="wb")
+#    }
+
+########################Reading pdf file #########################################
+for (i in 1:length(article_id)) {
+  pdf_file <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", article_id[i], ".pdf", sep="") #map with open biology pdf's
[…]

### 2019-09-23 TM_PeerJ - Copy.R

@@ -1,0 +1,310 @@
+###Notes###
+#install.packages("tidytext")
+#install.packages("dplyr")
+#install.packages("stringr")
+#install.packages("textdata") #for sentiment analysis
+
+library(dplyr)
+library(tidytext)
+library(pdftools)
+library(tm)
+library(stringr)
+library(here)
+
+setwd("C:/Users/Daniel/surfdrive/R/open_peer_review/peerj_reviews_txt")
+here()
+#########################################Getting the lexicons######################################################
+nrc_negative <- vector()
+nrc_positive <- vector()
+
+nrc <- get_sentiments("nrc") 
+
+for (i in 1:length(nrc$sentiment)){
+  if (nrc$sentiment[i] == "negative")
+    nrc_negative <- append(nrc_negative, nrc$word[i])
+}
+for (i in 1:length(nrc$sentiment)){
+  if (nrc$sentiment[i] == "positive")
+    nrc_positive <- append(nrc_positive, nrc$word[i])
+}
+
+#########################################variables used to create the dataframe#################################
+df_link <- c()
+df_section <- c()
+df_days <- c()
+df_version <- c()
+df_recommendation <- c()
+df_word_count <- c()
+df_masked <- c()
+df_positive <- c()
+df_negative <- c()
+df_id <- c()
+open_reviews <- 0
+closed_reviews <- 0
+total_version <- 0
+
+r <- 1
+#########################################read txt file##########################################################
+for (r in 1:10){ #starting the loop to create the dataframe from the 6800 PeerJ articles
+  
+  review_id <- r
+  
+  path <- paste(review_id,".txt", sep="")
+  
+  open_file <- file(path, open = "r")
+  lines <- readLines(open_file)
+  lines <- trimws(lines)
+  close(open_file)
+  
+  a <- length(lines)
+  if (lines[a] != "not_open_acces"){ #If the last line of the file is "not_open_acces" it means: The author has chosen not to publish the full peer review history of this article.
+    open_reviews = open_reviews + 1 #If reviews are open, add 1 to counter.
+    
+    ######variables######
+    
+    ###############################################Link############################################################
+    
+    link <- "" #reset link
+    link <- paste("https://peerj.com/articles/", review_id, "/reviews/", sep="") 
+    
+    ###############################Word count, positive and negative###############################################
+    
+    word_count <- vector()  #Vector that contains the wordcounts
[…]

### 2019-09-23 TM_PeerJ.R

@@ -1,0 +1,310 @@
+###Notes###
+#install.packages("tidytext")
+#install.packages("dplyr")
+#install.packages("stringr")
+#install.packages("textdata") #for sentiment analysis
+
+library(dplyr)
+library(tidytext)
+library(pdftools)
+library(tm)
+library(stringr)
+library(here)
+
+setwd("C:/Users/Daniel/surfdrive/R/open_peer_review/peerj_reviews_txt")
+here()
+#########################################Getting the lexicons######################################################
+nrc_negative <- vector()
+nrc_positive <- vector()
+
+nrc <- get_sentiments("nrc")
+
+for (i in 1:length(nrc$sentiment)){
+  if (nrc$sentiment[i] == "negative")
+    nrc_negative <- append(nrc_negative, nrc$word[i])
+}
+for (i in 1:length(nrc$sentiment)){
+  if (nrc$sentiment[i] == "positive")
+    nrc_positive <- append(nrc_positive, nrc$word[i])
+}
+
+#########################################variables used to create the dataframe#################################
+df_link <- c()
+df_section <- c()
+df_days <- c()
+df_version <- c()
+df_recommendation <- c()
+df_word_count <- c()
+df_masked <- c()
+df_positive <- c()
+df_negative <- c()
+df_id <- c()
+open_reviews <- 0
+closed_reviews <- 0
+total_version <- 0
+
+
+#########################################read txt file##########################################################
+for (r in 1:1){ #starting the loop to create the dataframe from the 6800 PeerJ articles
+  
+  review_id <- r
+  
+  path <- paste(review_id,".txt", sep="")
+  
+  open_file <- file(path, open = "r")
+  lines <- readLines(open_file)
+  lines <- trimws(lines)
+  close(open_file)
+  
+  a <- length(lines)
+  if (lines[a] != "not_open_acces"){ #If the last line of the file is "not_open_acces" it means: The author has chosen not to publish the full peer review history of this article.
+    open_reviews = open_reviews + 1 #If reviews are open, add 1 to counter.
+    
+    ######variables######
+    
+    ###############################################Link############################################################
+    
+    link <- "" #reset link
+    link <- paste("https://peerj.com/articles/", review_id, "/reviews/", sep="") 
+    
+    ###############################Word count, positive and negative###############################################
+    
+    word_count <- vector()  #Vector that contains the wordcounts
[…]

### 2019-09-23 TM_RoyalSociety.R

@@ -1,0 +1,237 @@
+###Notes###
+library(dplyr)
+library(tidytext)
+library(tm)
+library(stringr)
+options(max.print=9999999) #allows the console to output more lines
+
+#########################################Getting the lexicons######################################################
+nrc_negative <- vector()
+nrc_positive <- vector()
+
+nrc <- get_sentiments("nrc") 
+
+for (i in 1:length(nrc$sentiment)){
+  if (nrc$sentiment[i] == "negative")
+    nrc_negative <- append(nrc_negative, nrc$word[i])
+}
+for (i in 1:length(nrc$sentiment)){
+  if (nrc$sentiment[i] == "positive")
+    nrc_positive <- append(nrc_positive, nrc$word[i])
+}
+
+#########################################variables used to create the dataframe#################################
+df_link <- c()
+df_section <- c()
+df_days <- c()
+df_version <- c()
+df_recommendation <- c()
+df_word_count <- c()
+df_masked <- c()
+df_positive <- c()
+df_negative <- c()
+df_id <- c()
+
+#########################################Read txt id##############################################################
+article_id <- vector()
+
+path <- "E:\\Deze folder\\BEP Open Peer Review\\OB_pdf_list.txt"  #the list of non corrupted Open Biology ID's 
+#path <- "E:\\Deze folder\\BEP Open Peer Review\\OS_pdf_list.txt" #the list of non corrupted Open Science ID's 
+
+conn <- file(path,open="r")
+article_id <- readLines(conn)
+close(conn)
+
+
+###########################################Read txt file##########################################################
+for (r in 1:length(article_id)){
+  
+  review_id <- article_id[r]
+
+  path <- paste("E:\\Deze folder\\\\BEP Open Peer Review\\TXT_Files\\TRS\\Open Biology\\Review", review_id, ".txt", sep="") #used for Open Biology
+  #path <- paste("E:\\Deze folder\\\\BEP Open Peer Review\\TXT_Files\\TRS\\Open Science\\Review", review_id, ".txt", sep="") #used for Open Science
+  
+  if (file.exists(path)){
+  open_file <- file(path,open="r")
+  lines <- readLines(open_file)
+  lines <- trimws(lines)
+  
+  close(open_file)
+
+                                           ######variables######
+
+###########################Masked, Version, recommendation, days and word count###################################
+    
+    recommendation <- vector()
+    recommendation_count <- 1
+    masked <- vector()
+    author_count <- 1
+    version <- vector()
[…]

### 2019-09-25 manuscript.Rmd
update code, gitignore - RSOS df does not have all versions

@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library(data.table)
+library(dplyr)
+library(formattable)
+library(tidyr)
+library(ggplot2)
+library(here)
+
+here::here()
+
 ```
@@
 
-The database created from PeerJ uses reviews published from 21 February 2012 till
-18 March 2019. These reviews come from 11 different scientific sections and contain a total
-of 6800 articles. The reviews of PeerJ are structured differently from The Royal Society and
-do not contain individual recommendations of the reviewers. Instead the recommendation of
-the academic editor is displayed on the different versions of the manuscript. PeerJ does
-publicize all the different versions of the submitted manuscripts opposed to The Royal
-Society which only publishes the final accepted manuscript. The reviews of PeerJ do not
-contain a set of standard questions, but use 4 different topic on which the reviewers are asked
-to comment. These topics are; basic reporting, experimental design, validity of the findings
-and comments for the author. The guidelines on which topic has to contain which information
-seems not to be strictly defined and it is mainly up to the decision of the reviewer what
-information to put in which section. Basic reporting and comments for the author sections
-commonly contain the majority of the peer review. In some cases the reviewers refer to
-attached documents that assumably were included in the correspondence, but these
-documents are not publicized along the reviews. In these cases the data will be regarded
-missing in the database.
+```{r}
+# Read open science and open biology rds datafiles
+TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
+TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
+
+# Combine both datasets into one.
+TRS_data <- rbind(TRS_data_os, TRS_data_ob)
+
+PeerJ_data <- readRDS(file = "peerj_data.rds")
+
+TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]
+
+```
+
+Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
+What does this mean?

### 2019-09-25 Report_code.R

@@ -1,9 +1,3 @@
-# install.packages("data.table")
-# install.packages("dplyr")
-# install.packages("formattable")
-# install.packages("tidyr")
-# install.packages("ggplot2")
-
 library(data.table)
 library(dplyr)
 library(formattable)
@@ -12,10 +6,14 @@ library(ggplot2)
 
 options(max.print=9999999)
 
-TRS_data <- read.csv(file = "E:\\Deze folder\\BEP Open Peer Review\\TRS_Dataset.csv")
-#print(TRS_data)
+# Read open science and open biology rds datafiles
+TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
+TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
 
-PeerJ_data <- read.csv(file = "E:\\Deze folder\\BEP Open Peer Review\\PeerJ_Dataset.csv")
+# Combine both datasets into one.
+TRS_data <- rbind(TRS_data_os, TRS_data_ob)
+
+PeerJ_data <- readRDS(file = "peerj_data.rds")
 #print(PeerJ_data)
 
 ###################Variables table###################
@@ -42,9 +40,9 @@ print(v)
 
 #####How many articles are accepted without the version being reviewed TRS#####
 v <- 0 
-for (i in 1:(length(TRS_data$X)-1)){
-  if ((TRS_data$df_version[i] == 1)&(is.na(TRS_data$df_version[i])==FALSE)){
-    if (TRS_data$df_link[i]!= TRS_data$df_link[i+1]){
+for (i in 1:(length(TRS_data$df_link) - 1)) {
+  if ((TRS_data$df_version[i] == 1) & (is.na(TRS_data$df_version[i]) == FALSE)) {
+    if (TRS_data$df_link[i] != TRS_data$df_link[i + 1]) {
       v = v + 1
     }
   }
@@ -61,8 +59,8 @@ v_mean_v_5 <- vector()
 v_250days <- c(1:250)
 v_250days_5 <- seq(from = 2.5, to = 252.5, by = 5)
 
-for (i in 1:length(PeerJ_data$X)) {
-  if ((PeerJ_data$df_link[i] != PeerJ_data$df_link[i+1])&(is.na(PeerJ_data$df_version[i])==FALSE)&(is.na(PeerJ_data$df_days[i]) == FALSE)){
+for (i in 1:length(PeerJ_data$df_link)-1) {
[…]

### 2019-09-25 TM_PeerJ.R

@@ -1,310 +1,0 @@
-###Notes###
-#install.packages("tidytext")
-#install.packages("dplyr")
-#install.packages("stringr")
-#install.packages("textdata") #for sentiment analysis
-
-library(dplyr)
-library(tidytext)
-library(pdftools)
-library(tm)
-library(stringr)
-library(here)
-
-setwd("C:/Users/Daniel/surfdrive/R/open_peer_review/peerj_reviews_txt")
-here()
-#########################################Getting the lexicons######################################################
-nrc_negative <- vector()
-nrc_positive <- vector()
-
-nrc <- get_sentiments("nrc")
-
-for (i in 1:length(nrc$sentiment)){
-  if (nrc$sentiment[i] == "negative")
-    nrc_negative <- append(nrc_negative, nrc$word[i])
-}
-for (i in 1:length(nrc$sentiment)){
-  if (nrc$sentiment[i] == "positive")
-    nrc_positive <- append(nrc_positive, nrc$word[i])
-}
-
-#########################################variables used to create the dataframe#################################
-df_link <- c()
-df_section <- c()
-df_days <- c()
-df_version <- c()
-df_recommendation <- c()
-df_word_count <- c()
-df_masked <- c()
-df_positive <- c()
-df_negative <- c()
-df_id <- c()
-open_reviews <- 0
-closed_reviews <- 0
-total_version <- 0
-
-
-#########################################read txt file##########################################################
-for (r in 1:1){ #starting the loop to create the dataframe from the 6800 PeerJ articles
-  
-  review_id <- r
-  
-  path <- paste(review_id,".txt", sep="")
-  
-  open_file <- file(path, open = "r")
-  lines <- readLines(open_file)
-  lines <- trimws(lines)
-  close(open_file)
-  
-  a <- length(lines)
-  if (lines[a] != "not_open_acces"){ #If the last line of the file is "not_open_acces" it means: The author has chosen not to publish the full peer review history of this article.
-    open_reviews = open_reviews + 1 #If reviews are open, add 1 to counter.
-    
-    ######variables######
-    
-    ###############################################Link############################################################
-    
-    link <- "" #reset link
-    link <- paste("https://peerj.com/articles/", review_id, "/reviews/", sep="") 
-    
-    ###############################Word count, positive and negative###############################################
-    
-    word_count <- vector()  #Vector that contains the wordcounts
[…]

### 2019-09-25 check_open_review_royal_society.R

@@ -1,12 +1,17 @@
 library(pdftools)
 library(tm)
 library(stringr)
+library(here)
 
+here::here()
+
+#set up empty variables
 article_id <- vector()
 article_id_os_open <- vector()
 fix_doc <- vector()
 
-path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\TRS_Open_Biology_id.txt"
+#define path to 
+path <- "royal_society_pdf_files/Article_ID_OB.txt"
 
 conn <- file(path,open="r")
 article_id <- readLines(conn)
@@ -18,8 +23,8 @@ for (r in 1:length(article_id)){
   review_id <- article_id[r]
   document <- NULL
 
-  path <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", review_id, ".pdf", sep="")  #used for open biology
-  #path <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Science\\review", review_id, ".pdf", sep="") #used for open science
+  path <- paste("royal_society_pdf_files\\open_biology\\review", review_id, ".pdf", sep="")  #used for open biology
+  #path <- paste("royal_society_pdf_files\open_science\\review", review_id, ".pdf", sep="") #used for open science
 
   if (file.exists(path)){
     open_file <- file(path,open="r")
@@ -35,8 +40,8 @@ for (r in 1:length(article_id)){
   }
 }
 
-final_txt_file <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OB_pdf_list.txt" #used for open biology
-#final_txt_file <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OS_pdf_list.txt" #used for open science
+final_txt_file <- "royal_society_pdf_files\OB_pdf_list.txt" #used for open biology
+#final_txt_file <- "royal_society_pdf_files\open_biology\OS_pdf_list.txt" #used for open science
 
 #######################Storing the new list of not corrupted pdf files###########################
 sink(final_txt_file)

### 2019-09-25 peerj_download_reviews_create_text.R

@@ -1,16 +1,12 @@
-#install.packages("RCurl")
-#install.packages("XML")
-#install.packages(rvest)
-
 # load packages
 library(RCurl)
 library(XML)
 library(stringr)
 library(here)
 
-here("peerj_text_files")
+here()
 
-for (r in 1:7223){ #Uses the reviews 1 to 7240 from PeerJ
+for (r in 1:7223){ #Uses the reviews 1 to 7233 from PeerJ
   
   review_id <- r
   

### 2019-09-25 royal_society_open_biology_create_txt.R

@@ -1,0 +1,106 @@
+#install.packages("pdftools")
+#install.packages("stringr")
+#install.packages("tm")
+
+library(pdftools)
+library(stringr)
+library(tm)
+
+#########################list of article id's#####################################
+article_id <- vector()
+
+#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open biology (list with the open biology ID's)
+#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
+path <- "royal_society_pdf_files/OB_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open biology are contained
+#path <- "royal_society_pdf_files/OS_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open science are contained
+
+conn <- file(path,open="r")
+article_id <- readLines(conn)
+close(conn)
+
+########################downloading the pdf's#####################################
+##this section is used for downloading the pdf files.
+# sleep <- function() { Sys.sleep(20) } #needed to prevent an IP block from the royal society website
+# 
+#  for (i in 1:length(article_id)) {
+#    sleep()
+#    article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
+#    #article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
+#    
+#    url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="")
+#    destfile1 <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", article_id[i], ".pdf", sep="")
+#    download.file(url, destfile=destfile1 , mode="wb")
+#    }
+
+########################Reading pdf file #########################################
+for (i in 1:length(article_id)) {
+  pdf_file <- paste("royal_society_pdf_files/open_biology/review", article_id[i], ".pdf", sep="") #map with open biology pdf's
+  #pdf_file <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Science\\review", article_id[i], ".pdf", sep="") #map with open science pdf's
+  
+  if (file.exists(pdf_file)){
+  read <- readPDF(control = list(text = "-layout"))
[…]

### 2019-09-25 royal_society_open_science_create_txt.R

@@ -9,10 +9,10 @@ library(tm)
 #########################list of article id's#####################################
 article_id <- vector()
 
-#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\Article_ID_OB.txt" #used for downloading the pdf's from open biology (list with the open biology ID's)
-#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
-path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OB_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open biology are contained
-#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\OS_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open science are contained
+#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open biology (list with the open biology ID's)
+#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
+#path <- "royal_society_pdf_files/OB_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open biology are contained
+path <- "royal_society_pdf_files/OS_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open science are contained
 
 conn <- file(path,open="r")
 article_id <- readLines(conn)
@@ -34,8 +34,7 @@ close(conn)
 
 ########################Reading pdf file #########################################
 for (i in 1:length(article_id)) {
-  pdf_file <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", article_id[i], ".pdf", sep="") #map with open biology pdf's
-  #pdf_file <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Science\\review", article_id[i], ".pdf", sep="") #map with open science pdf's
+  pdf_file <- paste("royal_society_pdf_files/open_science/review", article_id[i], ".pdf", sep="") #map with open science pdf's
   
   if (file.exists(pdf_file)){
   read <- readPDF(control = list(text = "-layout"))
@@ -58,7 +57,7 @@ for (i in 1:length(article_id)) {
   y <- 1
   
[…]

### 2019-09-25 textmining_open_biology.R

@@ -5,21 +5,6 @@ library(tm)
 library(stringr)
 options(max.print=9999999) #allows the console to output more lines
 
-#########################################Getting the lexicons######################################################
-nrc_negative <- vector()
-nrc_positive <- vector()
-
-nrc <- get_sentiments("nrc") 
-
-for (i in 1:length(nrc$sentiment)){
-  if (nrc$sentiment[i] == "negative")
-    nrc_negative <- append(nrc_negative, nrc$word[i])
-}
-for (i in 1:length(nrc$sentiment)){
-  if (nrc$sentiment[i] == "positive")
-    nrc_positive <- append(nrc_positive, nrc$word[i])
-}
-
 #########################################variables used to create the dataframe#################################
 df_link <- c()
 df_section <- c()
@@ -28,15 +13,14 @@ df_version <- c()
 df_recommendation <- c()
 df_word_count <- c()
 df_masked <- c()
-df_positive <- c()
-df_negative <- c()
+df_reviewer_name <- c()
+df_reviewer_number <- c()
 df_id <- c()
 
 #########################################Read txt id##############################################################
 article_id <- vector()
 
-path <- "E:\\Deze folder\\BEP Open Peer Review\\OB_pdf_list.txt"  #the list of non corrupted Open Biology ID's 
-#path <- "E:\\Deze folder\\BEP Open Peer Review\\OS_pdf_list.txt" #the list of non corrupted Open Science ID's 
+path <- "royal_society_pdf_files/OB_pdf_list.txt"  #the list of non corrupted Open Biology ID's 
 
 conn <- file(path,open="r")
 article_id <- readLines(conn)
@@ -48,7 +32,7 @@ for (r in 1:length(article_id)){
   
   review_id <- article_id[r]
 
-  path <- paste("E:\\Deze folder\\\\BEP Open Peer Review\\TXT_Files\\TRS\\Open Biology\\Review", review_id, ".txt", sep="") #used for Open Biology
+  path <- paste("royal_society_txt_files/open_biology/review", review_id, ".txt", sep="") #used for Open Biology
   #path <- paste("E:\\Deze folder\\\\BEP Open Peer Review\\TXT_Files\\TRS\\Open Science\\Review", review_id, ".txt", sep="") #used for Open Science
   
   if (file.exists(path)){
@@ -75,6 +59,8 @@ for (r in 1:length(article_id)){
     positive <- vector()
     negative <- vector()
     switch_link <- 1
+    reviewer_name <- vector() #store reviewer names
[…]

### 2019-09-25 textmining_open_science.R

@@ -1,0 +1,194 @@
+###Notes###
+library(dplyr)
+library(tidytext)
+library(tm)
+library(stringr)
+options(max.print=9999999) #allows the console to output more lines
+
+#########################################variables used to create the dataframe#################################
+df_link <- c()
+df_section <- c()
+df_days <- c()
+df_version <- c()
+df_recommendation <- c()
+df_word_count <- c()
+df_masked <- c()
+df_reviewer_name <- c()
+df_reviewer_number <- c()
+df_id <- c()
+
+#########################################Read txt id##############################################################
+article_id <- vector()
+
+path <- "royal_society_pdf_files/OS_pdf_list.txt"  #the list of non corrupted Open Science ID's 
+
+conn <- file(path,open="r")
+article_id <- readLines(conn)
+close(conn)
+
+###########################################Read txt file##########################################################
+for (r in 1:length(article_id)){
+  
+  review_id <- article_id[r]
+  
+  path <- paste("royal_society_txt_files/open_science/review", review_id, ".txt", sep="") #used for Open Science
+  
+  if (file.exists(path)){
+    open_file <- file(path,open="r")
+    lines <- readLines(open_file)
+    lines <- trimws(lines)
+    
+    close(open_file)
+    
+    ######variables######
+    
+    ###########################Masked, Version, recommendation, days and word count###################################
+    
+    recommendation <- vector()
+    recommendation_count <- 1
+    masked <- vector()
+    author_count <- 1
+    version <- vector()
+    version_count <- 1
+    version_count2 <- 0  # used to fix a problem when version_count goes higher than the actual versions of the manuscript
+    timelapse <- vector()
+    dates <- vector()
+    days <- 0
+    switch_link <- 1
+    reviewer_name <- vector() #store reviewer names
+    reviewer_number <- vector() #store reviewer number
+    
+    word_count <- vector()  #Vector that contains the wordcounts
+    review_count <- 1       #Counts which review is being counted
+    switch <- 0
+    x <- 0                  #counter for word_count position
+    
+    
+    lct <- Sys.getlocale("LC_TIME")
+    Sys.setlocale("LC_TIME", "C")
+    
+    
+    for (i in 1:length(lines)){
+      
+      if ((switch == 1)&(lines[i] == "label_end_comment")) {
+        switch <- 0
+      }
+      
[…]

### 2019-09-25 textmining_peerj.R

@@ -1,9 +1,3 @@
-###Notes###
-#install.packages("tidytext")
-#install.packages("dplyr")
-#install.packages("stringr")
-#install.packages("textdata") #for sentiment analysis
-
 library(dplyr)
 library(tidytext)
 library(pdftools)
@@ -11,22 +5,7 @@ library(tm)
 library(stringr)
 library(here)
 
-setwd("C:/Users/Daniel/surfdrive/R/open_peer_review/peerj_reviews_txt")
 here()
-#########################################Getting the lexicons######################################################
-nrc_negative <- vector()
-nrc_positive <- vector()
-
-nrc <- get_sentiments("nrc") 
-
-for (i in 1:length(nrc$sentiment)){
-  if (nrc$sentiment[i] == "negative")
-    nrc_negative <- append(nrc_negative, nrc$word[i])
-}
-for (i in 1:length(nrc$sentiment)){
-  if (nrc$sentiment[i] == "positive")
-    nrc_positive <- append(nrc_positive, nrc$word[i])
-}
 
 #########################################variables used to create the dataframe#################################
 df_link <- c()
@@ -36,20 +15,18 @@ df_version <- c()
 df_recommendation <- c()
 df_word_count <- c()
 df_masked <- c()
-df_positive <- c()
-df_negative <- c()
+df_reviewer_name <- c()
 df_id <- c()
 open_reviews <- 0
 closed_reviews <- 0
 total_version <- 0
 
-r <- 1
 #########################################read txt file##########################################################
-for (r in 1:10){ #starting the loop to create the dataframe from the 6800 PeerJ articles
+for (r in 1:7223){ #starting the loop to create the dataframe from the 6800 PeerJ articles
   
   review_id <- r
   
-  path <- paste(review_id,".txt", sep="")
+  path <- paste("peerj_reviews_txt/",review_id,".txt", sep="")
   
   open_file <- file(path, open = "r")
   lines <- readLines(open_file)
@@ -70,8 +47,6 @@ for (r in 1:10){ #starting the loop to create the dataframe from the 6800 PeerJ 
     ###############################Word count, positive and negative###############################################
     
     word_count <- vector()  #Vector that contains the wordcounts
-    positive <- vector()    #Vector that contains the positive word count
-    negative <- vector()    #Vector that contains the negative word count
[…]

### 2019-10-11 manuscript.Rmd
update code and download pdf files

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]
+#TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]
+
+#Create dataframe for TRS and PeerJ of unique rows (e.g., for days)
+TRS_unique <- TRS_data[!duplicated(TRS_data$df_link),]
+PeerJ_unique <- PeerJ_data[!duplicated(PeerJ_data$df_link),]
+
+# One submission to PeerJ was accepted but no reviewer info. It means they are accepted by the editor? Or just an early mistake.
+sum(is.na(PeerJ_unique$df_days))
+
+# Mean review time (almost the same as Nino original - we have a few more pdf's)
+TRS_mean_review_time <- mean(TRS_unique$df_days)
+PeerJ_mean_review_time <- mean(PeerJ_unique$df_days, na.rm = TRUE)
+
+# How many reviews are masked?
+mean(TRS_data$df_masked)
+mean(PeerJ_data$df_masked)
+
+length(TRS_data$df_link)
+length(PeerJ_data$df_link)
+
+# Exploratory
+# Randomly split masked over 100 subgroups to see progression over time - seems stable.
+df_over_time <- data.frame(TRS_data$df_masked[1:3600], rep(seq(1,100,1),each = 360))
+colnames(df_over_time) <- c("masked", "time") # specify columns names
+x <- group_by(df_over_time, time)
+x <- summarize(x, m = mean(masked))
+
+df_over_time <- data.frame(PeerJ_data$df_masked[1:12300], rep(seq(1,100,1),each = 1230))
+colnames(df_over_time) <- c("masked", "time") # specify columns names
+x <- group_by(df_over_time, time)
+x <- summarize(x, m = mean(masked))
 
@@
 
+In Nino's BEP there were  3552 reviews in RSOS. I have 3629 after running all his code.
+
 Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.

### 2019-10-11 download_RSOS_pdf.R

@@ -1,0 +1,33 @@
+#install.packages("pdftools")
+#install.packages("stringr")
+#install.packages("tm")
+
+library(pdftools)
+library(stringr)
+library(tm)
+
+#########################list of article id's#####################################
+article_id <- vector()
+
+path <- "scopus_export_rsos.csv" #used for downloading the pdf's from open biology (list with the open biology ID's)
+#path <- "C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
+
+conn <- file(path,open="r")
+scopus_data <-  read.csv(path, stringsAsFactors = FALSE)
+article_id <- scopus_data$DOI
+close(conn)
+
+########################downloading the pdf's#####################################
+#this section is used for downloading the pdf files.
+sleep <- function() { Sys.sleep(20) } #needed to prevent an IP block from the royal society website
+i<-1
+for (i in 1:length(article_id)) {
+  sleep()
+  #article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
+  article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
+  
+  #url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsos.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="") #for biology
+  url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsos.", article_id[i], "&file=rsos", article_id[i], "_review_history.pdf", sep="")
+  destfile1 <- paste("royal_society_pdf_files\\open_science_2\\review", article_id[i], ".pdf", sep="")
+  download.file(url, destfile=destfile1 , mode="wb")
+}

### 2019-10-11 royal_society_open_biology_create_txt.R

@@ -56,6 +56,7 @@ for (i in 1:length(article_id)) {
   comment_count <-1
   x <- length(trs_doc)
   y <- 1
+  switch <- 0 
   
   while (y<x){
     if (str_sub(trs_doc[y], 1,4) == "RSOB"){  #Search for RSOS or RSOB
@@ -70,18 +71,20 @@ for (i in 1:length(article_id)) {
       x = x + 1
       y = y + 1
     }
-    if (str_sub(trs_doc[y], 1,15) == "Recommendation"){ #There is a small difference between how the recommendation is coded in Open Science and Open Biology - is is "Recommendation?" in open science and "Recommendation" in Open Biology
-      trs_doc <- append(trs_doc, paste("label_recommendation_", recommendation_count, sep="" ), after = y)
+    if (str_sub(trs_doc[y], 1,15) == "Recommendation") { #There is a small difference between how the recommendation is coded in Open Science and Open Biology - is is "Recommendation?" in open science and "Recommendation" in Open Biology
+      trs_doc <- append(trs_doc, paste("label_recommendation_", recommendation_count, sep = "" ), after = y)
       recommendation_count = recommendation_count + 1
       x = x + 1
+      switch <- 1
     }
-     if (str_sub(trs_doc[y], 1,22) == "Comments to the Author"){
-      trs_doc <- append(trs_doc, paste("label_comment_", comment_count, sep="" ), after = y)
+     if (str_sub(trs_doc[y], 1,22) == "Comments to the Author" & (switch == 1)) {
+      trs_doc <- append(trs_doc, paste("label_comment_", comment_count, sep = "" ), after = y)
       comment_count = comment_count + 1
        x = x + 1
+       switch <- 0
      }
-    if (str_sub(trs_doc[y], 1,15) == "Decision letter"){
-      trs_doc <- append(trs_doc, paste("label_end_comment", sep="" ), after = y -1)
+    if (str_sub(trs_doc[y], 1,15) == "Decision letter") {
+      trs_doc <- append(trs_doc, paste("label_end_comment", sep = "" ), after = y -1)
       x = x + 1
       y = y + 1
     }

### 2019-10-11 royal_society_open_science_create_txt.R

@@ -55,6 +55,7 @@ for (i in 1:length(article_id)) {
   comment_count <-1
   x <- length(trs_doc)
   y <- 1
+  switch <- 0
   
   while (y<x){
     if (str_sub(trs_doc[y], 1,4) == "RSOS"){ #Search for RSOS or RSOB
@@ -73,11 +74,13 @@ for (i in 1:length(article_id)) {
       trs_doc <- append(trs_doc, paste("label_recommendation_", recommendation_count, sep="" ), after = y)
       recommendation_count = recommendation_count + 1
       x = x + 1
+      switch <- 1
     }
-     if (str_sub(trs_doc[y], 1,22) == "Comments to the Author"){
+     if (str_sub(trs_doc[y], 1,22) == "Comments to the Author" & (switch == 1)){
       trs_doc <- append(trs_doc, paste("label_comment_", comment_count, sep="" ), after = y)
       comment_count = comment_count + 1
        x = x + 1
+       switch <- 0
      }
     if (str_sub(trs_doc[y], 1,15) == "Decision letter"){
       trs_doc <- append(trs_doc, paste("label_end_comment", sep="" ), after = y -1)

### 2019-10-11 textmining_peerj.R

@@ -49,6 +49,7 @@ for (r in 1:7223){ #starting the loop to create the dataframe from the 6800 Peer
     word_count <- vector()  #Vector that contains the wordcounts
     review_count <- 1        #Counts which review is being counted
     x <- 0                  #counter for word_count position
+    switch_review_count <- 0
     
     # PeerJ subdivides the review in 4 sections: 
     # Basic reporting (under label_br), experimental design (label_ed), 
@@ -60,19 +61,32 @@ for (r in 1:7223){ #starting the loop to create the dataframe from the 6800 Peer
         x = x + 1
         word_count[x] <- 0
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
+        review_count <- review_count + 1
+        switch_review_count <- 1
       }
       
       if(lines[i] == paste("label_ed_", review_count, sep="")){
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
+        if (switch_review_count == 0) {
+          review_count <- review_count + 1
+          switch_review_count <- 1
+        }
       }
       
       if(lines[i] == paste("label_votf_", review_count, sep="")){
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
+        if (switch_review_count == 0) {
+          review_count <- review_count + 1
+          switch_review_count <- 1
+        }
       }
       
       if(lines[i] == paste("label_cfta_", review_count, sep="")){
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
-        review_count = review_count + 1
+        if (switch_review_count == 0) {
+          review_count <- review_count + 1
+          switch_review_count <- 1
+        }
       }
     }
     
@@ -116,6 +130,7 @@ for (r in 1:7223){ #starting the loop to create the dataframe from the 6800 Peer
       }
       if (lines[i] == paste("label_author_", author_count, sep="")){
         reviewer_name <- append(reviewer_name, gsub(" ·", "", lines[i+1])) #Save author name (or Reviewer name)
+        switch_review_count <- 0
         if (grepl("Reviewer", lines[i+1])){
           masked <- append(masked, 1)
           version <- append(version, version_count - 1)

### 2019-10-19 manuscript.Rmd
update manuscript and data

@@
 
+# # Using data.table command
+# group <- as.data.table(PeerJ_data)
+# TEST <- group[group[, .I[df_version == max(df_version)], by=df_link]$V1]
+
+# Select only those reviews for each paper with the highest version (first review)
+# For PeerJ the highest number is the first review (for RSOS this is reversed)
+PeerJ_data_R1 <- group_by(PeerJ_data, df_link)
+PeerJ_data_R1 <- top_n(PeerJ_data_R1, 1, df_version)
+
+TRS_data_R1 <- group_by(TRS_data, df_link)
+TRS_data_R1 <- top_n(TRS_data_R1, -1, df_version) #use top_n but specify -1 for bottom 1, or first review.
+
+### general numbers
+sum(PeerJ_data_R1$df_masked == 0)
+sum(PeerJ_data_R1$df_masked == 1)
+
+sum(TRS_data_R1$df_masked == 0)
+sum(TRS_data_R1$df_masked == 1)
+
+# It is useful to select only cases that have a recommendation
+TRS_data_complete <- TRS_data[complete.cases(TRS_data$df_recommendation),]
+
+x <- group_by(PeerJ_data_R1, df_recommendation)
+x <- summarize(x, m = mean(df_masked))
+x
+
+x <- group_by(PeerJ_data_R1, df_recommendation)
+x <- summarize(x, m = sum(df_masked))
+x
+
+x <- group_by(TRS_data, df_recommendation)
+x <- summarize(x, m = mean(df_masked))
+x
+
+x <- group_by(TRS_data, df_recommendation)
+rowsum(TRS_data_complete[,c(5,7)], group = TRS_data_complete$df_recommendation, na.rm = TRUE)
+
+count(TRS_data$df_recommendation)
+
+x <- summarize(x, m = sum(df_masked))
+x <- x[1:4,1:2]
+chisq.test(x, correct=FALSE)
+
+x <- x[2:3,1:2]
+chisq.test(x, correct=FALSE)
+
 length(TRS_data$df_link)

### 2019-10-19 manuscript2.Rmd
update manuscript and data

---
title: "Open Peer Review"
author: "Daniel Lakens"
date: "22-9-2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(stringr)
library(ggplot2)
library(here)

here::here()

```
```{r}
#### READ IN DATA
# Read open science and open biology rds datafiles
TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
# Combine both datasets into one.
TRS_data <- rbind(TRS_data_os, TRS_data_ob)

#Read in PeerJ data
PeerJ_data <- readRDS(file = "peerj_data.rds")

# For manual checks, sort TRS data on doi number
TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]

#Create dataframe for TRS and PeerJ of unique rows (e.g., for days)
TRS_unique <- TRS_data[!duplicated(TRS_data$df_link),]
PeerJ_unique <- PeerJ_data[!duplicated(PeerJ_data$df_link),]

# We can see how many reviews are open in PeerJ by counting all txt files in the peer_reviews_txt folder, and seeing how many end up in our dataframe:
open_review_PeerJ <- nrow(PeerJ_unique)/length(list.files(path = "peerj_reviews_txt"))

# We can see how many reviews are open in TRS by counting all doi in scopus, and seeing how many end up in our list of open reviews:
OS_pdf_list <- readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r"))

open_review_TRS <- length(OS_pdf_list) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
# In this blog Royal Society says around 2/3 of reviews are published alongside the article in 2017: http://blogs.royalsociety.org/publishing/publication-of-peer-review-reports/ 
TRS_2017 <- filter(TRS_data, str_sub(TRS_data$df_link, -6) > 170000 & str_sub(TRS_data$df_link, -6) < 180000 & TRS_data$df_section == "Open Science")

TRS_2017_open <- OS_pdf_list[OS_pdf_list > 170000 & OS_pdf_list < 180000]
# Seems much lower in our sample. 
length(TRS_2017_open)/nrow(TRS_2017)

# open_review_TRS <- length(length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI))>170000 & readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r")<180000)) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)

XXX <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
# One submission to PeerJ was accepted but no reviewer info. It means they are accepted by the editor? Or just an early mistake.
sum(is.na(PeerJ_unique$df_days))

# Mean review time (
TRS_mean_review_time <- mean(TRS_unique$df_days)
PeerJ_mean_review_time <- mean(PeerJ_unique$df_days, na.rm = TRUE)

# How many reviews are anonymous?
mean(TRS_data$df_anonymous)
mean(PeerJ_data$df_anonymous)

# # Using data.table command
# group <- as.data.table(PeerJ_data)
# TEST <- group[group[, .I[df_version == max(df_version)], by=df_link]$V1]

# Select only those reviews for each paper with the highest version (first review)
PeerJ_data_R1 <- group_by(PeerJ_data, df_link)
PeerJ_data_R1 <- top_n(PeerJ_data_R1, 1, df_version)

TRS_data_R1 <- group_by(TRS_data, df_link)
TRS_data_R1 <- top_n(TRS_data_R1, 1, df_version)

### general numbers
sum(PeerJ_data_R1$df_anonymous == 0) # how many reviews for first submissions are not anonymous?
sum(PeerJ_data_R1$df_anonymous == 1) # how many reviews for first submissions are anonymous?

sum(TRS_data_R1$df_anonymous == 0)
sum(TRS_data_R1$df_anonymous == 1)

# It is useful to select only cases that have a recommendation
TRS_data_complete <- TRS_data[complete.cases(TRS_data$df_recommendation),]

```

## Peer Review Reports

PeerJ provides authors the option to reproduce the complete peer review history of their article alongside the final publication of the article. 
The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science). 
Peer reviewers have the option to provide their names to the authors when submitting their peer review for both the PeerJ and The Royal Society Open Science and Open Biology.

We examined the first 7223 articles pubished in the PeerJ, as well as the first `r length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)` articles in RSOS and the first `r length(read.csv("scopus_export_rsob.csv", stringsAsFactors = FALSE)$DOI)` articles in RSOB.

## Accessing Open Peer Reviews

PeerJ assigns all articles a number from 1, increasing consecutively with each published manuscript. Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article). Using text-mining tools in R (cite R, RCurl, XML, stringer) we downloaded all reviews and stored them as individual text files. Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files. A list of the DOI for every article published in these two outlets was retrieved through Scopus. All reviews were downloaded, and the PDF files were exported to plain text files using pdftools (CITE).

```{r}

# sum number of anonymous responses by subgroup using the by command in base R
PeerJ_anonymous_by_recommendation <- by(PeerJ_data_R1$df_anonymous == 1, PeerJ_data_R1$df_recommendation, sum)
PeerJ_notanonymous_by_recommendation <- by(PeerJ_data_R1$df_anonymous == 0, PeerJ_data_R1$df_recommendation, sum)

#create plot data for accept, minor, major recommendations
plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
                   c("anonymous", "anonymous", "anonymous", "not anonymous", "not anonymous", "not anonymous"),
                   c(PeerJ_anonymous_by_recommendation, PeerJ_notanonymous_by_recommendation))

colnames(plot_data) <- c("recommendation", "signed", "count")

ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

#create plot data for only minor, major recommendations
plot_data <- data.frame(factor(c("minor revision", "major revision", "minor revision", "major revision"), levels = c("minor revision", "major revision"))
                               ,
                   c("anonymous", "anonymous", "not anonymous", "not anonymous"),
                   c(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]))
colnames(plot_data) <- c("recommendation", "signed", "count")

ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

prop_data <- cbind(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "not anonymous") #add row names
# Test of these different proportions
prop.test(prop_data) #perform test of proportions

# In proportions
# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
# Calculate proportions
1-as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))

##########
# Analysis for The Royal Society (TRS)
##########

# sum number of anonymous responses by subgroup using the by command in base R
TRS_anonymous_by_recommendation <- by(TRS_data_R1$df_anonymous == 1, TRS_data_R1$df_recommendation, sum)
TRS_notanonymous_by_recommendation <- by(TRS_data_R1$df_anonymous == 0, TRS_data_R1$df_recommendation, sum)

#create plot data for accept, minor, major recommendations
plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
                   c("anonymous", "anonymous", "anonymous", "anonymous", "not anonymous", "not anonymous", "not anonymous", "not anonymous"),
                   c(TRS_anonymous_by_recommendation, TRS_notanonymous_by_recommendation))
colnames(plot_data) <- c("recommendation", "signed", "count")

ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

#create plot data for only minor, major recommendations
plot_data <- data.frame(c("minor revision", "major revision", "minor revision", "major revision"),
                   c("anonymous", "anonymous", "not anonymous", "not anonymous"),
                   c(TRS_anonymous_by_recommendation[2:3], TRS_notanonymous_by_recommendation[2:3]))
colnames(plot_data) <- c("recommendation", "signed", "count")

ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

prop_data <- cbind(TRS_anonymous_by_recommendation[2:3], TRS_notanonymous_by_recommendation[2:3]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "not anonymous") #add row names

# In proportions
# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
680/(680+524)
178/(178+83)

# Test of these different proportions
prop.test(prop_data) #perform test of proportions

prop_data <- cbind(TRS_anonymous_by_recommendation[c(1,3)], TRS_notanonymous_by_recommendation[c(1,3)]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "notanonymous") #add row names
prop.test(prop_data) #perform test of proportions

prop_data <- cbind(TRS_anonymous_by_recommendation[c(1,2)], TRS_notanonymous_by_recommendation[c(1,2)]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "notanonymous") #add row names
prop.test(prop_data) #perform test of proportions

# Calculate proportions
1-as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))

# Analyze words
# TRS
words <- by(TRS_data_R1$df_word_count, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)

plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
                   c("not anonymous", "not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous", "anonymous"),
                   c(words))
colnames(plot_data) <- c("recommendation", "signed", "wordcount")

ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)

# Word counts PeerJ

words <- by(PeerJ_data_R1$df_word_count, PeerJ_data_R1[,c(5,7)], mean, simplify = TRUE)

plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
                   c("not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous"),
                   c(words))
colnames(plot_data) <- c("recommendation", "signed", "wordcount")

ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
  geom_jitter() +
  theme_linedraw(base_size = 20)

t.test(PeerJ_data_R1$df_word_count ~ PeerJ_data_R1$df_anonymous)

# Exploratory
# Randomly split anonymous over 100 subgroups to see progression over time - seems stable.
df_over_time <- data.frame(TRS_data$df_anonymous[1:3600], rep(seq(1,100,1),each = 360))
colnames(df_over_time) <- c("anonymous", "time") # specify columns names
x <- group_by(df_over_time, time)
x <- summarize(x, m = mean(anonymous))

df_over_time <- data.frame(PeerJ_data$df_anonymous[1:12300], rep(seq(1,100,1),each = 1230))
colnames(df_over_time) <- c("anonymous", "time") # specify columns names
x <- group_by(df_over_time, time)
x <- summarize(x, m = mean(anonymous))

# Analysis total review time
# TRS
review_time <- by(TRS_data_R1$df_days, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)

plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
                   c("not anonymous", "not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous", "anonymous"),
                   c(review_time))
colnames(plot_data) <- c("recommendation", "signed", "days")

ggplot(plot_data, aes(x = recommendation, y = days, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)

heroes <- filter(TRS_data_R1, df_anonymous == 0 & df_recommendation == 4)
filter(PeerJ_data, df_anonymous == 0 & df_reviewer_name == "Daniel Lakens")

me <- filter(TRS_data, df_anonymous == 0)
me <- me[ with( me , order ( df_reviewer_name)),]

```

In Nino's BEP there were  3552 reviews in RSOS. I have 3629 after running all his code.

Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
What does this mean?

Word counts are not perfectly reliable for several reasons (e.g., addition of references, but also more importantly comments in an attached pdf - maybe we can search for attached and pdf in short comments to identify these. )

" This result is similar to the findings in Bornmann, Wolf,
and Daniel (2012) that the comments in public peer review are much longer than
the comments in closed peer review."

## Future Research

The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, and the names of reviewers who signed their review. Through the DOI, researchers can link this data to, for example, citation counts for each manuscript. This makes it possible to explore whether initial evaluations of a manuscript are related to future citations counts. By manually coding which career stage authors and reviewers belong to during the review process it is possible to gain insights into who is more likely practice open science. Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.

### 2019-10-19 open_peer_review.Rmd
update manuscript and data

---
title             : "The Proportion of Signed Open Reviews Depends on the Recommendation"
shorttitle        : "Recommendation Dependent Signing"
author: 
  - name          : "Daniel Lakens"
    affiliation   : "1"
    corresponding : yes
    address       : "ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
  - name          : "Nino van Sambeek"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology, The Netherlands"
author_note: |
  This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. 
abstract: |
  Open Peer Review is becoming increasingly common, and when reviewers decide whether or not to sign, they take their recommendation into account.

keywords          : "Peer Review, Open Science, Transparency"
wordcount         : 4926
bibliography      : ["signing_open_peer_review_.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
class             : "jou, a4paper"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}

library(dplyr)
library(stringr)
library(ggplot2)
library(here)

here::here()
#### READ IN DATA
# Read open science and open biology rds datafiles
TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
# Combine both datasets into one.
TRS_data <- rbind(TRS_data_os, TRS_data_ob)

#Read in PeerJ data
PeerJ_data <- readRDS(file = "peerj_data.rds")

# For manual checks, sort TRS data on doi number
TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]

#Create dataframe for TRS and PeerJ of unique rows (e.g., for days)
TRS_unique <- TRS_data[!duplicated(TRS_data$df_link),]
PeerJ_unique <- PeerJ_data[!duplicated(PeerJ_data$df_link),]
TRS_unique_os <- TRS_data_os[!duplicated(TRS_data_os$df_link),]
TRS_unique_ob <- TRS_data_ob[!duplicated(TRS_data_ob$df_link),]

# We can see how many reviews are open in PeerJ by counting all txt files in the peer_reviews_txt folder, and seeing how many end up in our dataframe:
open_review_PeerJ <- nrow(PeerJ_unique)/length(list.files(path = "peerj_reviews_txt"))

# We can see how many reviews are open in TRS by counting all doi in scopus, and seeing how many end up in our list of open reviews:
OS_pdf_list <- readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r"))

open_review_TRS <- length(OS_pdf_list) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
# In this blog Royal Society says around 2/3 of reviews are published alongside the article in 2017: http://blogs.royalsociety.org/publishing/publication-of-peer-review-reports/ 
TRS_2017 <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
TRS_2017 <- filter(TRS_2017, str_sub(TRS_2017$DOI, -6) > 170000 & str_sub(TRS_2017$DOI, -6) < 180000)

TRS_2017_open <- OS_pdf_list[OS_pdf_list > 170000 & OS_pdf_list < 180000]
# Seems close - I am not excluding corrections (that have no peer review history), I think the blog post is. 
length(TRS_2017_open)/nrow(TRS_2017)

# open_review_TRS <- length(length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI))>170000 & readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r")<180000)) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)

XXX <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
# One submission to PeerJ was accepted but no reviewer info. It means they are accepted by the editor? Or just an early mistake.
sum(is.na(PeerJ_unique$df_days))

# Mean review time (
TRS_mean_review_time <- mean(TRS_unique$df_days)
PeerJ_mean_review_time <- mean(PeerJ_unique$df_days, na.rm = TRUE)

# How many reviews are anonymous?
mean(TRS_data$df_anonymous)
mean(PeerJ_data$df_anonymous)

# # Using data.table command
# group <- as.data.table(PeerJ_data)
# TEST <- group[group[, .I[df_version == max(df_version)], by=df_link]$V1]

# Select only those reviews for each paper with the highest version (first review)
PeerJ_data_R1 <- group_by(PeerJ_data, df_link)
PeerJ_data_R1 <- top_n(PeerJ_data_R1, 1, df_version)
mean(count(PeerJ_data_R1, df_link)$n) #count reviews per article.

TRS_data_R1 <- group_by(TRS_data, df_link)
TRS_data_R1 <- top_n(TRS_data_R1, 1, df_version)

TRS_review_agree <- group_by(TRS_data_R1, df_link)
unique(TRS_review_agree$df_recommendation)

# We can easily check whether reviewers agree or not by looking at their recommendations.
TRS_review_agree <- group_by(TRS_data_R1, df_link)
TRS_review_agree <- mutate(TRS_review_agree, df_unique = n_distinct(df_recommendation))
TRS_review_agree <- TRS_review_agree[!duplicated(TRS_review_agree$df_link),]

ggplot(TRS_review_agree, aes(x = as.factor(df_unique))) + 
  geom_bar() +
  theme_linedraw(base_size = 20)

# Are there really reviws with 4 distinct recommendations?
sum(TRS_review_agree$df_unique == 4)

#Select the top recommendation for each review
TRS_data_R1_top <- top_n(TRS_data_R1, 1, df_recommendation) 
TRS_data_R1_top <- TRS_data_R1_top[!duplicated(TRS_data_R1_top$df_link),]
#Select the bottom recommendation for each review
TRS_data_R1_bottom <- top_n(TRS_data_R1, -1, df_recommendation) 
TRS_data_R1_bottom <- TRS_data_R1_bottom[!duplicated(TRS_data_R1_bottom$df_link),]

#Compute the difference between top and bottom
rev_dif <- TRS_data_R1_top$df_recommendation - TRS_data_R1_bottom$df_recommendation
#We table the difference - many are similar, many differ 1 category, some 2 few 3.
table(rev_dif)

# It is useful to select only cases that have a recommendation
TRS_data_complete <- TRS_data[complete.cases(TRS_data$df_recommendation),]

```

In a previous study where researchers were randomly assigned to a condition where their reviews would be signed, or not signed [@walsh_open_2000], reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51). This suggests that a causal effect exists between knowing your name will be known or not and the recommendation reviewers provide. Another study that randomly assigned reviewers to a condition where reviewer names would be shared alongside the reviews or a control condition did not find differences between recommendations that were made, but in this study a much larger percentage of reviewers (55%) declined to participate in the trial, raising the possibility of self-selection of participants [@rooyen_effect_2010]. Reviewers indicate they are less likely to review for a journal if their names will be made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers [@mulligan_peer_2013]. A more recent large survey among almost 3000 scientists found that 50.8% of reviewers believe signed open reviews would make peer review worse, with almost two-thirds of respondents indicating they believed reviewers would be less likely to devliver strong criticisms if their identity became known to the authors [@ross-hellauer_survey_2017].

## Accessing Open Peer Reviews

PeerJ assigns all articles a number from 1, increasing consecutively with each published manuscript. Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article). Using text-mining tools in R (cite R, RCurl, XML, stringer) we downloaded all reviews and stored them as individual text files. Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files. A list of the DOI for every article published in these two outlets was retrieved through Scopus. All reviews were downloaded, and the PDF files were exported to plain text files using pdftools [@ooms_pdftools_2019]. Text files were textmined using the stringr package [@wickham_stringr_2019].

For each article we extracted the nuber of revisions, and for each revision we saved for each reviewer whether the reviewer signed the review or not, the word count for their review, and the recommendation for that review round. Note that for PeerJ recommendations each round are giving by the editor. We therefore do not directly know which recommendation each reviewer provided. For RSOS and RSOB reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'. Although 'reject' recommendations occur for RSOS and RSOB, both PeerJ and RSOS and RSOB only share reviews for published articles, and therefore we have very few reject recommendation in RSOS and RSOB, and none in PeerJ. Searching all text files for PeerJ for 'appealed on' reveals 44 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published. We have coded these papers as 'major revisions'. We also extracted the names of all reviewers when they signed, and calculated the days each manuscript was under peer review from initial submission to acceptance for publication.

## Peer Review Reports

PeerJ provides authors the option to reproduce the complete peer review history of their article alongside the final publication of the article. 
The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science). 
Peer reviewers have the option to provide their names to the authors when submitting their peer review for both PeerJ and Royal Society Open Science and Open Biology.

We examined the first 7223 articles pubished in PeerJ, as well as the first `r length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)` articles in RSOS and the first `r length(read.csv("scopus_export_rsob.csv", stringsAsFactors = FALSE)$DOI)` articles in RSOB. We retrieved reviews for `r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique_os)` articles in RSOS, and `r nrow(TRS_unique_ob)` articles in RSOB. WE NEED TO REMOVE CORRECTIONS FROM THE NUMBERS ABOVE. Articles can go through multiple rounds of review. We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision. On average initial submissions at PeerJ received `r round(mean(count(PeerJ_data_R1, df_link)$n), 2)` reviews. Articles in the Royal Society journals received on average `r round(mean(count(TRS_data_R1, df_link)$n), 2)` reviews for the original submission.

```{r, include = FALSE}
# sum number of anonymous responses by subgroup using the by command in base R
PeerJ_anonymous_by_recommendation <- by(PeerJ_data_R1$df_anonymous == 1, PeerJ_data_R1$df_recommendation, sum)
PeerJ_notanonymous_by_recommendation <- by(PeerJ_data_R1$df_anonymous == 0, PeerJ_data_R1$df_recommendation, sum)

##########
# Analysis for The Royal Society (TRS)
##########

# sum number of anonymous responses by subgroup using the by command in base R
TRS_anonymous_by_recommendation <- by(TRS_data_R1$df_anonymous == 1, TRS_data_R1$df_recommendation, sum)
TRS_notanonymous_by_recommendation <- by(TRS_data_R1$df_anonymous == 0, TRS_data_R1$df_recommendation, sum)

```

## Signed reviews as a function of the recommendation

When analzing all reviews of original submissions in PeerJ `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their reviews and `r sum(PeerJ_data_R1$df_anonymous == 1)` did not. In The Royal Society journals `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their first review while `r sum(TRS_data_R1$df_anonymous == 1)` did not. The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for the Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed only the first 1214 articles published in PeerJ.

To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round. Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer. The percentage of signed peer reviews is larger for minor revisions (`r 100 * as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))[2]`%) than it is for major revisions (`r 100 * as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))[3]`%). Too few articles are accepted after the initial revision in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to provide reliable estimates for this category.

```{r, PeerJrec, fig.cap = "Frequencies of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended 'minor revisions' or 'major revisions'."}

# #create plot data for accept, minor, major recommendations
# plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
#                    c("anonymous", "anonymous", "anonymous", "not anonymous", "not anonymous", "not anonymous"),
#                    c(PeerJ_anonymous_by_recommendation, PeerJ_notanonymous_by_recommendation))
# 
# colnames(plot_data) <- c("recommendation", "signed", "count")
# 
# ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
#   geom_bar(position="dodge", stat="identity") +
#   theme_linedraw(base_size = 12)

#create plot data for only minor, major recommendations
plot_data <- data.frame(factor(c("minor revision", "major revision", "minor revision", "major revision"), levels = c("minor revision", "major revision"))
                               ,
                   c("anonymous", "anonymous", "not anonymous", "not anonymous"),
                   c(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]))
colnames(plot_data) <- c("recommendation", "signed", "count")

ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) +
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20) +  
  theme(legend.position = "top",
        legend.title=element_blank(),
        panel.grid.major.x = element_blank()) + 
  scale_fill_manual(values = c("#000000", "#808080")) + 
  coord_cartesian(ylim = c(0, 5000)) +
  geom_text(aes(label = count), 
              size = 6, 
              color = "black",
              position = position_dodge(width = 0.9),
              vjust = -.5)
```

Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of 'accept', 'minor revisions', 'major revisions', or 'reject'. We can therefore directly compare how recommendations are related to the decision to sign reviews. The percentage of signed peer reviews is decreases as recommendations become more negative, from `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[1]`% for 'accept' recommendations, `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[2]`% for 'minor revisions', `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[3]`% for 'major revisions', and `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[4]`% for 'reject' recommendations.

Since these data are correlational we can not draw causal conclusions. It is possible that reviewers are less likely to sign more negative reviews. It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews. Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.

# Additional Analyses

Open reviews make it possible to examine additional interesting questions. The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, and the names of reviewers who signed their review. Through the DOI, researchers can link this data to, for example, citation counts for each manuscript. This makes it possible to explore whether initial evaluations of a manuscript are related to future citations counts. By manually coding which career stage authors and reviewers belong to during the review process it is possible to gain insights into who is more likely practice open science. It is possible to extract information about the time between submission and acceptance for each article (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for RSOS and RSOB). Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.

For example, since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, we can see how often reviewers agree. For the `r sum(table(rev_dif))` individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in `r table(rev_dif)[1]` (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`%) of the time. For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject). There were `r sum(TRS_review_agree$df_unique == 4)` articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.

Regrettably, neither PeerJ nor RSOS make peer reviews available for manuscripts that were rejected. As a consequence, we have analyzed a biased sample of the literature. At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles. Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at specific journals.

```{r, TRSrec, fig.cap = "Frequencies of signed and unsigned reviews as a function of whether the reviewer at the Royal Society Open Science and Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}

#create plot data for accept, minor, major recommendations
plot_data <- data.frame(factor(c("accept", "minor", "major", "reject", "accept", "minor", "major", "reject"), levels = c("accept", "minor", "major", "reject")),
                   c("anonymous", "anonymous", "anonymous", "anonymous", "not anonymous", "not anonymous", "not anonymous", "not anonymous"),
                   c(TRS_anonymous_by_recommendation, TRS_notanonymous_by_recommendation))
colnames(plot_data) <- c("recommendation", "signed", "count")

ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20) + 
  theme(legend.position = "top",
        legend.title=element_blank(),
        panel.grid.major.x = element_blank()) + 
  scale_fill_manual(values = c("#000000", "#808080")) + 
  coord_cartesian(ylim = c(0, 1250)) +
  geom_text(aes(label = count), 
              size = 6, 
              color = "black",
              position = position_dodge(width = 0.9),
              vjust = -.5)

# #create plot data for only minor, major recommendations
# plot_data <- data.frame(c("minor revision", "major revision", "minor revision", "major revision"),
#                    c("anonymous", "anonymous", "not anonymous", "not anonymous"),
#                    c(TRS_anonymous_by_recommendation[2:3], TRS_notanonymous_by_recommendation[2:3]))
# colnames(plot_data) <- c("recommendation", "signed", "count")
# 
# ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
#   geom_bar(position="dodge", stat="identity") +
#   theme_linedraw(base_size = 20)

```

```{r}
prop_data <- cbind(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "not anonymous") #add row names
# Test of these different proportions
prop.test(prop_data) #perform test of proportions

# In proportions
# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
# Calculate proportions
1-as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))

```

```{r}
# Word counts PeerJ

words <- by(PeerJ_data_R1$df_word_count, PeerJ_data_R1[,c(5,7)], mean, simplify = TRUE)

plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
                   c("not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous"),
                   c(words))
colnames(plot_data) <- c("recommendation", "signed", "wordcount")

ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
  geom_jitter() +
  theme_linedraw(base_size = 20)

t.test(PeerJ_data_R1$df_word_count ~ PeerJ_data_R1$df_anonymous)

```

In Nino's BEP there were  3552 reviews in RSOS. I have 3629 after running all his code.

Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
What does this mean?

Word counts are not perfectly reliable for several reasons (e.g., addition of references, but also more importantly comments in an attached pdf - maybe we can search for attached and pdf in short comments to identify these. )

" This result is similar to the findings in Bornmann, Wolf,
and Daniel (2012) that the comments in public peer review are much longer than
the comments in closed peer review."

## Future Research

## NOTES

Searching all text files of PeerJ for 'appealed on' reveals 44 articles that were initially appealed, and subsequently published. 
From Nino's thesis for RSOS: "Interestingly, for 39 of the reviews we had
access to (and were thus published) the final recommendation given by the editor is to reject the manuscript. For these articles to still get published, the author has to appeal the rejection and change the decision made by the editor." 
Not sure how he got this - my code does not suggest this.
sum(PeerJ_data$df_recommendation == 4, na.rm = TRUE) # how many reviews for first submissions

From Wang et al: " Of the 3,569 review reports, 85 were submitted as
attachments in various formats (comments inserted to the manuscripts, PDF or Word
DOC) or the reviews contained no substantive content such as “no further comments.”"

# Author Contributions

N. van Sambeek and D. Lakens developed the idea. Both authors generated the R code to generate the data and anayze the results. N van Sambeek drafted the initial version of the manuscript as a Bachelor thesis, D. Lakens wrote the final version, both authors revised the manuscript.

# Conflict of Interest Statement

The authors report no conflicts of interest.

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r, include = FALSE}
### general numbers
sum(PeerJ_data_R1$df_anonymous == 0) # how many reviews for first submissions are not anonymous?
sum(PeerJ_data_R1$df_anonymous == 1) # how many reviews for first submissions are anonymous?

prop_data <- cbind(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "not anonymous") #add row names
# Test of these different proportions
prop.test(prop_data) #perform test of proportions

# In proportions
# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
# Calculate proportions
1-as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))

prop_data <- cbind(TRS_anonymous_by_recommendation[2:3], TRS_notanonymous_by_recommendation[2:3]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "not anonymous") #add row names

# In proportions
# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
680/(680+524)
178/(178+83)

# Test of these different proportions
prop.test(prop_data) #perform test of proportions

prop_data <- cbind(TRS_anonymous_by_recommendation[c(1,3)], TRS_notanonymous_by_recommendation[c(1,3)]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "notanonymous") #add row names
prop.test(prop_data) #perform test of proportions

prop_data <- cbind(TRS_anonymous_by_recommendation[c(1,2)], TRS_notanonymous_by_recommendation[c(1,2)]) #bind as matrix
rownames(prop_data) <- c("minor revision", "major revision") #add column names
colnames(prop_data) <- c("anonymous", "notanonymous") #add row names
prop.test(prop_data) #perform test of proportions

# Calculate proportions
1-as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))

# Analyze words
# TRS
words <- by(TRS_data_R1$df_word_count, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)

plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
                   c("not anonymous", "not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous", "anonymous"),
                   c(words))
colnames(plot_data) <- c("recommendation", "signed", "wordcount")

ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)

# Exploratory
# Randomly split anonymous over 100 subgroups to see progression over time - seems stable.
df_over_time <- data.frame(TRS_data$df_anonymous[1:3600], rep(seq(1,100,1),each = 360))
colnames(df_over_time) <- c("anonymous", "time") # specify columns names
x <- group_by(df_over_time, time)
x <- summarize(x, m = mean(anonymous))

df_over_time <- data.frame(PeerJ_data$df_anonymous[1:12300], rep(seq(1,100,1),each = 1230))
colnames(df_over_time) <- c("anonymous", "time") # specify columns names
x <- group_by(df_over_time, time)
x <- summarize(x, m = mean(anonymous))

# Analysis total review time
# TRS
review_time <- by(TRS_data_R1$df_days, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)

plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
                   c("not anonymous", "not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous", "anonymous"),
                   c(review_time))
colnames(plot_data) <- c("recommendation", "signed", "days")

ggplot(plot_data, aes(x = recommendation, y = days, fill = signed)) + 
  geom_bar(position="dodge", stat="identity") +
  theme_linedraw(base_size = 20)

t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)

heroes <- filter(TRS_data_R1, df_anonymous == 0 & df_recommendation == 4)
filter(PeerJ_data, df_anonymous == 0 & df_reviewer_name == "Daniel Lakens")

me <- filter(TRS_data, df_anonymous == 0)
me <- me[ with( me , order ( df_reviewer_name)),]

##data from Walsh et al 
##
41/(41+36) #accept
53/(53+35) #accept revision
43/(43+31) #resubmit with revision
30/(30+51) #reject

```

### 2019-10-19 open_peer_review.tex
update manuscript and data

\documentclass[,jou, a4paper,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The Proportion of Signed Open Reviews Depends on the Recommendation},
            pdfauthor={Daniel Lakens~\& Nino van Sambeek},
            pdfkeywords={Peer Review, Open Science, Transparency},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{The Proportion of Signed Open Reviews Depends on the Recommendation}
    \author{Daniel Lakens\textsuperscript{1}~\& Nino van Sambeek\textsuperscript{1}}
    \date{}

\shorttitle{Recommendation Dependent Signing}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology, The Netherlands}
\keywords{Peer Review, Open Science, Transparency\newline\indent Word count: 4926}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.

Correspondence concerning this article should be addressed to Daniel Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}

\abstract{
Open Peer Review is becoming increasingly common, and when reviewers decide whether or not to sign, they take their recommendation into account.

}

\begin{document}
\maketitle

In a previous study where researchers were randomly assigned to a condition where their reviews would be signed, or not signed (Walsh, Rooney, Appleby, \& Wilkinson, 2000), reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51). This suggests that a causal effect exists between knowing your name will be known or not and the recommendation reviewers provide. Another study that randomly assigned reviewers to a condition where reviewer names would be shared alongside the reviews or a control condition did not find differences between recommendations that were made, but in this study a much larger percentage of reviewers (55\%) declined to participate in the trial, raising the possibility of self-selection of participants (Rooyen, Delamothe, \& Evans, 2010). Reviewers indicate they are less likely to review for a journal if their names will be made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers (Mulligan, Hall, \& Raphael, 2013). A more recent large survey among almost 3000 scientists found that 50.8\% of reviewers believe signed open reviews would make peer review worse, with almost two-thirds of respondents indicating they believed reviewers would be less likely to devliver strong criticisms if their identity became known to the authors (Ross-Hellauer, Deppe, \& Schmidt, 2017).

\hypertarget{accessing-open-peer-reviews}{%
\subsection{Accessing Open Peer Reviews}\label{accessing-open-peer-reviews}}

PeerJ assigns all articles a number from 1, increasing consecutively with each published manuscript. Reviews are always accessible in html (i.e., at \url{https://peerj.com/articles/1/reviews} for the first article). Using text-mining tools in R (cite R, RCurl, XML, stringer) we downloaded all reviews and stored them as individual text files. Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files. A list of the DOI for every article published in these two outlets was retrieved through Scopus. All reviews were downloaded, and the PDF files were exported to plain text files using pdftools (Ooms, 2019). Text files were textmined using the stringr package (Wickham, 2019).

For each article we extracted the nuber of revisions, and for each revision we saved for each reviewer whether the reviewer signed the review or not, the word count for their review, and the recommendation for that review round. Note that for PeerJ recommendations each round are giving by the editor. We therefore do not directly know which recommendation each reviewer provided. For RSOS and RSOB reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}. Although \enquote{reject} recommendations occur for RSOS and RSOB, both PeerJ and RSOS and RSOB only share reviews for published articles, and therefore we have very few reject recommendation in RSOS and RSOB, and none in PeerJ. Searching all text files for PeerJ for \enquote{appealed on} reveals 44 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published. We have coded these papers as \enquote{major revisions}. We also extracted the names of all reviewers when they signed, and calculated the days each manuscript was under peer review from initial submission to acceptance for publication.

\hypertarget{peer-review-reports}{%
\subsection{Peer Review Reports}\label{peer-review-reports}}

PeerJ provides authors the option to reproduce the complete peer review history of their article alongside the final publication of the article.
The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science).
Peer reviewers have the option to provide their names to the authors when submitting their peer review for both PeerJ and Royal Society Open Science and Open Biology.

We examined the first 7223 articles pubished in PeerJ, as well as the first 2949 articles in RSOS and the first 708 articles in RSOB. We retrieved reviews for 4555 articles in PeerJ, 1412 articles in RSOS, and 148 articles in RSOB. WE NEED TO REMOVE CORRECTIONS FROM THE NUMBERS ABOVE. Articles can go through multiple rounds of review. We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision. On average initial submissions at PeerJ received 2.36 reviews. Articles in the Royal Society journals received on average 2.19 reviews for the original submission.

\hypertarget{signed-reviews-as-a-function-of-the-recommendation}{%
\subsection{Signed reviews as a function of the recommendation}\label{signed-reviews-as-a-function-of-the-recommendation}}

When analzing all reviews of original submissions in PeerJ 4172 reviewers signed their reviews and 6569 did not. In The Royal Society journals 1261 reviewers signed their first review while 2150 did not. The percentages of people who sign (38.84\% for PeerJ, 36.97\% for the Royal Society) are slightly lower than the 43.23\% reported by (Wang, You, Manasa, \& Wolfram, 2016), who analyzed only the first 1214 articles published in PeerJ.

To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round. Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer. The percentage of signed peer reviews is larger for minor revisions (46.37\%) than it is for major revisions (34.63\%). Too few articles are accepted after the initial revision in PeerJ (20 in total) to provide reliable estimates for this category.

\begin{figure}
\centering
\includegraphics{open_peer_review_files/figure-latex/PeerJrec-1.pdf}
\caption{\label{fig:PeerJrec}Frequencies of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended \enquote{minor revisions} or \enquote{major revisions}.}
\end{figure}

Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}. We can therefore directly compare how recommendations are related to the decision to sign reviews. The percentage of signed peer reviews is decreases as recommendations become more negative, from 46.99\% for \enquote{accept} recommendations, 43.86\% for \enquote{minor revisions}, 29.48\% for \enquote{major revisions}, and 11.07\% for \enquote{reject} recommendations.

Since these data are correlational we can not draw causal conclusions. It is possible that reviewers are less likely to sign more negative reviews. It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews. Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.

\hypertarget{additional-analyses}{%
\section{Additional Analyses}\label{additional-analyses}}

Open reviews make it possible to examine additional interesting questions. The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, and the names of reviewers who signed their review. Through the DOI, researchers can link this data to, for example, citation counts for each manuscript. This makes it possible to explore whether initial evaluations of a manuscript are related to future citations counts. By manually coding which career stage authors and reviewers belong to during the review process it is possible to gain insights into who is more likely practice open science. Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.

For example, since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, we can see how often reviewers agree. For the 1559 individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in 646 (41.44\%) of the time. For 42.14\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.69\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.73\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject). There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.

The average time between submission and acceptance for PeerJ for the articles open reviews are available for was 112 days, and for the Royal Society this was 133 days.

\begin{figure}
\centering
\includegraphics{open_peer_review_files/figure-latex/TRSrec-1.pdf}
\caption{\label{fig:TRSrec}Frequencies of signed and unsigned reviews as a function of whether the reviewer at the Royal Society Open Science and Open Biology recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
\end{figure}

\begin{verbatim}
## 
##  2-sample test for equality of proportions with continuity
##  correction
## 
## data:  prop_data
## X-squared = 142.6, df = 1, p-value < 2.2e-16
## alternative hypothesis: two.sided
## 95 percent confidence interval:
##  -0.1369924 -0.0978543
## sample estimates:
##    prop 1    prop 2 
## 0.5362998 0.6537231
\end{verbatim}

\begin{verbatim}
## [1] 0.6000000 0.5362998 0.6537231
\end{verbatim}

\includegraphics{open_peer_review_files/figure-latex/unnamed-chunk-3-1.pdf}

\begin{verbatim}
## Warning: Removed 2 rows containing missing values (geom_bar).
\end{verbatim}

\includegraphics{open_peer_review_files/figure-latex/unnamed-chunk-3-2.pdf}

\begin{verbatim}
## Warning: Removed 2 rows containing missing values (geom_point).
\end{verbatim}

\includegraphics{open_peer_review_files/figure-latex/unnamed-chunk-3-3.pdf}

\begin{verbatim}
## 
##  Welch Two Sample t-test
## 
## data:  PeerJ_data_R1$df_word_count by PeerJ_data_R1$df_anonymous
## t = 4.3438, df = 8046.6, p-value = 1.418e-05
## alternative hypothesis: true difference in means is not equal to 0
## 95 percent confidence interval:
##  21.25429 56.21419
## sample estimates:
## mean in group 0 mean in group 1 
##        481.1711        442.4369
\end{verbatim}

In Nino's BEP there were 3552 reviews in RSOS. I have 3629 after running all his code.

Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
What does this mean?

Word counts are not perfectly reliable for several reasons (e.g., addition of references, but also more importantly comments in an attached pdf - maybe we can search for attached and pdf in short comments to identify these. )

" This result is similar to the findings in Bornmann, Wolf,
and Daniel (2012) that the comments in public peer review are much longer than
the comments in closed peer review."

\hypertarget{future-research}{%
\subsection{Future Research}\label{future-research}}

\hypertarget{notes}{%
\subsection{NOTES}\label{notes}}

Searching all text files of PeerJ for \enquote{appealed on} reveals 44 articles that were initially appealed, and subsequently published.
From Nino's thesis for RSOS: \enquote{Interestingly, for 39 of the reviews we had
access to (and were thus published) the final recommendation given by the editor is to reject the manuscript. For these articles to still get published, the author has to appeal the rejection and change the decision made by the editor.}
Not sure how he got this - my code does not suggest this.
sum(PeerJ\_data\$df\_recommendation == 4, na.rm = TRUE) \# how many reviews for first submissions

From Wang et al: " Of the 3,569 review reports, 85 were submitted as
attachments in various formats (comments inserted to the manuscripts, PDF or Word
DOC) or the reviews contained no substantive content such as \enquote{no further comments.}"

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

N. van Sambeek and D. Lakens developed the idea. Both authors generated the R code to generate the data and anayze the results. N van Sambeek drafted the initial version of the manuscript as a Bachelor thesis, D. Lakens wrote the final version, both authors revised the manuscript.

\hypertarget{conflict-of-interest-statement}{%
\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}

The authors report no conflicts of interest.

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-mulligan_peer_2013}{}%
Mulligan, A., Hall, L., \& Raphael, E. (2013). Peer review in a changing world: An international study measuring the attitudes of researchers. \emph{Journal of the American Society for Information Science and Technology}, \emph{64}(1), 132--161. doi:\href{https://doi.org/10.1002/asi.22798}{10.1002/asi.22798}

\leavevmode\hypertarget{ref-ooms_pdftools_2019}{}%
Ooms, J. (2019). \emph{Pdftools: Text extraction, rendering and converting of PDF documents}.

\leavevmode\hypertarget{ref-rooyen_effect_2010}{}%
Rooyen, S. van, Delamothe, T., \& Evans, S. J. W. (2010). Effect on peer review of telling reviewers that their signed reviews might be posted on the web: Randomised controlled trial. \emph{BMJ}, \emph{341}, c5729. doi:\href{https://doi.org/10.1136/bmj.c5729}{10.1136/bmj.c5729}

\leavevmode\hypertarget{ref-ross-hellauer_survey_2017}{}%
Ross-Hellauer, T., Deppe, A., \& Schmidt, B. (2017). Survey on open peer review: Attitudes and experience amongst editors, authors and reviewers. \emph{PLOS ONE}, \emph{12}(12), e0189311. doi:\href{https://doi.org/10.1371/journal.pone.0189311}{10.1371/journal.pone.0189311}

\leavevmode\hypertarget{ref-walsh_open_2000}{}%
Walsh, E., Rooney, M., Appleby, L., \& Wilkinson, G. (2000). Open peer review: A randomised controlled trial. \emph{The British Journal of Psychiatry}, \emph{176}(1), 47--51. doi:\href{https://doi.org/10.1192/bjp.176.1.47}{10.1192/bjp.176.1.47}

\leavevmode\hypertarget{ref-wang_open_2016}{}%
Wang, P., You, S., Manasa, R., \& Wolfram, D. (2016). Open peer review in scientific publishing: A Web mining study of PeerJ authors and reviewers. \emph{Journal of Data and Information Science}, \emph{1}(4), 60--80.

\leavevmode\hypertarget{ref-wickham_stringr_2019}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}.

\end{document}

### 2019-10-19 check_not_corrupt_royal_society_open_biology.R

@@ -1,0 +1,41 @@
+library(pdftools)
+library(tm)
+library(stringr)
+library(here)
+
+here::here()
+
+#########################list of article id's#####################################
+article_id <- vector()
+# Create a list of all PDF files in the folder
+article_id <- str_extract(list.files(path = "royal_society_pdf_files\\open_biology\\", pattern = "\\.pdf$"), "[0-9]+") #list all files in the folder and extract article ID
+
+for (r in 1:length(article_id)){
+  fix_doc[1] <- "corrupted"
+  review_id <- article_id[r]
+  document <- NULL
+
+  path <- paste("royal_society_pdf_files\\open_biology\\review", review_id, ".pdf", sep="")  #used for open biology
+  
+  if (file.exists(path)){
+    open_file <- file(path,open="r")
+    try(read <- readPDF(control = list(text = "-layout")))
+    try(document <- Corpus(URISource(path), readerControl = list(reader = read)))
+    try(fix_doc <- content(document[[1]])) #this fails when if the file is corrupted resulting in the first item on the fix_doc list remaining "corrupted"
+    
+    if (fix_doc[1] != "corrupted") {
+      article_id_os_open <- append(article_id_os_open, article_id[r])
+    }
+    close(open_file)
+  }
+}
+
+final_txt_file <- "royal_society_pdf_files\\OB_pdf_list.txt" #used for open science
+
+#######################Storing the new list of not corrupted pdf files###########################
+sink(final_txt_file)
+for (i in 1:length(article_id_os_open)){
+  cat(article_id_os_open[i])
+  cat("\n")
+}
+sink()

### 2019-10-19 check_not_corrupt_royal_society_open_science.R

@@ -1,0 +1,41 @@
+library(pdftools)
+library(tm)
+library(stringr)
+library(here)
+
+here::here()
+
+#########################list of article id's#####################################
+article_id <- vector()
+# Create a list of all PDF files in the folder
+article_id <- str_extract(list.files(path = "royal_society_pdf_files\\open_science\\", pattern = "\\.pdf$"), "[0-9]+") #list all files in the folder and extract article ID
+
+for (r in 1:length(article_id)){
+  fix_doc[1] <- "corrupted"
+  review_id <- article_id[r]
+  document <- NULL
+
+  path <- paste("royal_society_pdf_files\\open_science\\review", review_id, ".pdf", sep="") #used for open science
+
+  if (file.exists(path)){
+    open_file <- file(path,open="r")
+    try(read <- readPDF(control = list(text = "-layout")))
+    try(document <- Corpus(URISource(path), readerControl = list(reader = read)))
+    try(fix_doc <- content(document[[1]])) #this fails when if the file is corrupted resulting in the first item on the fix_doc list remaining "corrupted"
+    
+    if (fix_doc[1] != "corrupted") {
+      article_id_os_open <- append(article_id_os_open, article_id[r])
+    }
+    close(open_file)
+  }
+}
+
+final_txt_file <- "royal_society_pdf_files\\OS_pdf_list.txt" #used for open science
+
+#######################Storing the new list of not corrupted pdf files###########################
+sink(final_txt_file)
+for (i in 1:length(article_id_os_open)){
+  cat(article_id_os_open[i])
+  cat("\n")
+}
+sink()

### 2019-10-19 download_RSOB_pdf.R

@@ -30,7 +30,7 @@ readUrl <- function(url, destfile1) {
 #########################list of article id's#####################################
 article_id <- vector()
 
-path <- "scopus_export_rsos.csv" #used for downloading the pdf's from open biology (list with the open biology ID's)
+path <- "scopus_export_rsob.csv" #used for downloading the pdf's from open biology (list with the open biology ID's)
 
 conn <- file(path,open="r")
 scopus_data <-  read.csv(path, stringsAsFactors = FALSE)
@@ -40,16 +40,21 @@ close(conn)
 ########################downloading the pdf's#####################################
 #this section is used for downloading the pdf files.
 sleep <- function() { Sys.sleep(30) } #needed to prevent an IP block from the royal society website
-i<-1
+
 for (i in 1:length(article_id)) {
   sleep()
-  #article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
-  article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
+  article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
+  #article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
   
-  #url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="") #for biology
-  url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsos.", article_id[i], "&file=rsos", article_id[i], "_review_history.pdf", sep="")
+  url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="") #for biology
+  #url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsos.", article_id[i], "&file=rsos", article_id[i], "_review_history.pdf", sep="")
   destfile1 <- paste("royal_society_pdf_files\\open_science\\review", article_id[i], ".pdf", sep="")
   #download.file(url, destfile=destfile1 , mode="wb")
   readUrl(url, destfile1)
   print(article_id[i])
 }
+
+
+##CHeck
[…]

### 2019-10-19 royal_society_open_biology_create_txt.R

@@ -7,36 +7,12 @@ library(stringr)
 library(tm)
 
 #########################list of article id's#####################################
-article_id <- vector()
-
-#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open biology (list with the open biology ID's)
-#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
-path <- "royal_society_pdf_files/OB_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open biology are contained
-#path <- "royal_society_pdf_files/OS_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open science are contained
-
-conn <- file(path,open="r")
-article_id <- readLines(conn)
-close(conn)
-
-########################downloading the pdf's#####################################
-##this section is used for downloading the pdf files.
-# sleep <- function() { Sys.sleep(20) } #needed to prevent an IP block from the royal society website
-# 
-#  for (i in 1:length(article_id)) {
-#    sleep()
-#    article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
-#    #article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
-#    
-#    url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="")
-#    destfile1 <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", article_id[i], ".pdf", sep="")
-#    download.file(url, destfile=destfile1 , mode="wb")
-#    }
+article_id <- readLines(file("royal_society_pdf_files/OB_pdf_list.txt", open = "r"))
 
 ########################Reading pdf file #########################################
 for (i in 1:length(article_id)) {
   pdf_file <- paste("royal_society_pdf_files/open_biology/review", article_id[i], ".pdf", sep="") #map with open biology pdf's
-  #pdf_file <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Science\\review", article_id[i], ".pdf", sep="") #map with open science pdf's
-  
+  print(article_id)
   if (file.exists(pdf_file)){
[…]

### 2019-10-19 royal_society_open_science_create_txt.R

@@ -7,35 +7,12 @@ library(stringr)
 library(tm)
 
 #########################list of article id's#####################################
-article_id <- vector()
-
-#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open biology (list with the open biology ID's)
-#path <- "royal_society_pdf_files/Article_ID_OB.txt" #used for downloading the pdf's from open science (list with the open biology ID's)
-#path <- "royal_society_pdf_files/OB_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open biology are contained
-path <- "royal_society_pdf_files/OS_pdf_list.txt" #uses list in which the non-corrupted pdf id's of open science are contained
-
-conn <- file(path,open="r")
-article_id <- readLines(conn)
-close(conn)
-
-########################downloading the pdf's#####################################
-##this section is used for downloading the pdf files.
-# sleep <- function() { Sys.sleep(20) } #needed to prevent an IP block from the royal society website
-# 
-#  for (i in 1:length(article_id)) {
-#    sleep()
-#    article_id[i] <- gsub("10.1098/rsob.", "", article_id[i])  #used for open biology
-#    #article_id[i] <- gsub("10.1098/rsos.", "", article_id[i]) #used for open science
-#    
-#    url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="")
-#    destfile1 <- paste("C:\\Users\\Nino9000\\Documents\\BEP Open Peer Review\\PDF_Files\\Open Biology\\review", article_id[i], ".pdf", sep="")
-#    download.file(url, destfile=destfile1 , mode="wb")
-#    }
+article_id <- readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r"))
 
 ########################Reading pdf file #########################################
 for (i in 1:length(article_id)) {
   pdf_file <- paste("royal_society_pdf_files/open_science/review", article_id[i], ".pdf", sep="") #map with open science pdf's
-  
+  print(article_id)
   if (file.exists(pdf_file)){
   read <- readPDF(control = list(text = "-layout"))
   document <- Corpus(URISource(pdf_file), readerControl = list(reader = read))

### 2019-10-19 textmining_open_biology.R

@@ -1,7 +1,4 @@
 ###Notes###
-library(dplyr)
-library(tidytext)
-library(tm)
 library(stringr)
 options(max.print=9999999) #allows the console to output more lines
 
@@ -12,7 +9,7 @@ df_days <- c()
 df_version <- c()
 df_recommendation <- c()
 df_word_count <- c()
-df_masked <- c()
+df_anonymous <- c()
 df_reviewer_name <- c()
 df_reviewer_number <- c()
 df_id <- c()
@@ -44,11 +41,11 @@ for (r in 1:length(article_id)){
 
                                            ######variables######
 
-###########################Masked, Version, recommendation, days and word count###################################
+###########################anonymous, Version, recommendation, days and word count###################################
     
     recommendation <- vector()
     recommendation_count <- 1
-    masked <- vector()
+    anonymous <- vector()
     author_count <- 1
     version <- vector()
     version_count <- 1
@@ -166,13 +163,19 @@ for (r in 1:length(article_id)){
         reviewer_number <- append(reviewer_number, str_sub(lines[i+1], 23, 23))  #Save author name (or Reviewer name)
         
         if (str_sub(lines[i+1], 14, 24) == "Reviewer 1"){
-          masked <- append(masked, 1)
+          anonymous <- append(anonymous, 1)
         } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 2"){
-          masked <- append(masked, 1)
+          anonymous <- append(anonymous, 1)
         } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 3"){
-          masked <- append(masked, 1)
+          anonymous <- append(anonymous, 1)
+        } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 4"){
+          anonymous <- append(anonymous, 1)
+        } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 5"){
+          anonymous <- append(anonymous, 1)
+        } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 6"){
+          anonymous <- append(anonymous, 1)
         } else {
-          masked <- append(masked, 0)
+          anonymous <- append(anonymous, 0)
         }
         author_count = author_count + 1
       }
@@ -211,7 +214,7 @@ for (r in 1:length(article_id)){
         df_version <- append(df_version, version[i])
         df_recommendation <- append(df_recommendation, recommendation[i])
         df_word_count <- append(df_word_count, word_count[i])
[…]

### 2019-10-19 textmining_open_science.R

@@ -1,7 +1,4 @@
 ###Notes###
-library(dplyr)
-library(tidytext)
-library(tm)
 library(stringr)
 options(max.print=9999999) #allows the console to output more lines
 
@@ -12,7 +9,7 @@ df_days <- c()
 df_version <- c()
 df_recommendation <- c()
 df_word_count <- c()
-df_masked <- c()
+df_anonymous <- c()
 df_reviewer_name <- c()
 df_reviewer_number <- c()
 df_id <- c()
@@ -42,11 +39,11 @@ for (r in 1:length(article_id)){
     
     ######variables######
     
-    ###########################Masked, Version, recommendation, days and word count###################################
+    ###########################anonymous, Version, recommendation, days and word count###################################
     
     recommendation <- vector()
     recommendation_count <- 1
-    masked <- vector()
+    anonymous <- vector()
     author_count <- 1
     version <- vector()
     version_count <- 1
@@ -137,13 +134,19 @@ for (r in 1:length(article_id)){
         reviewer_number <- append(reviewer_number, str_sub(lines[i+1], 23, 23))  #Save author name (or Reviewer name)
         
         if (str_sub(lines[i+1], 14, 24) == "Reviewer 1"){
-          masked <- append(masked, 1)
+          anonymous <- append(anonymous, 1)
         } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 2"){
-          masked <- append(masked, 1)
+          anonymous <- append(anonymous, 1)
         } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 3"){
-          masked <- append(masked, 1)
+          anonymous <- append(anonymous, 1)
+        } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 4"){
+          anonymous <- append(anonymous, 1)
+        } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 5"){
+          anonymous <- append(anonymous, 1)
+        } else if (str_sub(lines[i+1], 14, 24) == "Reviewer 6"){
+          anonymous <- append(anonymous, 1)
         } else {
-          masked <- append(masked, 0)
+          anonymous <- append(anonymous, 0)
         }
         author_count = author_count + 1
       }
@@ -181,7 +184,7 @@ for (r in 1:length(article_id)){
         df_version <- append(df_version, version[i])
         df_recommendation <- append(df_recommendation, recommendation[i])
[…]

### 2019-10-19 textmining_peerj.R

@@ -14,7 +14,7 @@ df_days <- c()
 df_version <- c()
 df_recommendation <- c()
 df_word_count <- c()
-df_masked <- c()
+df_anonymous <- c()
 df_reviewer_name <- c()
 df_id <- c()
 open_reviews <- 0
@@ -47,55 +47,44 @@ for (r in 1:7223){ #starting the loop to create the dataframe from the 6800 Peer
     ###############################Word count, positive and negative###############################################
     
     word_count <- vector()  #Vector that contains the wordcounts
-    review_count <- 1        #Counts which review is being counted
+    review_count <- 0        #Counts which review is being counted
     x <- 0                  #counter for word_count position
-    switch_review_count <- 0
-    
+
     # PeerJ subdivides the review in 4 sections: 
     # Basic reporting (under label_br), experimental design (label_ed), 
     # validity of findings (label_votf), and comments for the authors (label_cfta)
     # We add the words for all these sections under word count.
     # 
     for (i in 1:length(lines)){
-      if(lines[i] == paste("label_br_", review_count, sep="")){
+      if(lines[i] == paste("label_author_", review_count + 1, sep = "")){
+        review_count <- review_count + 1
         x = x + 1
+      }
+      
+      if(lines[i] == paste("label_br_", review_count, sep="")){
         word_count[x] <- 0
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
-        review_count <- review_count + 1
-        switch_review_count <- 1
       }
       
       if(lines[i] == paste("label_ed_", review_count, sep="")){
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
-        if (switch_review_count == 0) {
-          review_count <- review_count + 1
-          switch_review_count <- 1
-        }
       }
       
       if(lines[i] == paste("label_votf_", review_count, sep="")){
         word_count[x] <- word_count[x] + sapply(gregexpr("[[:alnum:]]+", lines[i+1]), function(x) sum(x > 0))
-        if (switch_review_count == 0) {
-          review_count <- review_count + 1
-          switch_review_count <- 1
-        }
       }
       
       if(lines[i] == paste("label_cfta_", review_count, sep="")){
[…]

### 2019-10-20 open_peer_review.Rmd
first draft

@@
 ---
-title             : "The Proportion of Signed Open Reviews Depends on the Recommendation"
-shorttitle        : "Recommendation Dependent Signing"
+title             : "Researchers Decision to Sign is Related to Their Recommendation"
+shorttitle        : "Recommendation Relates to Signing"
 author: 
-  - name          : "Daniel Lakens"
+  - name          : "Nino van Sambeek"
+    affiliation   : "1"
+  - name          : "Daniël Lakens"
     affiliation   : "1"
@@
     email         : "D.Lakens@tue.nl"
-  - name          : "Nino van Sambeek"
-    affiliation   : "1"
 affiliation:
@@
 abstract: |
-  Open Peer Review is becoming increasingly common, and when reviewers decide whether or not to sign, they take their recommendation into account.
+ Open review is becoming increasingly common.
+Surveys indicate that researchers are generally positive about making peer reviews available.
+Researchers are more negative about revealing the identity of reviewers.
+In part this is because of the possibility that reviewers will be less likely to express criticisms if their identity is known to authors.
+Experiments suggest that reviewers might be somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
+So far, there is surprisingly little information about what reviewers actually do in practice.
+We analyzed XXXX open reviews in PeerJ and XXXX reviews in the Royal Society Open Science and Open Biology to examine whether in practice the propability that a reviewer reveals their identity is related to their recommendation.
+When comparing XXXX signed and XXXX unsigned reviews, we observed a clear pattern where the more positive a recommendation, the more likely it was signed.
+Although our data does not allow for inferences about causal relationships, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
 
@@
 open_review_TRS <- length(OS_pdf_list) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
-# In this blog Royal Society says around 2/3 of reviews are published alongside the article in 2017: http://blogs.royalsociety.org/publishing/publication-of-peer-review-reports/ 
-TRS_2017 <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
-TRS_2017 <- filter(TRS_2017, str_sub(TRS_2017$DOI, -6) > 170000 & str_sub(TRS_2017$DOI, -6) < 180000)
 
-TRS_2017_open <- OS_pdf_list[OS_pdf_list > 170000 & OS_pdf_list < 180000]
-# Seems close - I am not excluding corrections (that have no peer review history), I think the blog post is. 
-length(TRS_2017_open)/nrow(TRS_2017)
+# How many entries in RSOS in total? Read in scopus datafile
+TRS_scopus_OS <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
+table(TRS_scopus_OS$Document.Type)
+# Excude Errata and Editorial (that have no reviews)
+TRS_scopus_OS <- TRS_scopus_OS[!TRS_scopus_OS$Document.Type == "Erratum" & !TRS_scopus_OS$Document.Type == "Editorial",]
+table(TRS_scopus_OS$Document.Type)
 
-# open_review_TRS <- length(length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI))>170000 & readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r")<180000)) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
+# How many entries in RSOS in total? Read in scopus datafile
+TRS_scopus_OB <- read.csv("scopus_export_rsob.csv", stringsAsFactors = FALSE)
+table(TRS_scopus_OB$Document.Type)
+# Excude Errata and Editorial (that have no reviews)
+TRS_scopus_OB <- TRS_scopus_OB[!TRS_scopus_OB$Document.Type == "Erratum" & !TRS_scopus_OB$Document.Type == "Editorial" & !TRS_scopus_OB$Document.Type == "Retracted",]
+table(TRS_scopus_OB$Document.Type)
 
-XXX <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
 # One submission to PeerJ was accepted but no reviewer info. It means they are accepted by the editor? Or just an early mistake.
@@
 
-# # Using data.table command
-# group <- as.data.table(PeerJ_data)
-# TEST <- group[group[, .I[df_version == max(df_version)], by=df_link]$V1]
-
-# Select only those reviews for each paper with the highest version (first review)
+# Select only those reviews for each paper with the highest version for PeerJ (first review)
 PeerJ_data_R1 <- group_by(PeerJ_data, df_link)
@@
 
+# Do the same for TRS
 TRS_data_R1 <- group_by(TRS_data, df_link)
 TRS_data_R1 <- top_n(TRS_data_R1, 1, df_version)
-
-TRS_review_agree <- group_by(TRS_data_R1, df_link)
-unique(TRS_review_agree$df_recommendation)
 
@@
 
-In a previous study where researchers were randomly assigned to a condition where their reviews would be signed, or not signed [@walsh_open_2000], reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51).
+As technology advances, science advances.
+The rise of the internet has made it possible to share all aspects of the scientific process.
+This includes opening up the peer review process.
+An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve the peer review process [@bruce_impact_2016].
+Having access to these peer review reports makes it possible to gain new insights about how scientists perform reviews.
+
+Some journals have chosen to not just share reviews publicly when an article is published, but in addition require reviewers to sign their reviews.
+An important argument for such a policy is that reviewers can receive credit for their work [@godlee_making_2002].
+However, scientists do not feel these benefits outweigh possible costs.
+Researchers indicate they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers [@mulligan_peer_2013].
+A more recent survey among almost 3000 scientists found that 50.8% of reviewers believe signed open reviews would make peer review worse [@ross-hellauer_survey_2017].
+Almost two-thirds of respondents believed reviewers would be less likely to deliver strong criticisms if their identity became known to the authors.
+
+These self-report studies are complemented by experiments in which reviewers are been randomly assigned to a condition where their names would be added to their reviews or not [@walsh_open_2000].
+Reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51).
 This suggests that a causal effect exists between knowing your name will be known or not and the recommendation reviewers provide.
-Another study that randomly assigned reviewers to a condition where reviewer names would be shared alongside the reviews or a control condition did not find differences between recommendations that were made, but in this study a much larger percentage of reviewers (55%) declined to participate in the trial, raising the possibility of self-selection of participants [@rooyen_effect_2010].
-Reviewers indicate they are less likely to review for a journal if their names will be made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers [@mulligan_peer_2013].
-A more recent large survey among almost 3000 scientists found that 50.8% of reviewers believe signed open reviews would make peer review worse, with almost two-thirds of respondents indicating they believed reviewers would be less likely to devliver strong criticisms if their identity became known to the authors [@ross-hellauer_survey_2017].
+Across four studies, a meta-analysis by Bruce and colleagues (2016) supports the conclusion that reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
 
-## Accessing Open Peer Reviews
+Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to highly critical reviews, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
+The trade-off between the benefit of getting credit for peer review work and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the most positive their recommendation is.
+If this strategic behavior occurs in practice, we should see a different pattern of recommendations for signed and unsigned reviews.
+One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, Journal of Hydrology: Regional Studies, and the International Journal of Surgery [@bravo_effect_2019].
+Although only 8.1% of reviewers choose to disclose their identity in these reviews, but the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
+Here, we examine this pattern in two large open access journals that publish across a wide range of scientific disciplines.
+In this replication and extension of the analysis by Bravo and colleagues (2019) we examine the relationship between recommendations and signed reviews in open peer reviews in mega-journals that publish scientific work across a wide range of scientific disciplines.
 
-PeerJ assigns all articles a number from 1, increasing consecutively with each published manuscript.
-Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article).
-Using text-mining tools in R (cite R, RCurl, XML, stringer) we downloaded all reviews and stored them as individual text files.
+# Accessing Open Peer Reviews
+
+To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles published in The Royal Society Open Science and Open Biology, and 7223 articles published in PeerJ.
+PeerJ launched in 2012 and gave reviewers the possibility to sign, and authors to make the peer reviews available with the final publication.
+The Royal Society Open science launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication.
+Royal Society Open Biology made sharing reviews with the final publication mandatory in 2017.
+Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, these reviews provide insights into the peer review behavior of scientists across a wide range of disciplines.
+
+PeerJ assigns all articles a number, increasing consecutively with each published manuscript.
+Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article can be found).
 Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files.
-A list of the DOI for every article published in these two outlets was retrieved through Scopus.
+A list of Digital Object Identifiers (DOIs) for every article published in these two outlets was retrieved through Scopus.
 All reviews were downloaded, and the PDF files were exported to plain text files using pdftools [@ooms_pdftools_2019].
-Text files were textmined using the stringr package [@wickham_stringr_2019].
+These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package [@wickham_stringr_2019].
 
-For each article we extracted the nuber of revisions, and for each revision we saved for each reviewer whether the reviewer signed the review or not, the word count for their review, and the recommendation for that review round.
+For each article we extracted the number of revisions, and for each revision we saved for each review whether the reviewer signed or not, the word count for their review, and the recommendation for that review round.
 Note that for PeerJ recommendations each round are giving by the editor.
-We therefore do not directly know which recommendation each reviewer provided.
+We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
 For RSOS and RSOB reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
 Although 'reject' recommendations occur for RSOS and RSOB, both PeerJ and RSOS and RSOB only share reviews for published articles, and therefore we have very few reject recommendation in RSOS and RSOB, and none in PeerJ.
-Searching all text files for PeerJ for 'appealed on' reveals 44 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
+Searching all reviews for PeerJ for the words 'appealed on' reveals 44 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
 We have coded these papers as 'major revisions'.
-We also extracted the names of all reviewers when they signed, and calculated the days each manuscript was under peer review from initial submission to acceptance for publication.
+All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at https://osf.io/jkbmw/.
 
-## Peer Review Reports
+# Peer Review Reports
 
-PeerJ provides authors the option to reproduce the complete peer review history of their article alongside the final publication of the article. 
+PeerJ provides authors the option to publish the peer reviews of their article alongside the final publication of the article.
 The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science).
@@
 
-We examined the first 7223 articles pubished in PeerJ, as well as the first `r length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)` articles in RSOS and the first `r length(read.csv("scopus_export_rsob.csv", stringsAsFactors = FALSE)$DOI)` articles in RSOB.
-We retrieved reviews for `r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique_os)` articles in RSOS, and `r nrow(TRS_unique_ob)` articles in RSOB.
-WE NEED TO REMOVE CORRECTIONS FROM THE NUMBERS ABOVE.
+We examined the first 7223 articles pubished in PeerJ, as well as the first `r length(TRS_scopus_OS$DOI)` articles in RSOS and the first `r length(TRS_scopus_OB$DOI)` articles in RSOB.
+We retrieved all reviews for all review rounds of `r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique_os)` articles in RSOS, and `r nrow(TRS_unique_ob)` articles in RSOB.
 Articles can go through multiple rounds of review.
-We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision.
+We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following [@bravo_effect_2019].
 On average initial submissions at PeerJ received `r round(mean(count(PeerJ_data_R1, df_link)$n), 2)` reviews.
@@
 
-## Signed reviews as a function of the recommendation
+# Signed reviews as a function of the recommendation
 
-When analzing all reviews of original submissions in PeerJ `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their reviews and `r sum(PeerJ_data_R1$df_anonymous == 1)` did not.
+When analyzing all reviews of original submissions in PeerJ `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their reviews and `r sum(PeerJ_data_R1$df_anonymous == 1)` did not.
 In The Royal Society journals `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their first review while `r sum(TRS_data_R1$df_anonymous == 1)` did not.
-The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for the Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed only the first 1214 articles published in PeerJ.
+The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for the Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed the first 1214 articles published in PeerJ.
 
@@
 # plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
-#                    c("anonymous", "anonymous", "anonymous", "not anonymous", "not anonymous", "not anonymous"),
+#                    c("unsigned", "unsigned", "unsigned", "signed", "signed", "signed"),
 #                    c(PeerJ_anonymous_by_recommendation, PeerJ_notanonymous_by_recommendation))
@@
                                ,
-                   c("anonymous", "anonymous", "not anonymous", "not anonymous"),
+                   c("unsigned", "unsigned", "signed", "signed"),
                    c(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]))
@@
 
-Since these data are correlational we can not draw causal conclusions.
-It is possible that reviewers are less likely to sign more negative reviews.
-It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
-Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-
-# Additional Analyses
-
-Open reviews make it possible to examine additional interesting questions.
-The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, and the names of reviewers who signed their review.
-Through the DOI, researchers can link this data to, for example, citation counts for each manuscript.
-This makes it possible to explore whether initial evaluations of a manuscript are related to future citations counts.
-By manually coding which career stage authors and reviewers belong to during the review process it is possible to gain insights into who is more likely practice open science.
-It is possible to extract information about the time between submission and acceptance for each article (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for RSOS and RSOB).
-Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.
-
-For example, since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, we can see how often reviewers agree.
-For the `r sum(table(rev_dif))` individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in `r table(rev_dif)[1]` (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`%) of the time.
-For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
-There were `r sum(TRS_review_agree$df_unique == 4)` articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
-
-Regrettably, neither PeerJ nor RSOS make peer reviews available for manuscripts that were rejected.
-As a consequence, we have analyzed a biased sample of the literature.
-At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
-Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at specific journals.
-
 ```{r, TRSrec, fig.cap = "Frequencies of signed and unsigned reviews as a function of whether the reviewer at the Royal Society Open Science and Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
@@
 plot_data <- data.frame(factor(c("accept", "minor", "major", "reject", "accept", "minor", "major", "reject"), levels = c("accept", "minor", "major", "reject")),
-                   c("anonymous", "anonymous", "anonymous", "anonymous", "not anonymous", "not anonymous", "not anonymous", "not anonymous"),
+                   c("unsigned", "unsigned", "unsigned", "unsigned", "signed", "signed", "signed", "signed"),
                    c(TRS_anonymous_by_recommendation, TRS_notanonymous_by_recommendation))
@@
 # plot_data <- data.frame(c("minor revision", "major revision", "minor revision", "major revision"),
-#                    c("anonymous", "anonymous", "not anonymous", "not anonymous"),
+#                    c("unsigned", "unsigned", "signed", "signed"),
 #                    c(TRS_anonymous_by_recommendation[2:3], TRS_notanonymous_by_recommendation[2:3]))
@@
 
-```{r}
+Since these data are correlational we can not draw causal conclusions.
+It is possible that reviewers are less likely to sign more negative reviews.
+It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
+Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
+Our results replicate the observations by Bravo and colleagues (2019).
+
+# Additional Analyses
+
+The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for RSOS and RSOB).
+Through the DOI, researchers can link this data to other sources of information such as citation counts.
+Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.
+For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
+With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (@wang_open_2016) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews.
+
+```{r wordcount}
+# Word counts PeerJ
+
+# words <- by(PeerJ_data_R1$df_word_count, PeerJ_data_R1[,c(5,7)], mean, simplify = TRUE)
+# 
+# plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
+#                    c("signed", "signed", "signed", "unsigned", "unsigned", "unsigned"),
+#                    c(words))
+# colnames(plot_data) <- c("recommendation", "signed", "word count")
+# 
+# ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
+#   geom_bar(position="dodge", stat="identity") +
+#   theme_linedraw(base_size = 20)
+# 
+# ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
+#   geom_bar(position="dodge", stat="identity") +
+#   theme_linedraw(base_size = 20)
+# 
+# t.test(PeerJ_data_R1$df_word_count ~ PeerJ_data_R1$df_anonymous)
+
+# Words count RSOS
+#
+
+words <- by(TRS_data_R1$df_word_count, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)
+
+plot_data <- data.frame(factor(c("accept", "minor", "major", "reject", "accept", "minor", "major", "reject"), levels = c("accept", "minor", "major", "reject")),
+                   c("signed", "signed", "signed", "signed", "unsigned", "unsigned", "unsigned", "unsigned"),
+                   c(words))
+colnames(plot_data) <- c("recommendation", "signed", "wordcount")
+
+ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
+  geom_bar(position="dodge", stat="identity") +
+  theme_linedraw(base_size = 20) + 
+  theme(legend.position = "top",
+        legend.title=element_blank(),
+        panel.grid.major.x = element_blank()) + 
+  scale_fill_manual(values = c("#000000", "#808080")) + 
+  coord_cartesian(ylim = c(0, 750)) +
+  geom_text(aes(label = round(wordcount,0)), 
+              size = 6, 
+              color = "black",
+              position = position_dodge(width = 0.9),
+              vjust = -.5) +
+  labs(y = "word count")
+
+# When tested, the difference is not significant
+# t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)
+```
+
+Since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, one example of the insights open reviews provide is how often reviewers agree.
+For the `r sum(table(rev_dif))` individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in `r table(rev_dif)[1]` (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`%) of the time.
+For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
+There were `r sum(TRS_review_agree$df_unique == 4)` articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
+
+Regrettably, neither PeerJ nor RSOS make peer reviews available for manuscripts that were rejected.
+As a consequence, we have analyzed a biased sample of the literature.
+At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
+Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at specific journals.
+Despite this limitation, the pattern of results is very similar to that observed by Bravo and colleagues (2019) who had access to the reviews for accepted and rejected manuscripts.
+Thus, even though the proportion of reject recommendation in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datsets that include rejected manuscripts.
+
+# Discussion
+
+Our analysis shows that when authors are given the choice to sign their reviews, signed reviews have more positive recommendations than unsigned reviews.
+This is true for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
+The effect is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
+Our results replicate and extend earlier findings by @bravo_effect_2019, and complement self-report and experimental results.
+Although our results do not allow for causal claims, they are in line with experimental results that reveal researchers give more positive recommendations when their name is published alongside their reviews [@bruce_impact_2016].
+
+Open reviews allow researchers to adress meta-scientific questions that give insights into the peer review process.
+Our data provide further support for the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
+Our correlational data, interpreted together with self-report data and experiments in the literature, increases the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
+This type of strategic behavior also follows from a purely rational strategy to optimize the benefits of peer review while minimizing the costs.
+For positive recommendations, reviewers will get credit for theor reviews, while for negative reviews, they do not run the risk of receiving any backlash from collegaues in their field.
+
+It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation [@bastian_signing_2018].
+Althoughit looks increasingly plausible that at least some reviewers feel hesitant to sign if they believe doing so could have negative consequences, but are willing to sign to gain credit for their work for more positive recommendations, it seems wortwhile to explore ways in which they can receive credit for all their peer review work, also when their recommendations are more negative.
+If more journals share open reviews, also for rejected manuscripts, future meta-scientific work might be able to study this important topic in more detail.
+
+```{r, include = FALSE}
+# We can in principle report p-values for tests for proportions, but I don't think this adds omething to the manuscript.
+
 prop_data <- cbind(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]) #bind as matrix
@@
 
-```{r}
-# Word counts PeerJ
-
-words <- by(PeerJ_data_R1$df_word_count, PeerJ_data_R1[,c(5,7)], mean, simplify = TRUE)
-
-plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
-                   c("not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous"),
-                   c(words))
-colnames(plot_data) <- c("recommendation", "signed", "wordcount")
-
-ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
-  geom_bar(position="dodge", stat="identity") +
-  theme_linedraw(base_size = 20)
-
-ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
-  geom_bar(position="dodge", stat="identity") +
-  theme_linedraw(base_size = 20)
-
-ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
-  geom_jitter() +
-  theme_linedraw(base_size = 20)
-
-t.test(PeerJ_data_R1$df_word_count ~ PeerJ_data_R1$df_anonymous)
-
-```
-
-In Nino's BEP there were  3552 reviews in RSOS. I have 3629 after running all his code.
-
-Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
-What does this mean?
-
-Word counts are not perfectly reliable for several reasons (e.g., addition of references, but also more importantly comments in an attached pdf - maybe we can search for attached and pdf in short comments to identify these.
-)
-
-" This result is similar to the findings in Bornmann, Wolf,
-and Daniel (2012) that the comments in public peer review are much longer than
-the comments in closed peer review."
-
-## Future Research
-
-## NOTES
-
-Searching all text files of PeerJ for 'appealed on' reveals 44 articles that were initially appealed, and subsequently published. 
-From Nino's thesis for RSOS: "Interestingly, for 39 of the reviews we had
-access to (and were thus published) the final recommendation given by the editor is to reject the manuscript.
-For these articles to still get published, the author has to appeal the rejection and change the decision made by the editor."
-Not sure how he got this - my code does not suggest this.
-sum(PeerJ_data$df_recommendation == 4, na.rm = TRUE) # how many reviews for first submissions
-
-From Wang et al: " Of the 3,569 review reports, 85 were submitted as
-attachments in various formats (comments inserted to the manuscripts, PDF or Word
-DOC) or the reviews contained no substantive content such as “no further comments.”"
-
 # Author Contributions
@@
 van Sambeek and D.
-Lakens developed the idea.
-Both authors generated the R code to generate the data and anayze the results.
+Lakens developed the idea, and jointly created the R code to generate and analyze the data.
 N van Sambeek drafted the initial version of the manuscript as a Bachelor thesis, D.
-Lakens wrote the final version, both authors revised the manuscript.
+Lakens drafted the final version, and both authors revised the final version of the manuscript.
 
@@
 rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("anonymous", "not anonymous") #add row names
+colnames(prop_data) <- c("unsigned", "signed") #add row names
 
@@
 rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("anonymous", "notanonymous") #add row names
+colnames(prop_data) <- c("unsigned", "notanonymous") #add row names
 prop.test(prop_data) #perform test of proportions
@@
 plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
-                   c("not anonymous", "not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous", "anonymous"),
+                   c("signed", "signed", "signed", "signed", "unsigned", "unsigned", "unsigned", "unsigned"),
                    c(words))
@@
 plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
-                   c("not anonymous", "not anonymous", "not anonymous", "not anonymous", "anonymous", "anonymous", "anonymous", "anonymous"),
+                   c("signed", "signed", "signed", "signed", "unsigned", "unsigned", "unsigned", "unsigned"),
                    c(review_time))

### 2019-10-20 open_peer_review.tex
first draft

@@
 \hypersetup{unicode=true,
-            pdftitle={The Proportion of Signed Open Reviews Depends on the Recommendation},
-            pdfauthor={Daniel Lakens~\& Nino van Sambeek},
+            pdftitle={Researchers Decision to Sign is Related to Their Recommendation},
+            pdfauthor={Nino van Sambeek~\& Daniël Lakens},
             pdfkeywords={Peer Review, Open Science, Transparency},
@@
 
-  \title{The Proportion of Signed Open Reviews Depends on the Recommendation}
-    \author{Daniel Lakens\textsuperscript{1}~\& Nino van Sambeek\textsuperscript{1}}
+  \title{Researchers Decision to Sign is Related to Their Recommendation}
+    \author{Nino van Sambeek\textsuperscript{1}~\& Daniël Lakens\textsuperscript{1}}
     \date{}
 
-\shorttitle{Recommendation Dependent Signing}
+\shorttitle{Recommendation Relates to Signing}
 \affiliation{
@@
 
-Correspondence concerning this article should be addressed to Daniel Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
+Correspondence concerning this article should be addressed to Daniël Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
 
 \abstract{
-Open Peer Review is becoming increasingly common, and when reviewers decide whether or not to sign, they take their recommendation into account.
+Open review is becoming increasingly common.
+Surveys indicate that researchers are generally positive about making peer reviews available.
+Researchers are more negative about revealing the identity of reviewers.
+In part this is because of the possibility that reviewers will be less likely to express criticisms if their identity is known to authors.
+Experiments suggest that reviewers might be somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
+So far, there is surprisingly little information about what reviewers actually do in practice.
+We analyzed XXXX open reviews in PeerJ and XXXX reviews in the Royal Society Open Science and Open Biology to examine whether in practice the propability that a reviewer reveals their identity is related to their recommendation.
+When comparing XXXX signed and XXXX unsigned reviews, we observed a clear pattern where the more positive a recommendation, the more likely it was signed.
+Although our data does not allow for inferences about causal relationships, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
 
@@
 
-In a previous study where researchers were randomly assigned to a condition where their reviews would be signed, or not signed (Walsh, Rooney, Appleby, \& Wilkinson, 2000), reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51).
+As technology advances, science advances.
+The rise of the internet has made it possible to share all aspects of the scientific process.
+This includes opening up the peer review process.
+An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve the peer review process (Bruce, Chauvin, Trinquart, Ravaud, \& Boutron, 2016).
+Having access to these peer review reports makes it possible to gain new insights about how scientists perform reviews.
+
+Some journals have chosen to not just share reviews publicly when an article is published, but in addition require reviewers to sign their reviews.
+An important argument for such a policy is that reviewers can receive credit for their work (Godlee, 2002).
+However, scientists do not feel these benefits outweigh possible costs.
+Researchers indicate they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers (Mulligan, Hall, \& Raphael, 2013).
+A more recent survey among almost 3000 scientists found that 50.8\% of reviewers believe signed open reviews would make peer review worse (Ross-Hellauer, Deppe, \& Schmidt, 2017).
+Almost two-thirds of respondents believed reviewers would be less likely to deliver strong criticisms if their identity became known to the authors.
+
+These self-report studies are complemented by experiments in which reviewers are been randomly assigned to a condition where their names would be added to their reviews or not (Walsh, Rooney, Appleby, \& Wilkinson, 2000).
+Reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51).
 This suggests that a causal effect exists between knowing your name will be known or not and the recommendation reviewers provide.
-Another study that randomly assigned reviewers to a condition where reviewer names would be shared alongside the reviews or a control condition did not find differences between recommendations that were made, but in this study a much larger percentage of reviewers (55\%) declined to participate in the trial, raising the possibility of self-selection of participants (Rooyen, Delamothe, \& Evans, 2010).
-Reviewers indicate they are less likely to review for a journal if their names will be made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers (Mulligan, Hall, \& Raphael, 2013).
-A more recent large survey among almost 3000 scientists found that 50.8\% of reviewers believe signed open reviews would make peer review worse, with almost two-thirds of respondents indicating they believed reviewers would be less likely to devliver strong criticisms if their identity became known to the authors (Ross-Hellauer, Deppe, \& Schmidt, 2017).
+Across four studies, a meta-analysis by Bruce and colleagues (2016) supports the conclusion that reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
+
+Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to highly critical reviews, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
+The trade-off between the benefit of getting credit for peer review work and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the most positive their recommendation is.
+If this strategic behavior occurs in practice, we should see a different pattern of recommendations for signed and unsigned reviews.
+One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, Journal of Hydrology: Regional Studies, and the International Journal of Surgery (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
+Although only 8.1\% of reviewers choose to disclose their identity in these reviews, but the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
+Here, we examine this pattern in two large open access journals that publish across a wide range of scientific disciplines.
+In this replication and extension of the analysis by Bravo and colleagues (2019) we examine the relationship between recommendations and signed reviews in open peer reviews in mega-journals that publish scientific work across a wide range of scientific disciplines.
 
 \hypertarget{accessing-open-peer-reviews}{%
-\subsection{Accessing Open Peer Reviews}\label{accessing-open-peer-reviews}}
+\section{Accessing Open Peer Reviews}\label{accessing-open-peer-reviews}}
 
-PeerJ assigns all articles a number from 1, increasing consecutively with each published manuscript.
-Reviews are always accessible in html (i.e., at \url{https://peerj.com/articles/1/reviews} for the first article).
-Using text-mining tools in R (cite R, RCurl, XML, stringer) we downloaded all reviews and stored them as individual text files.
+To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 3576 articles published in The Royal Society Open Science and Open Biology, and 7223 articles published in PeerJ.
+PeerJ launched in 2012 and gave reviewers the possibility to sign, and authors to make the peer reviews available with the final publication.
+The Royal Society Open science launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication.
+Royal Society Open Biology made sharing reviews with the final publication mandatory in 2017.
+Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, these reviews provide insights into the peer review behavior of scientists across a wide range of disciplines.
+
+PeerJ assigns all articles a number, increasing consecutively with each published manuscript.
+Reviews are always accessible in html (i.e., at \url{https://peerj.com/articles/1/reviews} for the first article can be found).
 Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files.
-A list of the DOI for every article published in these two outlets was retrieved through Scopus.
+A list of Digital Object Identifiers (DOIs) for every article published in these two outlets was retrieved through Scopus.
 All reviews were downloaded, and the PDF files were exported to plain text files using pdftools (Ooms, 2019).
-Text files were textmined using the stringr package (Wickham, 2019).
+These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package (Wickham, 2019).
 
-For each article we extracted the nuber of revisions, and for each revision we saved for each reviewer whether the reviewer signed the review or not, the word count for their review, and the recommendation for that review round.
+For each article we extracted the number of revisions, and for each revision we saved for each review whether the reviewer signed or not, the word count for their review, and the recommendation for that review round.
 Note that for PeerJ recommendations each round are giving by the editor.
-We therefore do not directly know which recommendation each reviewer provided.
+We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
 For RSOS and RSOB reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
 Although \enquote{reject} recommendations occur for RSOS and RSOB, both PeerJ and RSOS and RSOB only share reviews for published articles, and therefore we have very few reject recommendation in RSOS and RSOB, and none in PeerJ.
-Searching all text files for PeerJ for \enquote{appealed on} reveals 44 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
+Searching all reviews for PeerJ for the words \enquote{appealed on} reveals 44 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
 We have coded these papers as \enquote{major revisions}.
-We also extracted the names of all reviewers when they signed, and calculated the days each manuscript was under peer review from initial submission to acceptance for publication.
+All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at \url{https://osf.io/jkbmw/}.
 
 \hypertarget{peer-review-reports}{%
-\subsection{Peer Review Reports}\label{peer-review-reports}}
+\section{Peer Review Reports}\label{peer-review-reports}}
 
-PeerJ provides authors the option to reproduce the complete peer review history of their article alongside the final publication of the article.
+PeerJ provides authors the option to publish the peer reviews of their article alongside the final publication of the article.
 The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science).
@@
 
-We examined the first 7223 articles pubished in PeerJ, as well as the first 2949 articles in RSOS and the first 708 articles in RSOB.
-We retrieved reviews for 4555 articles in PeerJ, 1412 articles in RSOS, and 148 articles in RSOB.
-WE NEED TO REMOVE CORRECTIONS FROM THE NUMBERS ABOVE.
+We examined the first 7223 articles pubished in PeerJ, as well as the first 2887 articles in RSOS and the first 689 articles in RSOB.
+We retrieved all reviews for all review rounds of 4555 articles in PeerJ, 1412 articles in RSOS, and 148 articles in RSOB.
 Articles can go through multiple rounds of review.
-We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision.
+We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following (Bravo et al., 2019).
 On average initial submissions at PeerJ received 2.36 reviews.
@@
 \hypertarget{signed-reviews-as-a-function-of-the-recommendation}{%
-\subsection{Signed reviews as a function of the recommendation}\label{signed-reviews-as-a-function-of-the-recommendation}}
+\section{Signed reviews as a function of the recommendation}\label{signed-reviews-as-a-function-of-the-recommendation}}
 
-When analzing all reviews of original submissions in PeerJ 4172 reviewers signed their reviews and 6569 did not.
+When analyzing all reviews of original submissions in PeerJ 4172 reviewers signed their reviews and 6569 did not.
 In The Royal Society journals 1261 reviewers signed their first review while 2150 did not.
-The percentages of people who sign (38.84\% for PeerJ, 36.97\% for the Royal Society) are slightly lower than the 43.23\% reported by (Wang, You, Manasa, \& Wolfram, 2016), who analyzed only the first 1214 articles published in PeerJ.
+The percentages of people who sign (38.84\% for PeerJ, 36.97\% for the Royal Society) are slightly lower than the 43.23\% reported by (Wang, You, Manasa, \& Wolfram, 2016), who analyzed the first 1214 articles published in PeerJ.
 
@@
 
-Since these data are correlational we can not draw causal conclusions.
-It is possible that reviewers are less likely to sign more negative reviews.
-It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
-Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-
-\hypertarget{additional-analyses}{%
-\section{Additional Analyses}\label{additional-analyses}}
-
-Open reviews make it possible to examine additional interesting questions.
-The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, and the names of reviewers who signed their review.
-Through the DOI, researchers can link this data to, for example, citation counts for each manuscript.
-This makes it possible to explore whether initial evaluations of a manuscript are related to future citations counts.
-By manually coding which career stage authors and reviewers belong to during the review process it is possible to gain insights into who is more likely practice open science.
-Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.
-
-For example, since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, we can see how often reviewers agree.
-For the 1559 individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in 646 (41.44\%) of the time.
-For 42.14\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.69\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.73\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
-There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
-
-The average time between submission and acceptance for PeerJ for the articles open reviews are available for was 112 days, and for the Royal Society this was 133 days.
-
 \begin{figure}
@@
 
-\begin{verbatim}
-## 
-##  2-sample test for equality of proportions with continuity
-##  correction
-## 
-## data:  prop_data
-## X-squared = 142.6, df = 1, p-value < 2.2e-16
-## alternative hypothesis: two.sided
-## 95 percent confidence interval:
-##  -0.1369924 -0.0978543
-## sample estimates:
-##    prop 1    prop 2 
-## 0.5362998 0.6537231
-\end{verbatim}
+Since these data are correlational we can not draw causal conclusions.
+It is possible that reviewers are less likely to sign more negative reviews.
+It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
+Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
+Our results replicate the observations by Bravo and colleagues (2019).
 
-\begin{verbatim}
-## [1] 0.6000000 0.5362998 0.6537231
-\end{verbatim}
+\hypertarget{additional-analyses}{%
+\section{Additional Analyses}\label{additional-analyses}}
 
-\includegraphics{open_peer_review_files/figure-latex/unnamed-chunk-3-1.pdf}
+The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, the names of reviewers who signed their review, and the time in review (112 days for PeerJ, 133 days for RSOS and RSOB).
+Through the DOI, researchers can link this data to other sources of information such as citation counts.
+Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.
+For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
+With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (Wang et al.
+(2016)) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews.
 
-\begin{verbatim}
-## Warning: Removed 2 rows containing missing values (geom_bar).
-\end{verbatim}
+\includegraphics{open_peer_review_files/figure-latex/wordcount-1.pdf}
 
-\includegraphics{open_peer_review_files/figure-latex/unnamed-chunk-3-2.pdf}
+Since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, one example of the insights open reviews provide is how often reviewers agree.
+For the 1559 individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in 646 (41.44\%) of the time.
+For 42.14\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.69\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.73\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
+There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
 
-\begin{verbatim}
-## Warning: Removed 2 rows containing missing values (geom_point).
-\end{verbatim}
+Regrettably, neither PeerJ nor RSOS make peer reviews available for manuscripts that were rejected.
+As a consequence, we have analyzed a biased sample of the literature.
+At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
+Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at specific journals.
+Despite this limitation, the pattern of results is very similar to that observed by Bravo and colleagues (2019) who had access to the reviews for accepted and rejected manuscripts.
+Thus, even though the proportion of reject recommendation in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datsets that include rejected manuscripts.
 
-\includegraphics{open_peer_review_files/figure-latex/unnamed-chunk-3-3.pdf}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
-\begin{verbatim}
-## 
-##  Welch Two Sample t-test
-## 
-## data:  PeerJ_data_R1$df_word_count by PeerJ_data_R1$df_anonymous
-## t = 4.3438, df = 8046.6, p-value = 1.418e-05
-## alternative hypothesis: true difference in means is not equal to 0
-## 95 percent confidence interval:
-##  21.25429 56.21419
-## sample estimates:
-## mean in group 0 mean in group 1 
-##        481.1711        442.4369
-\end{verbatim}
+Our analysis shows that when authors are given the choice to sign their reviews, signed reviews have more positive recommendations than unsigned reviews.
+This is true for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
+The effect is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
+Our results replicate and extend earlier findings by Bravo et al.
+(2019), and complement self-report and experimental results.
+Although our results do not allow for causal claims, they are in line with experimental results that reveal researchers give more positive recommendations when their name is published alongside their reviews (Bruce et al., 2016).
 
-In Nino's BEP there were 3552 reviews in RSOS. I have 3629 after running all his code.
+Open reviews allow researchers to adress meta-scientific questions that give insights into the peer review process.
+Our data provide further support for the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
+Our correlational data, interpreted together with self-report data and experiments in the literature, increases the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
+This type of strategic behavior also follows from a purely rational strategy to optimize the benefits of peer review while minimizing the costs.
+For positive recommendations, reviewers will get credit for theor reviews, while for negative reviews, they do not run the risk of receiving any backlash from collegaues in their field.
 
-Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
-What does this mean?
-
-Word counts are not perfectly reliable for several reasons (e.g., addition of references, but also more importantly comments in an attached pdf - maybe we can search for attached and pdf in short comments to identify these.
-)
-
-" This result is similar to the findings in Bornmann, Wolf,
-and Daniel (2012) that the comments in public peer review are much longer than
-the comments in closed peer review."
-
-\hypertarget{future-research}{%
-\subsection{Future Research}\label{future-research}}
-
-\hypertarget{notes}{%
-\subsection{NOTES}\label{notes}}
-
-Searching all text files of PeerJ for \enquote{appealed on} reveals 44 articles that were initially appealed, and subsequently published.
-From Nino's thesis for RSOS: \enquote{Interestingly, for 39 of the reviews we had
-access to (and were thus published) the final recommendation given by the editor is to reject the manuscript.
-For these articles to still get published, the author has to appeal the rejection and change the decision made by the editor.}
-Not sure how he got this - my code does not suggest this.
-sum(PeerJ\_data\$df\_recommendation == 4, na.rm = TRUE) \# how many reviews for first submissions
-
-From Wang et al: " Of the 3,569 review reports, 85 were submitted as
-attachments in various formats (comments inserted to the manuscripts, PDF or Word
-DOC) or the reviews contained no substantive content such as \enquote{no further comments.}"
+It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation (Bastian, 2018).
+Althoughit looks increasingly plausible that at least some reviewers feel hesitant to sign if they believe doing so could have negative consequences, but are willing to sign to gain credit for their work for more positive recommendations, it seems wortwhile to explore ways in which they can receive credit for all their peer review work, also when their recommendations are more negative.
+If more journals share open reviews, also for rejected manuscripts, future meta-scientific work might be able to study this important topic in more detail.
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-bastian_signing_2018}{}%
+Bastian, H.
+(2018).
+Signing Critical Peer Reviews \& the Fear of Retaliation: What Should We Do?
+\textbar{} Absolutely Maybe.
+https://blogs.plos.org/absolutely-maybe/2018/03/22/signing-critical-peer-reviews-the-fear-of-retaliation-what-should-we-do/.
+
+\leavevmode\hypertarget{ref-bravo_effect_2019}{}%
+Bravo, G., Grimaldo, F., López-Iñesta, E., Mehmani, B., \& Squazzoni, F.
+(2019).
+The effect of publishing peer review reports on referee behavior in five scholarly journals.
+\emph{Nature Communications}, \emph{10}(1), 1--8.
+doi:\href{https://doi.org/10.1038/s41467-018-08250-2}{10.1038/s41467-018-08250-2}
+
+\leavevmode\hypertarget{ref-bruce_impact_2016}{}%
+Bruce, R., Chauvin, A., Trinquart, L., Ravaud, P., \& Boutron, I.
+(2016).
+Impact of interventions to improve the quality of peer review of biomedical journals: A systematic review and meta-analysis.
+\emph{BMC Medicine}, \emph{14}.
+doi:\href{https://doi.org/10.1186/s12916-016-0631-5}{10.1186/s12916-016-0631-5}
+
+\leavevmode\hypertarget{ref-godlee_making_2002}{}%
+Godlee, F.
+(2002).
+Making Reviewers Visible: Openness, Accountability, and Credit.
+\emph{JAMA}, \emph{287}(21), 2762--2765.
+doi:\href{https://doi.org/10.1001/jama.287.21.2762}{10.1001/jama.287.21.2762}
+
 \leavevmode\hypertarget{ref-mulligan_peer_2013}{}%
@@
 Ooms, J. (2019). \emph{Pdftools: Text extraction, rendering and converting of PDF documents}.
-
-\leavevmode\hypertarget{ref-rooyen_effect_2010}{}%
-Rooyen, S.
-van, Delamothe, T., \& Evans, S.
-J.
-W.
-(2010).
-Effect on peer review of telling reviewers that their signed reviews might be posted on the web: Randomised controlled trial.
-\emph{BMJ}, \emph{341}, c5729.
-doi:\href{https://doi.org/10.1136/bmj.c5729}{10.1136/bmj.c5729}
 

### 2019-10-27 download_RSOB_pdf.R
update reviews and code

@@ -48,7 +48,7 @@ for (i in 1:length(article_id)) {
   
   url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsob.", article_id[i], "&file=rsob", article_id[i], "_review_history.pdf", sep="") #for biology
   #url <- paste("https://royalsocietypublishing.org/action/downloadSupplement?doi=10.1098%2Frsos.", article_id[i], "&file=rsos", article_id[i], "_review_history.pdf", sep="")
-  destfile1 <- paste("royal_society_pdf_files\\open_science\\review", article_id[i], ".pdf", sep="")
+  destfile1 <- paste("royal_society_pdf_files\\open_biology\\review", article_id[i], ".pdf", sep="")
   #download.file(url, destfile=destfile1 , mode="wb")
   readUrl(url, destfile1)
   print(article_id[i])

### 2019-10-27 peerj_download_reviews_create_text.R

@@ -6,7 +6,7 @@ library(here)
 
 here()
 
-for (r in 1:7223){ #Uses the reviews 1 to 7233 from PeerJ
+for (r in 1:7930){ #Uses the reviews 1 to 7930 from PeerJ
   
   review_id <- r
   

### 2019-10-27 peerj_cs_download_reviews_create_text.R
peerj cs reviews add

@@ -1,0 +1,183 @@
+# load packages
+library(RCurl)
+library(XML)
+library(stringr)
+library(here)
+
+here()
+
+for (r in 1:225){ #Uses the reviews 1 to 7233 from PeerJ
+  
+  review_id <- r
+  
+  # download html
+  html <- getURL(paste("https://peerj.com/articles/cs-", review_id, "/reviews/", sep=""), followlocation = TRUE, .mapUnicode = FALSE) #added .mapUnicode = FALSE otherwise reviews for 140 gave a bug
+  
+  #parse html
+  PeerJdoc = htmlParse(html, asText=TRUE)
+  plain.text <- xpathSApply(PeerJdoc, "//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)][not(ancestor::form)]", xmlValue)
+  
+  ############################Text cleaning##########################################
+  peerdoc <- paste(plain.text, collapse = "  ")
+  peerdoc <- strsplit(peerdoc, "\n\n")
+  peerdoc <- unlist(peerdoc)
+  peerdoc <- trimws(peerdoc)
+  peerdoc <- str_trim(peerdoc)
+  peerdoc <- gsub("?", "", peerdoc)
+  peerdoc <- gsub("\n", "", peerdoc)
+  peerdoc <- gsub("\t", "", peerdoc)
+  peerdoc <- gsub("\t\t", "", peerdoc)
+  peerdoc <- gsub("\\s+", " ", peerdoc)
+  peerdoc <- peerdoc[peerdoc != ""]
+  
+  ##############################Labeling section#####################################
+  #in this section labels get added to the txt files to mark the locations at which important information is contained
+  
+  version_count <- 1
+  author_count <- 1
+  x = length(peerdoc)     #for the while loop
+  y = 1                   #for the while loop
+  
+  while (y<x){
+    if((str_sub(peerdoc[y], 1, 10) == "Version 0.")){
+      peerdoc <- append(peerdoc, paste("label_version_", version_count , sep=""), after= y - 1)
+      peerdoc <- append(peerdoc, paste("label_recommendation_", version_count, sep="" ), after=y+4)
+      version_count = version_count +1
+      x=x+1
+      y=y+1
+    }
+    if(peerdoc[y] == "Basic reporting"){
+      peerdoc <- append(peerdoc, paste("label_br_", author_count, sep="" ), after=y)
+      peerdoc <- append(peerdoc, paste("label_author_", author_count , sep=""), after= y - 3)
[…]

### 2019-10-28 open_peer_review.Rmd
update code after rerunning everything

@@
 ---
-title             : "Researchers Decision to Sign is Related to Their Recommendation"
+title             : "Researchers Decision to Sign Reviews is Related to Their Recommendation"
 shorttitle        : "Recommendation Relates to Signing"
@@
 abstract: |
- Open review is becoming increasingly common.
-Surveys indicate that researchers are generally positive about making peer reviews available.
-Researchers are more negative about revealing the identity of reviewers.
-In part this is because of the possibility that reviewers will be less likely to express criticisms if their identity is known to authors.
-Experiments suggest that reviewers might be somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
-So far, there is surprisingly little information about what reviewers actually do in practice.
-We analyzed XXXX open reviews in PeerJ and XXXX reviews in the Royal Society Open Science and Open Biology to examine whether in practice the propability that a reviewer reveals their identity is related to their recommendation.
-When comparing XXXX signed and XXXX unsigned reviews, we observed a clear pattern where the more positive a recommendation, the more likely it was signed.
-Although our data does not allow for inferences about causal relationships, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
+ Surveys indicate that researchers are generally positive about making peer reviews available alongside published articles.
+Researchers are more negative about revealing the identity of reviewers, They worry reviewers will be less likely to express criticisms if their identity is known to authors.
+Experiments suggest that reviewers are somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
+One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
+We replicate and extend this finding by analyzing 7930 open reviews in PeerJ and XXXX reviews in the Royal Society Open Science and Open Biology where authors can voluntarily make their identity known.
+Our results confirm that the probability that a reviewer reveals their identity is related to their recommendation.
+The more positive a recommendation was, the more likely it was that authors shared their identity.
+Although our data is correlational and does not allow causal conclusions, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
+We also share XXXX textmined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
 
@@
 An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve the peer review process [@bruce_impact_2016].
-Having access to these peer review reports makes it possible to gain new insights about how scientists perform reviews.
+Open peer review can be implemented by making peer reviews available, but also be revealing the identity of reviewers during or after the peer review process.
+An important argument for revealing the identity of reviewers is that they can receive credit for their work [@godlee_making_2002].
+However, scientists do not feel these benefits outweigh possible costs, and are worried that criticism on manuscripts might lead to backlash from the authors in the future.
+Some reviewers might accept these consequences, while other might choose to strategically reveal their identity only for positive reviews they write.
 
-Some journals have chosen to not just share reviews publicly when an article is published, but in addition require reviewers to sign their reviews.
-An important argument for such a policy is that reviewers can receive credit for their work [@godlee_making_2002].
-However, scientists do not feel these benefits outweigh possible costs.
-Researchers indicate they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers [@mulligan_peer_2013].
-A more recent survey among almost 3000 scientists found that 50.8% of reviewers believe signed open reviews would make peer review worse [@ross-hellauer_survey_2017].
+Researchers indicate that they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about manuscripts they believe are poor quality [@mulligan_peer_2013].
+A more recent survey found that 50.8% of almost 3000 scientists believe that revealing the identity of reviewers would make peer review worse [@ross-hellauer_survey_2017].
 Almost two-thirds of respondents believed reviewers would be less likely to deliver strong criticisms if their identity became known to the authors.
 
-These self-report studies are complemented by experiments in which reviewers are been randomly assigned to a condition where their names would be added to their reviews or not [@walsh_open_2000].
-Reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51).
-This suggests that a causal effect exists between knowing your name will be known or not and the recommendation reviewers provide.
-Across four studies, a meta-analysis by Bruce and colleagues (2016) supports the conclusion that reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
+These self-report studies are complemented by experiments in which reviewers are randomly assigned to a condition where their identity would be revealed during the peer review process [@walsh_open_2000].
+Reviewers in the condition where their identity was revealed were less likely to recommend rejection (n = 30) than reviewers who remained anonymous (n = 51).
+This suggests that a causal effect exists between knowing your identity will be revealed, and the recommendation that is made during the peer review process.
+A meta-analysis by Bruce and colleagues (2016) supports the conclusion that across four studies reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
 
-Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to highly critical reviews, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
+Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
 The trade-off between the benefit of getting credit for peer review work and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the most positive their recommendation is.
@@
 One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, Journal of Hydrology: Regional Studies, and the International Journal of Surgery [@bravo_effect_2019].
-Although only 8.1% of reviewers choose to disclose their identity in these reviews, but the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
-Here, we examine this pattern in two large open access journals that publish across a wide range of scientific disciplines.
-In this replication and extension of the analysis by Bravo and colleagues (2019) we examine the relationship between recommendations and signed reviews in open peer reviews in mega-journals that publish scientific work across a wide range of scientific disciplines.
+Although only 8.1% of reviewers choose to disclose their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
 
-# Accessing Open Peer Reviews
+# The current study
 
-To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles published in The Royal Society Open Science and Open Biology, and 7223 articles published in PeerJ.
-PeerJ launched in 2012 and gave reviewers the possibility to sign, and authors to make the peer reviews available with the final publication.
-The Royal Society Open science launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication.
-Royal Society Open Biology made sharing reviews with the final publication mandatory in 2017.
+We examined the relationship between recommendations peer reviewer make and the probability that they have signed their review in two large open access journals, PeerJ and Royal Society Open Science and Open Biology.
+These journals publish across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
+To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as `r length(TRS_scopus_OS$DOI) + length(TRS_scopus_OB$DOI)` articles published in The Royal Society Open Science (RSOS) and Royal Society Open Biology (RSOB).
+PeerJ launched in 2012 and provides reviewers the possibility to sign, and provides authors the possibility to make peer reviews available with the final publication.
+RSOS launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication, and made this mandatory in January 2019.
+RSOB made sharing reviews with the final publication mandatory in May 2017.
+Peer reviewers have the option to make their identity known when submitting their review to RSOS or RSOB.
 Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, these reviews provide insights into the peer review behavior of scientists across a wide range of disciplines.
+
+# Accessing Open Reviews
 
@@
 Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article can be found).
-Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files.
+For RSOS and RSOB reviews are published online as a PDF file.
 A list of Digital Object Identifiers (DOIs) for every article published in these two outlets was retrieved through Scopus.
-All reviews were downloaded, and the PDF files were exported to plain text files using pdftools [@ooms_pdftools_2019].
-These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package [@wickham_stringr_2019].
+All reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R [@r_core_team_r_2013; @ooms_pdftools_2019].
+These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package in R [@wickham_stringr_2019].
 
-For each article we extracted the number of revisions, and for each revision we saved for each review whether the reviewer signed or not, the word count for their review, and the recommendation for that review round.
-Note that for PeerJ recommendations each round are giving by the editor.
+For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round.
+Note that for PeerJ the editor makes the recommendation for each revision, based on the reviews.
 We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
 For RSOS and RSOB reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
-Although 'reject' recommendations occur for RSOS and RSOB, both PeerJ and RSOS and RSOB only share reviews for published articles, and therefore we have very few reject recommendation in RSOS and RSOB, and none in PeerJ.
-Searching all reviews for PeerJ for the words 'appealed on' reveals 44 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
+Although 'reject' recommendations occur for RSOS and RSOB, both PeerJ, RSOS, and RSOB only share reviews for published articles, and therefore we have very few 'reject' recommendations in RSOS and RSOB, and none in PeerJ.
+Searching all reviews for PeerJ for the words 'appealed on' revealed 44 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
 We have coded these papers as 'major revisions'.
@@
 
-# Peer Review Reports
+# Results
 
-PeerJ provides authors the option to publish the peer reviews of their article alongside the final publication of the article.
-The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science).
-Peer reviewers have the option to provide their names to the authors when submitting their peer review for both PeerJ and Royal Society Open Science and Open Biology.
-
-We examined the first 7223 articles pubished in PeerJ, as well as the first `r length(TRS_scopus_OS$DOI)` articles in RSOS and the first `r length(TRS_scopus_OB$DOI)` articles in RSOB.
+We examined the first 7930 articles pubished in PeerJ, as well as the first `r length(TRS_scopus_OS$DOI)` articles in RSOS and the first `r length(TRS_scopus_OB$DOI)` articles in RSOB.
 We retrieved all reviews for all review rounds of `r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique_os)` articles in RSOS, and `r nrow(TRS_unique_ob)` articles in RSOB.
@@
 
-When analyzing all reviews of original submissions in PeerJ `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their reviews and `r sum(PeerJ_data_R1$df_anonymous == 1)` did not.
-In The Royal Society journals `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their first review while `r sum(TRS_data_R1$df_anonymous == 1)` did not.
-The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for the Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed the first 1214 articles published in PeerJ.
+For all original submissions in PeerJ `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed, and `r sum(PeerJ_data_R1$df_anonymous == 1)` reviewers did not.
+In Royal Society journals `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their first review while `r sum(TRS_data_R1$df_anonymous == 1)` did not.
+The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed the first 1214 articles published in PeerJ.
 
@@
 The percentage of signed peer reviews is larger for minor revisions (`r 100 * as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))[2]`%) than it is for major revisions (`r 100 * as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))[3]`%).
-Too few articles are accepted after the initial revision in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to provide reliable estimates for this category.
+Too few articles are immediately accepted after the first round of reviews in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to provide reliable estimates for this category.
 
@@
 We can therefore directly compare how recommendations are related to the decision to sign reviews.
-The percentage of signed peer reviews is decreases as recommendations become more negative, from `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[1]`% for 'accept' recommendations, `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[2]`% for 'minor revisions', `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[3]`% for 'major revisions', and `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[4]`% for 'reject' recommendations.
+The percentage of signed peer reviews decreases as recommendations become more negative, from `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[1]`% for 'accept' recommendations, `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[2]`% for 'minor revisions', `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[3]`% for 'major revisions', and `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[4]`% for 'reject' recommendations.
 
@@
 
-Since these data are correlational we can not draw causal conclusions.
+We can not draw causal conclusions based on this correlational data.
 It is possible that reviewers are less likely to sign more negative reviews.
 It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
-Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-Our results replicate the observations by Bravo and colleagues (2019).
+Given the literature described in the introduction, we know researchers are concerned about voicing criticism when their identity becomes known, and experimental evidence suggests that if identities will be shared with authors, recommendation become somewhat more positive.
+Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
+Although we had access to less 'reject' manipulations than Bravo and colleagues (2019) because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates their findings across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteers to disclose their identity.
+This replication suggests this difference in recommendations depending on whether reviews are signed or not is a reliable observation.
 
@@
 
-The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for RSOS and RSOB).
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for RSOS and RSOB).
 Through the DOI, researchers can link this data to other sources of information such as citation counts.
-Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.
+Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
 For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
@@
 
-Since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, one example of the insights open reviews provide is how often reviewers agree.
-For the `r sum(table(rev_dif))` individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in `r table(rev_dif)[1]` (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`%) of the time.
+Since we know the invididual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
+For the `r sum(table(rev_dif))` papers where te reviews were published, all reviewers agreed on the recommendation in `r table(rev_dif)[1]` (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`%) of the time.
 For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
@@
 Our analysis shows that when authors are given the choice to sign their reviews, signed reviews have more positive recommendations than unsigned reviews.
-This is true for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
-The effect is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
-Our results replicate and extend earlier findings by @bravo_effect_2019, and complement self-report and experimental results.
-Although our results do not allow for causal claims, they are in line with experimental results that reveal researchers give more positive recommendations when their name is published alongside their reviews [@bruce_impact_2016].
+This pattern is clearly present for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
+The pattern is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
+Our results replicate and extend earlier findings by @bravo_effect_2019, and complement self-report and experimental results in the literature.
 
-Open reviews allow researchers to adress meta-scientific questions that give insights into the peer review process.
-Our data provide further support for the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
-Our correlational data, interpreted together with self-report data and experiments in the literature, increases the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
+Peer review is generally seen as an important quality control mechanism in science, yet researchers can rarely evaluate the quality of peer review at journals.
+Open reviews allow researchers to examine meta-scientific questions that give insights into the peer review process.
+Our data support the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
+Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
 This type of strategic behavior also follows from a purely rational strategy to optimize the benefits of peer review while minimizing the costs.
-For positive recommendations, reviewers will get credit for theor reviews, while for negative reviews, they do not run the risk of receiving any backlash from collegaues in their field.
+For positive recommendations, reviewers will get credit for their reviews, while for negative reviews, they do not run the risk of receiving any backlash from colleagues in their field.
 
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation [@bastian_signing_2018].
-Althoughit looks increasingly plausible that at least some reviewers feel hesitant to sign if they believe doing so could have negative consequences, but are willing to sign to gain credit for their work for more positive recommendations, it seems wortwhile to explore ways in which they can receive credit for all their peer review work, also when their recommendations are more negative.
+Although it looks increasingly plausible that at least some reviewers feel hesitant to sign if they believe doing so could have negative consequences, but are willing to sign to gain credit for their work for more positive recommendations, it seems worthwhile to explore ways in which they can receive credit for all their peer review work, also when their recommendations are more negative.
 If more journals share open reviews, also for rejected manuscripts, future meta-scientific work might be able to study this important topic in more detail.

### 2019-10-28 check_not_corrupt_royal_society_open_biology.R

@@ -7,6 +7,9 @@ here::here()
 
 #########################list of article id's#####################################
 article_id <- vector()
+article_id_os_open <- vector()
+fix_doc <- vector()
+
 # Create a list of all PDF files in the folder
 article_id <- str_extract(list.files(path = "royal_society_pdf_files\\open_biology\\", pattern = "\\.pdf$"), "[0-9]+") #list all files in the folder and extract article ID
 

### 2019-10-28 check_not_corrupt_royal_society_open_science.R

@@ -7,6 +7,9 @@ here::here()
 
 #########################list of article id's#####################################
 article_id <- vector()
+article_id_os_open <- vector()
+fix_doc <- vector()
+
 # Create a list of all PDF files in the folder
 article_id <- str_extract(list.files(path = "royal_society_pdf_files\\open_science\\", pattern = "\\.pdf$"), "[0-9]+") #list all files in the folder and extract article ID
 

### 2019-10-28 download_RSOS_pdf.R

@@ -39,7 +39,7 @@ close(conn)
 
 ########################downloading the pdf's#####################################
 #this section is used for downloading the pdf files.
-sleep <- function() { Sys.sleep(30) } #needed to prevent an IP block from the royal society website
+sleep <- function() { Sys.sleep(20) } #needed to prevent an IP block from the royal society website
 i<-1
 for (i in 1:length(article_id)) {
   sleep()

### 2019-10-28 textmining_peerj_cs.R

@@ -22,11 +22,11 @@ closed_reviews <- 0
 total_version <- 0
 
 #########################################read txt file##########################################################
-for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 PeerJ articles
+for (r in 1:225){ #starting the loop to create the dataframe from the 6800 PeerJ articles
   
   review_id <- r
   
-  path <- paste("peerj_reviews_txt/",review_id,".txt", sep="")
+  path <- paste("peerj_cs_reviews_txt/",review_id,".txt", sep="")
   
   open_file <- file(path, open = "r")
   lines <- readLines(open_file)
@@ -42,7 +42,7 @@ for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 Peer
     ###############################################Link############################################################
     
     link <- "" #reset link
-    link <- paste("https://peerj.com/articles/", review_id, "/reviews/", sep="") 
+    link <- paste("https://peerj.com/articles/cs-", review_id, "/reviews/", sep="") 
     
     ###############################Word count, positive and negative###############################################
     
@@ -160,7 +160,7 @@ for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 Peer
     } else if (select_section == "zoological science"){
       section <- lines[a]
     } else {
-      section <- "NA"
+      section <- "computer science"
     }
     
     ############################################Timelapse##########################################################
@@ -205,4 +205,4 @@ for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 Peer
 #################################Creating dataframe and csv file#################################################
 df <- data.frame(df_link, df_section, df_days, df_version, df_recommendation, df_word_count, df_anonymous, df_reviewer_name)
 
-saveRDS(df, file = "peerj_data.rds")             #used to create the rds file
+saveRDS(df, file = "peerj_cs_data.rds")             #used to create the rds file

### 2019-10-28 royal_society_open_biology_create_txt.R
update datasets for preprint

@@ -12,7 +12,7 @@ article_id <- readLines(file("royal_society_pdf_files/OB_pdf_list.txt", open = "
 ########################Reading pdf file #########################################
 for (i in 1:length(article_id)) {
   pdf_file <- paste("royal_society_pdf_files/open_biology/review", article_id[i], ".pdf", sep="") #map with open biology pdf's
-  print(article_id)
+  print(article_id[i])
   if (file.exists(pdf_file)){
   read <- readPDF(control = list(text = "-layout"))
   document <- Corpus(URISource(pdf_file), readerControl = list(reader = read))

### 2019-10-28 royal_society_open_science_create_txt.R

@@ -12,7 +12,7 @@ article_id <- readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "
 ########################Reading pdf file #########################################
 for (i in 1:length(article_id)) {
   pdf_file <- paste("royal_society_pdf_files/open_science/review", article_id[i], ".pdf", sep="") #map with open science pdf's
-  print(article_id)
+  print(article_id[i])
   if (file.exists(pdf_file)){
   read <- readPDF(control = list(text = "-layout"))
   document <- Corpus(URISource(pdf_file), readerControl = list(reader = read))

### 2019-10-28 open_peer_review.Rmd
pre-print ready

@@
 author_note: |
- This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. 
+ This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/jkbmw/
 abstract: |
@@
 One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
-We replicate and extend this finding by analyzing 7930 open reviews in PeerJ and XXXX reviews in the Royal Society Open Science and Open Biology where authors can voluntarily make their identity known.
+We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science and Open Biology where authors can voluntarily make their identity known.
 Our results confirm that the probability that a reviewer reveals their identity is related to their recommendation.
@@
 Although our data is correlational and does not allow causal conclusions, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
-We also share XXXX textmined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
+We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
 
 keywords          : "Peer Review, Open Science, Transparency"
-wordcount         : 4926
+wordcount         : 2711
 bibliography      : ["signing_open_peer_review_.bib"]
@@
 #Read in PeerJ data
-PeerJ_data <- readRDS(file = "peerj_data.rds")
+PeerJ_main_data <- readRDS(file = "peerj_data.rds")
+PeerJ_cs_data <- readRDS(file = "peerj_cs_data.rds")
+# Combine both datasets into one.
+PeerJ_data <- rbind(PeerJ_main_data, PeerJ_cs_data)
 
@@
 table(TRS_scopus_OS$Document.Type)
+errata_editorial <- sum(table(TRS_scopus_OS$Document.Type)[c(3,4)])
 # Excude Errata and Editorial (that have no reviews)
@@
 table(TRS_scopus_OB$Document.Type)
+errata_editorial <- errata_editorial + sum(table(TRS_scopus_OB$Document.Type)[c(2,3,5)])
 # Excude Errata and Editorial (that have no reviews)
@@
 
+# How many reviews in total in the traw txt files?
+length(TRS_data$df_anonymous)+length(PeerJ_data$df_anonymous)
+
 # Select only those reviews for each paper with the highest version for PeerJ (first review)
@@
 
-ggplot(TRS_review_agree, aes(x = as.factor(df_unique))) + 
-  geom_bar() +
-  theme_linedraw(base_size = 20)
-
 # Are there really reviws with 4 distinct recommendations?
-sum(TRS_review_agree$df_unique == 4)
+sum(TRS_review_agree$df_unique == 4) # Reported as a fun fact in the additional analyses
 
@@
 
-# The current study
+# The Current Study
 
@@
 Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article can be found).
+PeerJ has several more recent dedicated journals for computer science and chemistry.
+In the analyses reported here we included PeerJ Computer Science, which started in 2015, but ignore the chemistry journals that started at the end of 2019 due to the small number of published articles.
 For RSOS and RSOB reviews are published online as a PDF file.
@@
 
-We examined the first 7930 articles pubished in PeerJ, as well as the first `r length(TRS_scopus_OS$DOI)` articles in RSOS and the first `r length(TRS_scopus_OB$DOI)` articles in RSOB.
-We retrieved all reviews for all review rounds of `r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique_os)` articles in RSOS, and `r nrow(TRS_unique_ob)` articles in RSOB.
+We examined `r 7930+225` articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles from Royal Society (`r length(TRS_scopus_OS$DOI)` from RSOS, `r length(TRS_scopus_OB$DOI)` from RSOB, `r errata_editorial` of which were editorials or errata) published up to October 2019.
+We retrieved all reviews when these were made available (`r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique)` articles in Royal Society).
 Articles can go through multiple rounds of review.
-We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following [@bravo_effect_2019].
+We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following @bravo_effect_2019.
 On average initial submissions at PeerJ received `r round(mean(count(PeerJ_data_R1, df_link)$n), 2)` reviews.
@@
 
-For all original submissions in PeerJ `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed, and `r sum(PeerJ_data_R1$df_anonymous == 1)` reviewers did not.
-In Royal Society journals `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their first review while `r sum(TRS_data_R1$df_anonymous == 1)` did not.
+For all `r nrow(PeerJ_unique)` articles published in PeerJ where reviews were available we retrieved `r length(PeerJ_data_R1$df_anonymous)` unique reviews (as each article is typically reviewed by multiple reviewers) for the initial submission.
+In total `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their review for the initial submission, and `r sum(PeerJ_data_R1$df_anonymous == 1)` reviewers did not.
+In Royal Society journals we analyzed `r nrow(TRS_unique)` articles for which we retrieved `r length(TRS_data_R1$df_anonymous)` unique reviews for the first submission, where `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their review, and `r sum(TRS_data_R1$df_anonymous == 1)` did not.
 The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed the first 1214 articles published in PeerJ.
 
-To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round.
+To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
 Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer.
-The percentage of signed peer reviews is larger for minor revisions (`r 100 * as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))[2]`%) than it is for major revisions (`r 100 * as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))[3]`%).
-Too few articles are immediately accepted after the first round of reviews in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to provide reliable estimates for this category.
+For minor revisions, a greater proportion or reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
+Too few articles are immediately accepted after the first round of reviews in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to impact the proportions in the other two categories.
 
-```{r, PeerJrec, fig.cap = "Frequencies of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended 'minor revisions' or 'major revisions'."}
+```{r, PeerJrec, fig.cap = "Proportions of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended 'minor revisions' or 'major revisions'."}
 
@@
 
-#create plot data for only minor, major recommendations
-plot_data <- data.frame(factor(c("minor revision", "major revision", "minor revision", "major revision"), levels = c("minor revision", "major revision"))
-                               ,
+# Makes more sense to plot proportions
+PeerJ_anonymous_by_recommendation_proportion <- PeerJ_anonymous_by_recommendation/sum(PeerJ_anonymous_by_recommendation)
+
+PeerJ_notanonymous_by_recommendation_proportion <- PeerJ_notanonymous_by_recommendation/sum(PeerJ_notanonymous_by_recommendation)
+
+# create plot data for only minor, major recommendations
+# Remove _proportion for raw frequencies plot
+plot_data <- data.frame(factor(c("minor revision", "major revision", "minor revision", "major revision"), levels = c("minor revision", "major revision")),
                    c("unsigned", "unsigned", "signed", "signed"),
-                   c(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]))
+                   c(PeerJ_anonymous_by_recommendation_proportion[2:3], PeerJ_notanonymous_by_recommendation_proportion[2:3]))
 colnames(plot_data) <- c("recommendation", "signed", "count")
@@
   scale_fill_manual(values = c("#000000", "#808080")) + 
-  coord_cartesian(ylim = c(0, 5000)) +
-  geom_text(aes(label = count), 
+  coord_cartesian(ylim = c(0, 1)) +
+  geom_text(aes(label = sprintf('%.2f',count)), 
               size = 6, 
@@
 Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of 'accept', 'minor revisions', 'major revisions', or 'reject'.
-We can therefore directly compare how recommendations are related to the decision to sign reviews.
-The percentage of signed peer reviews decreases as recommendations become more negative, from `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[1]`% for 'accept' recommendations, `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[2]`% for 'minor revisions', `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[3]`% for 'major revisions', and `r 100 * as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))[4]`% for 'reject' recommendations.
+We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}).
+The overal pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).
 
-```{r, TRSrec, fig.cap = "Frequencies of signed and unsigned reviews as a function of whether the reviewer at the Royal Society Open Science and Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
+```{r, TRSrec, fig.cap = "Proportions of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
+
+# Makes more sense to plot proportions
+TRS_anonymous_by_recommendation_proportion <- TRS_anonymous_by_recommendation/sum(TRS_anonymous_by_recommendation)
+TRS_notanonymous_by_recommendation_proportion <- TRS_notanonymous_by_recommendation/sum(TRS_notanonymous_by_recommendation)
 
@@
                    c("unsigned", "unsigned", "unsigned", "unsigned", "signed", "signed", "signed", "signed"),
-                   c(TRS_anonymous_by_recommendation, TRS_notanonymous_by_recommendation))
+                   c(TRS_anonymous_by_recommendation_proportion, TRS_notanonymous_by_recommendation_proportion))
 colnames(plot_data) <- c("recommendation", "signed", "count")
@@
   scale_fill_manual(values = c("#000000", "#808080")) + 
-  coord_cartesian(ylim = c(0, 1250)) +
-  geom_text(aes(label = count), 
+  coord_cartesian(ylim = c(0, 1)) +
+  geom_text(aes(label = sprintf('%.2f',count)), 
               size = 6, 
@@
 It is possible that reviewers are less likely to sign more negative reviews.
-It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
-Given the literature described in the introduction, we know researchers are concerned about voicing criticism when their identity becomes known, and experimental evidence suggests that if identities will be shared with authors, recommendation become somewhat more positive.
+It is also possible that people who sign their reviews generally give more positive recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
+Based on the literature reviewed in the introduction we know researchers are hesitant to voice criticism when their identity will be known, and experimental evidence suggests that if identities are shared with authors, recommendations become somewhat more positive.
 Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-Although we had access to less 'reject' manipulations than Bravo and colleagues (2019) because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates their findings across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteers to disclose their identity.
-This replication suggests this difference in recommendations depending on whether reviews are signed or not is a reliable observation.
+Although we had access to few 'reject' recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by @bravo_effect_2019 across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteers to disclose their identity.
+This replication suggests the difference in recommendations depending on whether reviews are signed or not is a reliable observation.
 
@@
 For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
-With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (@wang_open_2016) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews.
+With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (@wang_open_2016) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews (see Figure \ref{fig:wordcount}).
 
-```{r wordcount}
+```{r wordcount, fig.cap = "Word count for reviews for first submission at Royal Society journals as a factor of the recommendation."}
 # Word counts PeerJ
@@
 
-Since we know the invididual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
-For the `r sum(table(rev_dif))` papers where te reviews were published, all reviewers agreed on the recommendation in `r table(rev_dif)[1]` (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`%) of the time.
+Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
+For the `r sum(table(rev_dif))` papers where te reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (s0 `r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
 For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
@@
 At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
-Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at specific journals.
-Despite this limitation, the pattern of results is very similar to that observed by Bravo and colleagues (2019) who had access to the reviews for accepted and rejected manuscripts.
+Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
+Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.
 Thus, even though the proportion of reject recommendation in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datsets that include rejected manuscripts.
@@
 Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
-This type of strategic behavior also follows from a purely rational strategy to optimize the benefits of peer review while minimizing the costs.
+This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs.
 For positive recommendations, reviewers will get credit for their reviews, while for negative reviews, they do not run the risk of receiving any backlash from colleagues in their field.
@@
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation [@bastian_signing_2018].
-Although it looks increasingly plausible that at least some reviewers feel hesitant to sign if they believe doing so could have negative consequences, but are willing to sign to gain credit for their work for more positive recommendations, it seems worthwhile to explore ways in which they can receive credit for all their peer review work, also when their recommendations are more negative.
-If more journals share open reviews, also for rejected manuscripts, future meta-scientific work might be able to study this important topic in more detail.
-
-```{r, include = FALSE}
-# We can in principle report p-values for tests for proportions, but I don't think this adds omething to the manuscript.
-
-prop_data <- cbind(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]) #bind as matrix
-rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("anonymous", "not anonymous") #add row names
-# Test of these different proportions
-prop.test(prop_data) #perform test of proportions
-
-# In proportions
-# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
-# Calculate proportions
-1-as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))
-
-```
+Although the available data suggests that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign more positive recommendations to get credit for their work, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their, regardless of whether their recommendation is positive or negative.
 
@@
 Lakens drafted the final version, and both authors revised the final version of the manuscript.
-
-# Conflict of Interest Statement
-
 The authors report no conflicts of interest.

### 2019-10-28 open_peer_review.tex
pre-print ready

@@
 \hypersetup{unicode=true,
-            pdftitle={Researchers Decision to Sign is Related to Their Recommendation},
+            pdftitle={Researchers Decision to Sign Reviews is Related to Their Recommendation},
             pdfauthor={Nino van Sambeek~\& Daniël Lakens},
@@
 
-  \title{Researchers Decision to Sign is Related to Their Recommendation}
+  \title{Researchers Decision to Sign Reviews is Related to Their Recommendation}
     \author{Nino van Sambeek\textsuperscript{1}~\& Daniël Lakens\textsuperscript{1}}
@@
 \textsuperscript{1} Eindhoven University of Technology, The Netherlands}
-\keywords{Peer Review, Open Science, Transparency\newline\indent Word count: 4926}
+\keywords{Peer Review, Open Science, Transparency\newline\indent Word count: 2711}
 \usepackage{csquotes}
@@
 \authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
+All data underlying this reproducible manuscript are available at \url{https://osf.io/jkbmw/}
 
@@
 \abstract{
-Open review is becoming increasingly common.
-Surveys indicate that researchers are generally positive about making peer reviews available.
-Researchers are more negative about revealing the identity of reviewers.
-In part this is because of the possibility that reviewers will be less likely to express criticisms if their identity is known to authors.
-Experiments suggest that reviewers might be somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
-So far, there is surprisingly little information about what reviewers actually do in practice.
-We analyzed XXXX open reviews in PeerJ and XXXX reviews in the Royal Society Open Science and Open Biology to examine whether in practice the propability that a reviewer reveals their identity is related to their recommendation.
-When comparing XXXX signed and XXXX unsigned reviews, we observed a clear pattern where the more positive a recommendation, the more likely it was signed.
-Although our data does not allow for inferences about causal relationships, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
+Surveys indicate that researchers are generally positive about making peer reviews available alongside published articles.
+Researchers are more negative about revealing the identity of reviewers, They worry reviewers will be less likely to express criticisms if their identity is known to authors.
+Experiments suggest that reviewers are somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
+One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
+We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science and Open Biology where authors can voluntarily make their identity known.
+Our results confirm that the probability that a reviewer reveals their identity is related to their recommendation.
+The more positive a recommendation was, the more likely it was that authors shared their identity.
+Although our data is correlational and does not allow causal conclusions, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
+We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
 
@@
 An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve the peer review process (Bruce, Chauvin, Trinquart, Ravaud, \& Boutron, 2016).
-Having access to these peer review reports makes it possible to gain new insights about how scientists perform reviews.
+Open peer review can be implemented by making peer reviews available, but also be revealing the identity of reviewers during or after the peer review process.
+An important argument for revealing the identity of reviewers is that they can receive credit for their work (Godlee, 2002).
+However, scientists do not feel these benefits outweigh possible costs, and are worried that criticism on manuscripts might lead to backlash from the authors in the future.
+Some reviewers might accept these consequences, while other might choose to strategically reveal their identity only for positive reviews they write.
 
-Some journals have chosen to not just share reviews publicly when an article is published, but in addition require reviewers to sign their reviews.
-An important argument for such a policy is that reviewers can receive credit for their work (Godlee, 2002).
-However, scientists do not feel these benefits outweigh possible costs.
-Researchers indicate they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about poor quaity papers (Mulligan, Hall, \& Raphael, 2013).
-A more recent survey among almost 3000 scientists found that 50.8\% of reviewers believe signed open reviews would make peer review worse (Ross-Hellauer, Deppe, \& Schmidt, 2017).
+Researchers indicate that they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about manuscripts they believe are poor quality (Mulligan, Hall, \& Raphael, 2013).
+A more recent survey found that 50.8\% of almost 3000 scientists believe that revealing the identity of reviewers would make peer review worse (Ross-Hellauer, Deppe, \& Schmidt, 2017).
 Almost two-thirds of respondents believed reviewers would be less likely to deliver strong criticisms if their identity became known to the authors.
 
-These self-report studies are complemented by experiments in which reviewers are been randomly assigned to a condition where their names would be added to their reviews or not (Walsh, Rooney, Appleby, \& Wilkinson, 2000).
-Reviewers in the signed condition were less likely to recommend rejection (n = 30) than researchers in the unsigned condition (n = 51).
-This suggests that a causal effect exists between knowing your name will be known or not and the recommendation reviewers provide.
-Across four studies, a meta-analysis by Bruce and colleagues (2016) supports the conclusion that reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
+These self-report studies are complemented by experiments in which reviewers are randomly assigned to a condition where their identity would be revealed during the peer review process (Walsh, Rooney, Appleby, \& Wilkinson, 2000).
+Reviewers in the condition where their identity was revealed were less likely to recommend rejection (n = 30) than reviewers who remained anonymous (n = 51).
+This suggests that a causal effect exists between knowing your identity will be revealed, and the recommendation that is made during the peer review process.
+A meta-analysis by Bruce and colleagues (2016) supports the conclusion that across four studies reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
 
-Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to highly critical reviews, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
+Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
 The trade-off between the benefit of getting credit for peer review work and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the most positive their recommendation is.
@@
 One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, Journal of Hydrology: Regional Studies, and the International Journal of Surgery (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
-Although only 8.1\% of reviewers choose to disclose their identity in these reviews, but the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
-Here, we examine this pattern in two large open access journals that publish across a wide range of scientific disciplines.
-In this replication and extension of the analysis by Bravo and colleagues (2019) we examine the relationship between recommendations and signed reviews in open peer reviews in mega-journals that publish scientific work across a wide range of scientific disciplines.
+Although only 8.1\% of reviewers choose to disclose their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
 
-\hypertarget{accessing-open-peer-reviews}{%
-\section{Accessing Open Peer Reviews}\label{accessing-open-peer-reviews}}
+\hypertarget{the-current-study}{%
+\section{The Current Study}\label{the-current-study}}
 
-To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 3576 articles published in The Royal Society Open Science and Open Biology, and 7223 articles published in PeerJ.
-PeerJ launched in 2012 and gave reviewers the possibility to sign, and authors to make the peer reviews available with the final publication.
-The Royal Society Open science launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication.
-Royal Society Open Biology made sharing reviews with the final publication mandatory in 2017.
+We examined the relationship between recommendations peer reviewer make and the probability that they have signed their review in two large open access journals, PeerJ and Royal Society Open Science and Open Biology.
+These journals publish across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
+To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as 3576 articles published in The Royal Society Open Science (RSOS) and Royal Society Open Biology (RSOB).
+PeerJ launched in 2012 and provides reviewers the possibility to sign, and provides authors the possibility to make peer reviews available with the final publication.
+RSOS launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication, and made this mandatory in January 2019.
+RSOB made sharing reviews with the final publication mandatory in May 2017.
+Peer reviewers have the option to make their identity known when submitting their review to RSOS or RSOB.
 Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, these reviews provide insights into the peer review behavior of scientists across a wide range of disciplines.
+
+\hypertarget{accessing-open-reviews}{%
+\section{Accessing Open Reviews}\label{accessing-open-reviews}}
 
@@
 Reviews are always accessible in html (i.e., at \url{https://peerj.com/articles/1/reviews} for the first article can be found).
-Reviews of articles published in The Royal Society Open Science and Open Biology are published online with the articles as PDF files.
+PeerJ has several more recent dedicated journals for computer science and chemistry.
+In the analyses reported here we included PeerJ Computer Science, which started in 2015, but ignore the chemistry journals that started at the end of 2019 due to the small number of published articles.
+For RSOS and RSOB reviews are published online as a PDF file.
 A list of Digital Object Identifiers (DOIs) for every article published in these two outlets was retrieved through Scopus.
-All reviews were downloaded, and the PDF files were exported to plain text files using pdftools (Ooms, 2019).
-These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package (Wickham, 2019).
+All reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2019; R Core Team, 2013).
+These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package in R (Wickham, 2019).
 
-For each article we extracted the number of revisions, and for each revision we saved for each review whether the reviewer signed or not, the word count for their review, and the recommendation for that review round.
-Note that for PeerJ recommendations each round are giving by the editor.
+For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round.
+Note that for PeerJ the editor makes the recommendation for each revision, based on the reviews.
 We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
 For RSOS and RSOB reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
-Although \enquote{reject} recommendations occur for RSOS and RSOB, both PeerJ and RSOS and RSOB only share reviews for published articles, and therefore we have very few reject recommendation in RSOS and RSOB, and none in PeerJ.
-Searching all reviews for PeerJ for the words \enquote{appealed on} reveals 44 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
+Although \enquote{reject} recommendations occur for RSOS and RSOB, both PeerJ, RSOS, and RSOB only share reviews for published articles, and therefore we have very few \enquote{reject} recommendations in RSOS and RSOB, and none in PeerJ.
+Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 44 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
 We have coded these papers as \enquote{major revisions}.
@@
 
-\hypertarget{peer-review-reports}{%
-\section{Peer Review Reports}\label{peer-review-reports}}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-PeerJ provides authors the option to publish the peer reviews of their article alongside the final publication of the article.
-The Royal Society Open Science and Open Biology also provided authors with the option to publish peer reviews alongside the article, and made this mandatory from May 2017 (Open Biology) and January 2019 (Open Science).
-Peer reviewers have the option to provide their names to the authors when submitting their peer review for both PeerJ and Royal Society Open Science and Open Biology.
-
-We examined the first 7223 articles pubished in PeerJ, as well as the first 2887 articles in RSOS and the first 689 articles in RSOB.
-We retrieved all reviews for all review rounds of 4555 articles in PeerJ, 1412 articles in RSOS, and 148 articles in RSOB.
+We examined 8155 articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as 3576 articles from Royal Society (2887 from RSOS, 689 from RSOB, 81 of which were editorials or errata) published up to October 2019.
+We retrieved all reviews when these were made available (5087 articles in PeerJ, 1964 articles in Royal Society).
 Articles can go through multiple rounds of review.
-We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following (Bravo et al., 2019).
+We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following Bravo et al.
+(2019).
 On average initial submissions at PeerJ received 2.36 reviews.
-Articles in the Royal Society journals received on average 2.19 reviews for the original submission.
+Articles in the Royal Society journals received on average 2.13 reviews for the original submission.
 
@@
 
-When analyzing all reviews of original submissions in PeerJ 4172 reviewers signed their reviews and 6569 did not.
-In The Royal Society journals 1261 reviewers signed their first review while 2150 did not.
-The percentages of people who sign (38.84\% for PeerJ, 36.97\% for the Royal Society) are slightly lower than the 43.23\% reported by (Wang, You, Manasa, \& Wolfram, 2016), who analyzed the first 1214 articles published in PeerJ.
+For all 5087 articles published in PeerJ where reviews were available we retrieved 12010 unique reviews (as each article is typically reviewed by multiple reviewers) for the initial submission.
+In total 4592 reviewers signed their review for the initial submission, and 7418 reviewers did not.
+In Royal Society journals we analyzed 1964 articles for which we retrieved 4188 unique reviews for the first submission, where 1549 reviewers signed their review, and 2639 did not.
+The percentages of people who sign (38.23\% for PeerJ, 36.99\% for Royal Society) are slightly lower than the 43.23\% reported by (Wang, You, Manasa, \& Wolfram, 2016), who analyzed the first 1214 articles published in PeerJ.
 
-To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round.
+To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
 Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer.
-The percentage of signed peer reviews is larger for minor revisions (46.37\%) than it is for major revisions (34.63\%).
-Too few articles are accepted after the initial revision in PeerJ (20 in total) to provide reliable estimates for this category.
+For minor revisions, a greater proportion or reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
+Too few articles are immediately accepted after the first round of reviews in PeerJ (22 in total) to impact the proportions in the other two categories.
 
@@
 \includegraphics{open_peer_review_files/figure-latex/PeerJrec-1.pdf}
-\caption{\label{fig:PeerJrec}Frequencies of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended \enquote{minor revisions} or \enquote{major revisions}.}
+\caption{\label{fig:PeerJrec}Proportions of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended \enquote{minor revisions} or \enquote{major revisions}.}
 \end{figure}
@@
 Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.
-We can therefore directly compare how recommendations are related to the decision to sign reviews.
-The percentage of signed peer reviews is decreases as recommendations become more negative, from 46.99\% for \enquote{accept} recommendations, 43.86\% for \enquote{minor revisions}, 29.48\% for \enquote{major revisions}, and 11.07\% for \enquote{reject} recommendations.
+We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}).
+The overal pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).
 
@@
 \includegraphics{open_peer_review_files/figure-latex/TRSrec-1.pdf}
-\caption{\label{fig:TRSrec}Frequencies of signed and unsigned reviews as a function of whether the reviewer at the Royal Society Open Science and Open Biology recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
+\caption{\label{fig:TRSrec}Proportions of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
 \end{figure}
 
-Since these data are correlational we can not draw causal conclusions.
+We can not draw causal conclusions based on this correlational data.
 It is possible that reviewers are less likely to sign more negative reviews.
-It is also possible that people who sign their reviews are in general less negative in their recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
-Given the literature described in the introduction that provides anecdotal evidence researchers worry they will be able to provide open criticism if their names are public, and experimental evidence suggesting that if names are made public, recommendation become somewhat more positive, it seems plausible at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-Our results replicate the observations by Bravo and colleagues (2019).
+It is also possible that people who sign their reviews generally give more positive recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
+Based on the literature reviewed in the introduction we know researchers are hesitant to voice criticism when their identity will be known, and experimental evidence suggests that if identities are shared with authors, recommendations become somewhat more positive.
+Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
+Although we had access to few \enquote{reject} recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by Bravo et al.
+(2019) across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteers to disclose their identity.
+This replication suggests the difference in recommendations depending on whether reviews are signed or not is a reliable observation.
 
@@
 
-The dataset we are sharing has information about the recommendations of reviewers or editors after each round of peer review, the names of reviewers who signed their review, and the time in review (112 days for PeerJ, 133 days for RSOS and RSOB).
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for RSOS and RSOB).
 Through the DOI, researchers can link this data to other sources of information such as citation counts.
-Because the reviews themselves are included in our dataset, researchers interested can use the text files to answer more details questions about the content of peer reviews across different domains.
+Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
 For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
 With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (Wang et al.
-(2016)) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews.
+(2016)) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews (see Figure \ref{fig:wordcount}).
 
+\begin{figure}
+\centering
 \includegraphics{open_peer_review_files/figure-latex/wordcount-1.pdf}
+\caption{\label{fig:wordcount}Word count for reviews for first submission at Royal Society journals as a factor of the recommendation.}
+\end{figure}
 
-Since multiple reviewers for The Royal Society Open Science and Open Biology make their individual recommendations known, one example of the insights open reviews provide is how often reviewers agree.
-For the 1559 individual papers that we were able to retrieve reviews from, reviewers agreed on the recommendation in 646 (41.44\%) of the time.
-For 42.14\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.69\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.73\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
+Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
+For the 1963 papers where te reviews were published, all reviewers agreed on the recommendation for 830 articles (s0 42.28\% of the time).
+For 41.72\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.37\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.63\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
 There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
@@
 At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
-Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at specific journals.
-Despite this limitation, the pattern of results is very similar to that observed by Bravo and colleagues (2019) who had access to the reviews for accepted and rejected manuscripts.
+Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
+Despite this limitation, the pattern of results we observe is very similar to that reported by Bravo et al.
+(2019) who had access to the reviews for accepted and rejected manuscripts.
 Thus, even though the proportion of reject recommendation in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datsets that include rejected manuscripts.
@@
 Our analysis shows that when authors are given the choice to sign their reviews, signed reviews have more positive recommendations than unsigned reviews.
-This is true for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
-The effect is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
+This pattern is clearly present for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
+The pattern is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
 Our results replicate and extend earlier findings by Bravo et al.
-(2019), and complement self-report and experimental results.
-Although our results do not allow for causal claims, they are in line with experimental results that reveal researchers give more positive recommendations when their name is published alongside their reviews (Bruce et al., 2016).
+(2019), and complement self-report and experimental results in the literature.
 
-Open reviews allow researchers to adress meta-scientific questions that give insights into the peer review process.
-Our data provide further support for the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
-Our correlational data, interpreted together with self-report data and experiments in the literature, increases the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
-This type of strategic behavior also follows from a purely rational strategy to optimize the benefits of peer review while minimizing the costs.
-For positive recommendations, reviewers will get credit for theor reviews, while for negative reviews, they do not run the risk of receiving any backlash from collegaues in their field.
+Peer review is generally seen as an important quality control mechanism in science, yet researchers can rarely evaluate the quality of peer review at journals.
+Open reviews allow researchers to examine meta-scientific questions that give insights into the peer review process.
+Our data support the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
+Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
+This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs.
+For positive recommendations, reviewers will get credit for their reviews, while for negative reviews, they do not run the risk of receiving any backlash from colleagues in their field.
 
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation (Bastian, 2018).
-Althoughit looks increasingly plausible that at least some reviewers feel hesitant to sign if they believe doing so could have negative consequences, but are willing to sign to gain credit for their work for more positive recommendations, it seems wortwhile to explore ways in which they can receive credit for all their peer review work, also when their recommendations are more negative.
-If more journals share open reviews, also for rejected manuscripts, future meta-scientific work might be able to study this important topic in more detail.
+Although the available data suggests that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign more positive recommendations to get credit for their work, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their, regardless of whether their recommendation is positive or negative.
 
@@
 Lakens drafted the final version, and both authors revised the final version of the manuscript.
-
-\hypertarget{conflict-of-interest-statement}{%
-\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
-
 The authors report no conflicts of interest.
@@
 
+\leavevmode\hypertarget{ref-r_core_team_r_2013}{}%
+R Core Team. (2013). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing.
+
 \leavevmode\hypertarget{ref-ross-hellauer_survey_2017}{}%

### 2019-10-28 Report_code.R
clean

@@ -1,440 +1,0 @@
-library(data.table)
-library(dplyr)
-library(formattable)
-library(tidyr)
-library(ggplot2)
-
-options(max.print=9999999)
-
-# Read open science and open biology rds datafiles
-TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
-TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
-
-# Combine both datasets into one.
-TRS_data <- rbind(TRS_data_os, TRS_data_ob)
-
-PeerJ_data <- readRDS(file = "peerj_data.rds")
-#print(PeerJ_data)
-
-###################Variables table###################
-varlist <- c("Link", "Section", "Days", "Version", "Recommendation", "Word count", "Masked", "Positive", "Negative")
-varlist2 <- c("The url of the review","Which journal/field of study the review belongs to", "The time between submitting the initial manuscript and publication in days", "The version for which the review is written", "The recommendation that is given by either the editor(PeerJ) or the reviewer(TRS)", "The amount of words that the review contains", "If the reviewer has signed the review or not", "The amount of positive words per 1000 words", "The amount of negative words per 1000 words")
-df_plot <- data.frame(varlist, varlist2)
-names(df_plot)[names(df_plot) == "varlist"] <- "Variable"
-names(df_plot)[names(df_plot) == "varlist2"] <- "Description"
-formattable(df_plot, align = c("l", rep("l", NCOL(df_plot))), size = 14)
-
-mean(PeerJ_data$df_days, na.rm = TRUE)
-t.test(PeerJ_data$df_days, TRS_data$df_days)
-
-#####How many articles are accepted without the version being reviewed PeerJ#####
-v <- 0 
-for (i in 1:length(PeerJ_data$X)){
-  if ((PeerJ_data$df_version[i] == 1)&(is.na(PeerJ_data$df_version[i])==FALSE)){
-    if (PeerJ_data$df_link[i]!= PeerJ_data$df_link[i-1]){
-    v = v + 1
-    }
-  }
-}
-print(v)
-
-#####How many articles are accepted without the version being reviewed TRS#####
-v <- 0 
[…]

### 2019-10-28 open_peer_review.Rmd
preprint

@@
 title             : "Researchers Decision to Sign Reviews is Related to Their Recommendation"
-shorttitle        : "Recommendation Relates to Signing"
+shorttitle        : "Signing Open Reviews"
 author: 
@@
 author_note: |
- This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/jkbmw/
+ This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/9526a/
 abstract: |
  Surveys indicate that researchers are generally positive about making peer reviews available alongside published articles.
-Researchers are more negative about revealing the identity of reviewers, They worry reviewers will be less likely to express criticisms if their identity is known to authors.
-Experiments suggest that reviewers are somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
+Researchers are more negative about revealing the identity of reviewers.
+They worry reviewers will be less likely to express criticism if their identity is known to authors.
+Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be made known to authors, than when they will remain anonymous.
 One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
-We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science and Open Biology where authors can voluntarily make their identity known.
-Our results confirm that the probability that a reviewer reveals their identity is related to their recommendation.
-The more positive a recommendation was, the more likely it was that authors shared their identity.
-Although our data is correlational and does not allow causal conclusions, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
+We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews.
+These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers decision to sign is related to their recommendation.
+The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations.
 We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
@@
 This includes opening up the peer review process.
-An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve the peer review process [@bruce_impact_2016].
-Open peer review can be implemented by making peer reviews available, but also be revealing the identity of reviewers during or after the peer review process.
-An important argument for revealing the identity of reviewers is that they can receive credit for their work [@godlee_making_2002].
+An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve peer review [@bruce_impact_2016].
+Open peer review can be implemented by making peer reviews available, but also by revealing the identity of reviewers during or after the peer review process.
+An important argument in favour of revealing the identity of reviewers is that they can receive credit for their work [@godlee_making_2002].
 However, scientists do not feel these benefits outweigh possible costs, and are worried that criticism on manuscripts might lead to backlash from the authors in the future.
@@
 
-Researchers indicate that they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about manuscripts they believe are poor quality [@mulligan_peer_2013].
+Researchers self-report that they would be less likely to review for a journal if their identity is made public, and anecdotally mention that signed reviews would make it more difficult to be honest about manuscripts they believe are poor quality [@mulligan_peer_2013].
 A more recent survey found that 50.8% of almost 3000 scientists believe that revealing the identity of reviewers would make peer review worse [@ross-hellauer_survey_2017].
@@
 Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
-The trade-off between the benefit of getting credit for peer review work and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the most positive their recommendation is.
+The trade-off between the benefit of getting credit when performing peer reviews and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the more positive their recommendation is.
 If this strategic behavior occurs in practice, we should see a different pattern of recommendations for signed and unsigned reviews.
-One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, Journal of Hydrology: Regional Studies, and the International Journal of Surgery [@bravo_effect_2019].
+One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, the Journal of Hydrology: Regional Studies, and the International Journal of Surgery [@bravo_effect_2019].
 Although only 8.1% of reviewers choose to disclose their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
@@
 
-We examined the relationship between recommendations peer reviewer make and the probability that they have signed their review in two large open access journals, PeerJ and Royal Society Open Science and Open Biology.
+We examined the relationship between recommendations peer reviewer make and the probability that they signed their review in two large open access journals, PeerJ and Royal Society Open Science.
+In our analyses we reviews for PeerJ with reviews for PeerJ Computer Science, which started in 2015.
+We ignore more recently launched PeerJ journals in the field of Chemistry due to the small number of published articles in these journals.
+We combine reviews for Royal Society Open Biology (RSOB) in the analysis of reviews for the much larger Royal Society Open Science (RSOS).
 These journals publish across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
-To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as `r length(TRS_scopus_OS$DOI) + length(TRS_scopus_OB$DOI)` articles published in The Royal Society Open Science (RSOS) and Royal Society Open Biology (RSOB).
+To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as `r length(TRS_scopus_OS$DOI) + length(TRS_scopus_OB$DOI)` articles published in The Royal Society.
 PeerJ launched in 2012 and provides reviewers the possibility to sign, and provides authors the possibility to make peer reviews available with the final publication.
@@
 PeerJ assigns all articles a number, increasing consecutively with each published manuscript.
-Reviews are always accessible in html (i.e., at https://peerj.com/articles/1/reviews for the first article can be found).
-PeerJ has several more recent dedicated journals for computer science and chemistry.
-In the analyses reported here we included PeerJ Computer Science, which started in 2015, but ignore the chemistry journals that started at the end of 2019 due to the small number of published articles.
-For RSOS and RSOB reviews are published online as a PDF file.
-A list of Digital Object Identifiers (DOIs) for every article published in these two outlets was retrieved through Scopus.
-All reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R [@r_core_team_r_2013; @ooms_pdftools_2019].
-These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package in R [@wickham_stringr_2019].
+Reviews are always accessible in html (i.e., reviews for the first article published in PeerJ are available at https://peerj.com/articles/1/reviews).
+For Royal Society Open Science reviews are published online as a PDF file.
+A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
+All available reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R [@r_core_team_r_2013; @ooms_pdftools_2019].
+These text files were mined for recommendations, reviewer names, submission and acceptance dates, and the review content, using the stringr package in R [@wickham_stringr_2019].
 
 For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round.
-Note that for PeerJ the editor makes the recommendation for each revision, based on the reviews.
+Note that for PeerJ the editor makes the recommendation for each submission based on the reviews.
 We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
-For RSOS and RSOB reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
-Although 'reject' recommendations occur for RSOS and RSOB, both PeerJ, RSOS, and RSOB only share reviews for published articles, and therefore we have very few 'reject' recommendations in RSOS and RSOB, and none in PeerJ.
-Searching all reviews for PeerJ for the words 'appealed on' revealed 44 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
+For Royal Society reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
+Because PeerJ and Royal Society only share reviews for published articles there are few 'reject' recommendations reviews for Royal Scoiety and no 'reject' recommendations by editors among PeerJ reviews.
+Searching all reviews for PeerJ for the words 'appealed on' revealed 47 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
 We have coded these papers as 'major revisions'.
-All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at https://osf.io/jkbmw/.
+All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at https://osf.io/9526a/.
 
@@
 We examined `r 7930+225` articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles from Royal Society (`r length(TRS_scopus_OS$DOI)` from RSOS, `r length(TRS_scopus_OB$DOI)` from RSOB, `r errata_editorial` of which were editorials or errata) published up to October 2019.
-We retrieved all reviews when these were made available (`r nrow(PeerJ_unique)` articles in PeerJ, `r nrow(TRS_unique)` articles in Royal Society).
+We retrieved all reviews when these were made available (the reviews were available for `r nrow(PeerJ_unique)` articles in PeerJ, and `r nrow(TRS_unique)` articles in Royal Society).
 Articles can go through multiple rounds of review.
-We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following @bravo_effect_2019.
+We focus on the first review round in our analyses as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following @bravo_effect_2019.
 On average initial submissions at PeerJ received `r round(mean(count(PeerJ_data_R1, df_link)$n), 2)` reviews.
@@
 In Royal Society journals we analyzed `r nrow(TRS_unique)` articles for which we retrieved `r length(TRS_data_R1$df_anonymous)` unique reviews for the first submission, where `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their review, and `r sum(TRS_data_R1$df_anonymous == 1)` did not.
-The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for Royal Society) are slightly lower than the 43.23% reported by [@wang_open_2016], who analyzed the first 1214 articles published in PeerJ.
+The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for Royal Society) are slightly lower than the 43.23% reported by @wang_open_2016 who analyzed the first 1214 articles published in PeerJ.
 
-To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
+To answer our main research question we plotted the signed an unsigned reviews for PeerJ as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
 Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer.
@@
 
-```{r, PeerJrec, fig.cap = "Proportions of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended 'minor revisions' or 'major revisions'."}
+```{r, PeerJrec, fig.cap = "Proportion of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended 'minor revisions' or 'major revisions'."}
 
@@
 
-```{r, TRSrec, fig.cap = "Proportions of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
+```{r, TRSrec, fig.cap = "Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
 
@@
 Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-Although we had access to few 'reject' recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by @bravo_effect_2019 across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteers to disclose their identity.
-This replication suggests the difference in recommendations depending on whether reviews are signed or not is a reliable observation.
+Although we had access to few 'reject' recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by @bravo_effect_2019 across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteer to disclose their identity.
+This replication suggests that the difference in recommendations depending on whether reviews are signed or not is a rather reliable observation.
 
@@
 Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
-For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
-With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (@wang_open_2016) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews (see Figure \ref{fig:wordcount}).
-
-```{r wordcount, fig.cap = "Word count for reviews for first submission at Royal Society journals as a factor of the recommendation."}
-# Word counts PeerJ
-
-# words <- by(PeerJ_data_R1$df_word_count, PeerJ_data_R1[,c(5,7)], mean, simplify = TRUE)
-# 
-# plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "accept", "minor revision", "major revision"), levels = c("accept", "minor revision", "major revision")),
-#                    c("signed", "signed", "signed", "unsigned", "unsigned", "unsigned"),
-#                    c(words))
-# colnames(plot_data) <- c("recommendation", "signed", "word count")
-# 
-# ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
-#   geom_bar(position="dodge", stat="identity") +
-#   theme_linedraw(base_size = 20)
-# 
-# ggplot(PeerJ_data_R1, aes(x = df_recommendation, y = df_word_count, fill = as.factor(df_anonymous))) + 
-#   geom_bar(position="dodge", stat="identity") +
-#   theme_linedraw(base_size = 20)
-# 
-# t.test(PeerJ_data_R1$df_word_count ~ PeerJ_data_R1$df_anonymous)
-
-# Words count RSOS
-#
-
-words <- by(TRS_data_R1$df_word_count, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)
-
-plot_data <- data.frame(factor(c("accept", "minor", "major", "reject", "accept", "minor", "major", "reject"), levels = c("accept", "minor", "major", "reject")),
-                   c("signed", "signed", "signed", "signed", "unsigned", "unsigned", "unsigned", "unsigned"),
-                   c(words))
-colnames(plot_data) <- c("recommendation", "signed", "wordcount")
-
-ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
-  geom_bar(position="dodge", stat="identity") +
-  theme_linedraw(base_size = 20) + 
-  theme(legend.position = "top",
-        legend.title=element_blank(),
-        panel.grid.major.x = element_blank()) + 
-  scale_fill_manual(values = c("#000000", "#808080")) + 
-  coord_cartesian(ylim = c(0, 750)) +
-  geom_text(aes(label = round(wordcount,0)), 
-              size = 6, 
-              color = "black",
-              position = position_dodge(width = 0.9),
-              vjust = -.5) +
-  labs(y = "word count")
-
-# When tested, the difference is not significant
-# t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)
-```
-
 Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
-For the `r sum(table(rev_dif))` papers where te reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (s0 `r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
+For the `r sum(table(rev_dif))` papers where te reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
 For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
@@
 Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.
-Thus, even though the proportion of reject recommendation in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datsets that include rejected manuscripts.
+Thus, even though the proportion of reject recommendations in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datasets that include rejected manuscripts.
 
@@
 This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs.
-For positive recommendations, reviewers will get credit for their reviews, while for negative reviews, they do not run the risk of receiving any backlash from colleagues in their field.
+For positive recommendations, reviewers will get credit for their reviews, while for negative reviews they do not run the risk of receiving any backlash from colleagues in their field.
 
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation [@bastian_signing_2018].
-Although the available data suggests that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign more positive recommendations to get credit for their work, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their, regardless of whether their recommendation is positive or negative.
+Based on all available research is seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
+Therefore, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their reviews, regardless of whether their recommendation is positive or negative.
 
@@
 Lakens developed the idea, and jointly created the R code to generate and analyze the data.
-N van Sambeek drafted the initial version of the manuscript as a Bachelor thesis, D.
+N.
+van Sambeek drafted the initial version of the manuscript as a Bachelor thesis, D.
 Lakens drafted the final version, and both authors revised the final version of the manuscript.
@@
 ```{r, include = FALSE}
-### general numbers
-sum(PeerJ_data_R1$df_anonymous == 0) # how many reviews for first submissions are not anonymous?
-sum(PeerJ_data_R1$df_anonymous == 1) # how many reviews for first submissions are anonymous?
+# Reviewer 2 is not evil
 
-prop_data <- cbind(PeerJ_anonymous_by_recommendation[2:3], PeerJ_notanonymous_by_recommendation[2:3]) #bind as matrix
+# sum number of responses by subgroup using the by command in base R
+TRS_reviewer1_recommendation <- by(TRS_data_R1$df_reviewer_number == 1, TRS_data_R1$df_recommendation, sum)
+
+TRS_reviewer2_recommendation <- by(TRS_data_R1$df_reviewer_number == 2, TRS_data_R1$df_recommendation, sum)
+
+# Makes more sense to plot proportions
+TRS_reviewer1_recommendation_proportion <- TRS_reviewer1_recommendation/sum(TRS_reviewer1_recommendation)
+TRS_reviewer2_recommendation_proportion <- TRS_reviewer2_recommendation/sum(TRS_reviewer2_recommendation)
+
+#create plot data for accept, minor, major recommendations
+plot_data <- data.frame(factor(c("accept", "minor", "major", "reject", "accept", "minor", "major", "reject"), levels = c("accept", "minor", "major", "reject")),
+                   c("reviewer 1", "reviewer 1", "reviewer 1", "reviewer 1", "reviewer 2", "reviewer 2", "reviewer 2", "reviewer 2"),
+                   c(TRS_reviewer1_recommendation_proportion, TRS_reviewer2_recommendation_proportion))
+colnames(plot_data) <- c("recommendation", "reviewer", "count")
+
+ggplot(plot_data, aes(x = recommendation, y = count, fill = reviewer)) + 
+  geom_bar(position="dodge", stat="identity") +
+  theme_linedraw(base_size = 20) + 
+  theme(legend.position = "top",
+        legend.title=element_blank(),
+        panel.grid.major.x = element_blank()) + 
+  scale_fill_manual(values = c("#000000", "#808080")) + 
+  coord_cartesian(ylim = c(0, 1)) +
+  geom_text(aes(label = sprintf('%.2f',count)), 
+              size = 6, 
+              color = "black",
+              position = position_dodge(width = 0.9),
+              vjust = -.5)
+
+prop_data <- cbind(TRS_reviewer1_recommendation[2:3], TRS_reviewer2_recommendation[2:3]) #bind as matrix
 rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("anonymous", "not anonymous") #add row names
+colnames(prop_data) <- c("reviewer1", "reviewer2") #add row names
 # Test of these different proportions
@@
 
-# In proportions
-# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
-# Calculate proportions
-1-as.vector(PeerJ_notanonymous_by_recommendation/(PeerJ_notanonymous_by_recommendation + PeerJ_anonymous_by_recommendation))
-
-prop_data <- cbind(TRS_anonymous_by_recommendation[2:3], TRS_notanonymous_by_recommendation[2:3]) #bind as matrix
-rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("unsigned", "signed") #add row names
-
-# In proportions
-# 2061 is 53.6% of a total of 3843 articles that receive a minor revision at the first review are anonymous (and 46.4% is not anonymous), for a major revision, 65.4% (4495 out of 6876) is anonymous, 34.6% is not anonymous.
-680/(680+524)
-178/(178+83)
-
-# Test of these different proportions
-prop.test(prop_data) #perform test of proportions
-
-prop_data <- cbind(TRS_anonymous_by_recommendation[c(1,3)], TRS_notanonymous_by_recommendation[c(1,3)]) #bind as matrix
-rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("unsigned", "notanonymous") #add row names
-prop.test(prop_data) #perform test of proportions
-
-prop_data <- cbind(TRS_anonymous_by_recommendation[c(1,2)], TRS_notanonymous_by_recommendation[c(1,2)]) #bind as matrix
-rownames(prop_data) <- c("minor revision", "major revision") #add column names
-colnames(prop_data) <- c("unsigned", "notanonymous") #add row names
-prop.test(prop_data) #perform test of proportions
-
-# Calculate proportions
-1-as.vector(TRS_notanonymous_by_recommendation/(TRS_notanonymous_by_recommendation + TRS_anonymous_by_recommendation))
-
-# Analyze words
-# TRS
-words <- by(TRS_data_R1$df_word_count, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)
-
-plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
-                   c("signed", "signed", "signed", "signed", "unsigned", "unsigned", "unsigned", "unsigned"),
-                   c(words))
-colnames(plot_data) <- c("recommendation", "signed", "wordcount")
-
-ggplot(plot_data, aes(x = recommendation, y = wordcount, fill = signed)) + 
-  geom_bar(position="dodge", stat="identity") +
-  theme_linedraw(base_size = 20)
-
-t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)
-
-# Exploratory
-# Randomly split anonymous over 100 subgroups to see progression over time - seems stable.
-df_over_time <- data.frame(TRS_data$df_anonymous[1:3600], rep(seq(1,100,1),each = 360))
-colnames(df_over_time) <- c("anonymous", "time") # specify columns names
-x <- group_by(df_over_time, time)
-x <- summarize(x, m = mean(anonymous))
-
-df_over_time <- data.frame(PeerJ_data$df_anonymous[1:12300], rep(seq(1,100,1),each = 1230))
-colnames(df_over_time) <- c("anonymous", "time") # specify columns names
-x <- group_by(df_over_time, time)
-x <- summarize(x, m = mean(anonymous))
-
-# Analysis total review time
-# TRS
-review_time <- by(TRS_data_R1$df_days, TRS_data_R1[,c(5,7)], mean, simplify = TRUE)
-
-plot_data <- data.frame(factor(c("accept", "minor revision", "major revision", "reject", "accept", "minor revision", "major revision", "reject"), levels = c("accept", "minor revision", "major revision", "reject")),
-                   c("signed", "signed", "signed", "signed", "unsigned", "unsigned", "unsigned", "unsigned"),
-                   c(review_time))
-colnames(plot_data) <- c("recommendation", "signed", "days")
-
-ggplot(plot_data, aes(x = recommendation, y = days, fill = signed)) + 
-  geom_bar(position="dodge", stat="identity") +
-  theme_linedraw(base_size = 20)
-
-t.test(TRS_data_R1$df_word_count ~ TRS_data_R1$df_anonymous)
-
-heroes <- filter(TRS_data_R1, df_anonymous == 0 & df_recommendation == 4)
-filter(PeerJ_data, df_anonymous == 0 & df_reviewer_name == "Daniel Lakens")
-
-me <- filter(TRS_data, df_anonymous == 0)
-me <- me[ with( me , order ( df_reviewer_name)),]
-
-##data from Walsh et al 
-##
-41/(41+36) #accept
-53/(53+35) #accept revision
-43/(43+31) #resubmit with revision
-30/(30+51) #reject
-
 ```

### 2019-10-28 open_peer_review.tex
preprint

@@
 
-\shorttitle{Recommendation Relates to Signing}
+\shorttitle{Researchers Decision to Sign Reviews is Related to Their Recommendation}
 \affiliation{
@@
 \authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All data underlying this reproducible manuscript are available at \url{https://osf.io/jkbmw/}
+All data underlying this reproducible manuscript are available at \url{https://osf.io/9526a/}
 
@@
 Surveys indicate that researchers are generally positive about making peer reviews available alongside published articles.
-Researchers are more negative about revealing the identity of reviewers, They worry reviewers will be less likely to express criticisms if their identity is known to authors.
-Experiments suggest that reviewers are somewhat more likely to recommend to accept articles when they are told their name will be shared alongside the reviews, than when they will remain anonymous.
+Researchers are more negative about revealing the identity of reviewers.
+They worry reviewers will be less likely to express criticism if their identity is known to authors.
+Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be made known to authors, than when they will remain anonymous.
 One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
-We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science and Open Biology where authors can voluntarily make their identity known.
-Our results confirm that the probability that a reviewer reveals their identity is related to their recommendation.
-The more positive a recommendation was, the more likely it was that authors shared their identity.
-Although our data is correlational and does not allow causal conclusions, it provides behavioral data from real peer reviews that demonstrates convincingly that reviewers who sign their reviews give more positive recommendations.
+We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews.
+These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers decision to sign is related to their recommendation.
+The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations.
 We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
@@
 This includes opening up the peer review process.
-An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve the peer review process (Bruce, Chauvin, Trinquart, Ravaud, \& Boutron, 2016).
-Open peer review can be implemented by making peer reviews available, but also be revealing the identity of reviewers during or after the peer review process.
-An important argument for revealing the identity of reviewers is that they can receive credit for their work (Godlee, 2002).
+An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve peer review (Bruce, Chauvin, Trinquart, Ravaud, \& Boutron, 2016).
+Open peer review can be implemented by making peer reviews available, but also by revealing the identity of reviewers during or after the peer review process.
+An important argument in favour of revealing the identity of reviewers is that they can receive credit for their work (Godlee, 2002).
 However, scientists do not feel these benefits outweigh possible costs, and are worried that criticism on manuscripts might lead to backlash from the authors in the future.
@@
 
-Researchers indicate that they would be less likely to review for a journal if their names are made public, and anecdotally mention that signed reviews would make it more difficult to be honest about manuscripts they believe are poor quality (Mulligan, Hall, \& Raphael, 2013).
+Researchers self-report that they would be less likely to review for a journal if their identity is made public, and anecdotally mention that signed reviews would make it more difficult to be honest about manuscripts they believe are poor quality (Mulligan, Hall, \& Raphael, 2013).
 A more recent survey found that 50.8\% of almost 3000 scientists believe that revealing the identity of reviewers would make peer review worse (Ross-Hellauer, Deppe, \& Schmidt, 2017).
@@
 Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
-The trade-off between the benefit of getting credit for peer review work and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the most positive their recommendation is.
+The trade-off between the benefit of getting credit when performing peer reviews and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the more positive their recommendation is.
 If this strategic behavior occurs in practice, we should see a different pattern of recommendations for signed and unsigned reviews.
-One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, Journal of Hydrology: Regional Studies, and the International Journal of Surgery (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
+One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, the Journal of Hydrology: Regional Studies, and the International Journal of Surgery (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
 Although only 8.1\% of reviewers choose to disclose their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
@@
 
-We examined the relationship between recommendations peer reviewer make and the probability that they have signed their review in two large open access journals, PeerJ and Royal Society Open Science and Open Biology.
+We examined the relationship between recommendations peer reviewer make and the probability that they signed their review in two large open access journals, PeerJ and Royal Society Open Science.
+In our analyses we reviews for PeerJ with reviews for PeerJ Computer Science, which started in 2015.
+We ignore more recently launched PeerJ journals in the field of Chemistry due to the small number of published articles in these journals.
+We combine reviews for Royal Society Open Biology (RSOB) in the analysis of reviews for the much larger Royal Society Open Science (RSOS).
 These journals publish across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
-To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as 3576 articles published in The Royal Society Open Science (RSOS) and Royal Society Open Biology (RSOB).
+To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as 3576 articles published in The Royal Society.
 PeerJ launched in 2012 and provides reviewers the possibility to sign, and provides authors the possibility to make peer reviews available with the final publication.
@@
 PeerJ assigns all articles a number, increasing consecutively with each published manuscript.
-Reviews are always accessible in html (i.e., at \url{https://peerj.com/articles/1/reviews} for the first article can be found).
-PeerJ has several more recent dedicated journals for computer science and chemistry.
-In the analyses reported here we included PeerJ Computer Science, which started in 2015, but ignore the chemistry journals that started at the end of 2019 due to the small number of published articles.
-For RSOS and RSOB reviews are published online as a PDF file.
-A list of Digital Object Identifiers (DOIs) for every article published in these two outlets was retrieved through Scopus.
-All reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2019; R Core Team, 2013).
-These text files were mined for recommendations, reviewers names, submission and acceptance dates, and the review content, using the stringr package in R (Wickham, 2019).
+Reviews are always accessible in html (i.e., reviews for the first article published in PeerJ are available at \url{https://peerj.com/articles/1/reviews}).
+For Royal Society Open Science reviews are published online as a PDF file.
+A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
+All available reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2019; R Core Team, 2013).
+These text files were mined for recommendations, reviewer names, submission and acceptance dates, and the review content, using the stringr package in R (Wickham, 2019).
 
 For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round.
-Note that for PeerJ the editor makes the recommendation for each revision, based on the reviews.
+Note that for PeerJ the editor makes the recommendation for each submission based on the reviews.
 We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
-For RSOS and RSOB reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
-Although \enquote{reject} recommendations occur for RSOS and RSOB, both PeerJ, RSOS, and RSOB only share reviews for published articles, and therefore we have very few \enquote{reject} recommendations in RSOS and RSOB, and none in PeerJ.
-Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 44 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
+For Royal Society reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
+Because PeerJ and Royal Society only share reviews for published articles there are few \enquote{reject} recommendations reviews for Royal Scoiety and no \enquote{reject} recommendations by editors among PeerJ reviews.
+Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 47 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
 We have coded these papers as \enquote{major revisions}.
-All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at \url{https://osf.io/jkbmw/}.
+All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at \url{https://osf.io/9526a/}.
 
@@
 We examined 8155 articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as 3576 articles from Royal Society (2887 from RSOS, 689 from RSOB, 81 of which were editorials or errata) published up to October 2019.
-We retrieved all reviews when these were made available (5087 articles in PeerJ, 1964 articles in Royal Society).
+We retrieved all reviews when these were made available (the reviews were available for 5087 articles in PeerJ, and 1964 articles in Royal Society).
 Articles can go through multiple rounds of review.
-We focus on the first review round as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following Bravo et al.
+We focus on the first review round in our analyses as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following Bravo et al.
 (2019).
@@
 In Royal Society journals we analyzed 1964 articles for which we retrieved 4188 unique reviews for the first submission, where 1549 reviewers signed their review, and 2639 did not.
-The percentages of people who sign (38.23\% for PeerJ, 36.99\% for Royal Society) are slightly lower than the 43.23\% reported by (Wang, You, Manasa, \& Wolfram, 2016), who analyzed the first 1214 articles published in PeerJ.
+The percentages of people who sign (38.23\% for PeerJ, 36.99\% for Royal Society) are slightly lower than the 43.23\% reported by Wang, You, Manasa, and Wolfram (2016) who analyzed the first 1214 articles published in PeerJ.
 
-To answer our main research question we plotted the signed an unsigned reviews as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
+To answer our main research question we plotted the signed an unsigned reviews for PeerJ as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
 Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer.
@@
 \includegraphics{open_peer_review_files/figure-latex/PeerJrec-1.pdf}
-\caption{\label{fig:PeerJrec}Proportions of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended \enquote{minor revisions} or \enquote{major revisions}.}
+\caption{\label{fig:PeerJrec}Proportion of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended \enquote{minor revisions} or \enquote{major revisions}.}
 \end{figure}
@@
 \includegraphics{open_peer_review_files/figure-latex/TRSrec-1.pdf}
-\caption{\label{fig:TRSrec}Proportions of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
+\caption{\label{fig:TRSrec}Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
 \end{figure}
@@
 Although we had access to few \enquote{reject} recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by Bravo et al.
-(2019) across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteers to disclose their identity.
-This replication suggests the difference in recommendations depending on whether reviews are signed or not is a reliable observation.
+(2019) across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteer to disclose their identity.
+This replication suggests that the difference in recommendations depending on whether reviews are signed or not is a rather reliable observation.
 
@@
 Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
-For example, we can examine the word count for signed and unsigned reviews as a function of the recommendation.
-With the caveat that the graph below present uncleaned raw word counts, we replicate the results reported by (Wang et al.
-(2016)) for PeerJ in the dataset for Royal Society Open Science and Open Biology that there is no statistical difference between the word count for signed and unsigned reviews, despite a small numerical difference in the same direction as in their analysis of PeerJ reviews (see Figure \ref{fig:wordcount}).
-
-\begin{figure}
-\centering
-\includegraphics{open_peer_review_files/figure-latex/wordcount-1.pdf}
-\caption{\label{fig:wordcount}Word count for reviews for first submission at Royal Society journals as a factor of the recommendation.}
-\end{figure}
-
 Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
-For the 1963 papers where te reviews were published, all reviewers agreed on the recommendation for 830 articles (s0 42.28\% of the time).
+For the 1963 papers where te reviews were published, all reviewers agreed on the recommendation for 830 articles (42.28\% of the time).
 For 41.72\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.37\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.63\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
@@
 (2019) who had access to the reviews for accepted and rejected manuscripts.
-Thus, even though the proportion of reject recommendation in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datsets that include rejected manuscripts.
+Thus, even though the proportion of reject recommendations in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datasets that include rejected manuscripts.
 
@@
 This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs.
-For positive recommendations, reviewers will get credit for their reviews, while for negative reviews, they do not run the risk of receiving any backlash from colleagues in their field.
+For positive recommendations, reviewers will get credit for their reviews, while for negative reviews they do not run the risk of receiving any backlash from colleagues in their field.
 
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation (Bastian, 2018).
-Although the available data suggests that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign more positive recommendations to get credit for their work, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their, regardless of whether their recommendation is positive or negative.
+Based on all available research is seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
+Therefore, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their reviews, regardless of whether their recommendation is positive or negative.
 

### 2019-10-29 open_peer_review.Rmd
preprint done

@@
 ---
-title             : "Researchers Decision to Sign Reviews is Related to Their Recommendation"
+title             : "Reviewers' Decision to Sign Reviews is Related to Their Recommendation"
 shorttitle        : "Signing Open Reviews"
@@
 abstract: |
- Surveys indicate that researchers are generally positive about making peer reviews available alongside published articles.
+ Surveys indicate that researchers generally have a positive attitude towards open peer review when this consists of making reviews available alongside published articles.
 Researchers are more negative about revealing the identity of reviewers.
 They worry reviewers will be less likely to express criticism if their identity is known to authors.
-Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be made known to authors, than when they will remain anonymous.
-One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
+Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be communicated to authors, than when they will remain anonymous.
+One recent study revealed reviewers in five journals who voluntarily signed their reviews gave more positive recommendations than those who did not sign their reviews.
 We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews.
-These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers decision to sign is related to their recommendation.
+These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers' decision to sign is related to their recommendation.
 The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations.
@@
 
-keywords          : "Peer Review, Open Science, Transparency"
+keywords          : "Peer Review, Open Reviews, Transparency, Open Science"
 wordcount         : 2711
@@
 As technology advances, science advances.
-The rise of the internet has made it possible to share all aspects of the scientific process.
+The rise of the internet has made it possible to transparently share all steps in the scientific process [@spellman_short_2015].
 This includes opening up the peer review process.
@@
 However, scientists do not feel these benefits outweigh possible costs, and are worried that criticism on manuscripts might lead to backlash from the authors in the future.
-Some reviewers might accept these consequences, while other might choose to strategically reveal their identity only for positive reviews they write.
+Some reviewers might accept these negative consequences, while other might choose to strategically reveal their identity only for positive reviews they write.
 
@@
 One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, the Journal of Hydrology: Regional Studies, and the International Journal of Surgery [@bravo_effect_2019].
-Although only 8.1% of reviewers choose to disclose their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
+Although only 8.1% of reviewers voluntarily disclosed their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not sign.
 
@@
 
-We examined the relationship between recommendations peer reviewer make and the probability that they signed their review in two large open access journals, PeerJ and Royal Society Open Science.
-In our analyses we reviews for PeerJ with reviews for PeerJ Computer Science, which started in 2015.
-We ignore more recently launched PeerJ journals in the field of Chemistry due to the small number of published articles in these journals.
-We combine reviews for Royal Society Open Biology (RSOB) in the analysis of reviews for the much larger Royal Society Open Science (RSOS).
-These journals publish across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
-To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as `r length(TRS_scopus_OS$DOI) + length(TRS_scopus_OB$DOI)` articles published in The Royal Society.
-PeerJ launched in 2012 and provides reviewers the possibility to sign, and provides authors the possibility to make peer reviews available with the final publication.
-RSOS launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication, and made this mandatory in January 2019.
-RSOB made sharing reviews with the final publication mandatory in May 2017.
+We examined the relationship between recommendations peer reviewers make and the probability that they signed their review in two large open access journals, PeerJ (including reviews for PeerJ Computer Science) and Royal Society Open Science (including Royal Society Open Biology).
+We ignored more recently launched PeerJ journals in the field of Chemistry due to the small number of articles published to date in these journals.
+PeerJ and Royal Society publish articles across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
+PeerJ launched in 2012 and PeerJ Computer Science launched in 2015.
+PeerJ provides reviewers the possibility to sign, and authors the possibility to make peer reviews available with the final publication.
+Royal Society Open Science (RSOS) launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication, and made this mandatory in January 2019.
+Royal Society Open Biology (RSOB) made sharing reviews with the final publication mandatory in May 2017.
 Peer reviewers have the option to make their identity known when submitting their review to RSOS or RSOB.
-Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, these reviews provide insights into the peer review behavior of scientists across a wide range of disciplines.
+Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, the reviews for PeerJ and Royal Society provide insights into the peer review behavior of scientists across a wide range of disciplines.
 
@@
 Reviews are always accessible in html (i.e., reviews for the first article published in PeerJ are available at https://peerj.com/articles/1/reviews).
-For Royal Society Open Science reviews are published online as a PDF file.
+For Royal Society reviews are published online as a PDF file.
 A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
@@
 For Royal Society reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
-Because PeerJ and Royal Society only share reviews for published articles there are few 'reject' recommendations reviews for Royal Scoiety and no 'reject' recommendations by editors among PeerJ reviews.
+Because PeerJ and Royal Society only share reviews for published articles there are few 'reject' recommendations for Royal Scoiety and no 'reject' recommendations by editors among PeerJ reviews.
 Searching all reviews for PeerJ for the words 'appealed on' revealed 47 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
@@
 
-We examined `r 7930+225` articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles from Royal Society (`r length(TRS_scopus_OS$DOI)` from RSOS, `r length(TRS_scopus_OB$DOI)` from RSOB, `r errata_editorial` of which were editorials or errata) published up to October 2019.
+We examined `r 7930+225` articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles from Royal Society (`r length(TRS_scopus_OS$DOI)` from RSOS, `r length(TRS_scopus_OB$DOI)` from RSOB, `r errata_editorial` of which were editorials or errata without reviews) published up to October 2019.
 We retrieved all reviews when these were made available (the reviews were available for `r nrow(PeerJ_unique)` articles in PeerJ, and `r nrow(TRS_unique)` articles in Royal Society).
@@
 
-For all `r nrow(PeerJ_unique)` articles published in PeerJ where reviews were available we retrieved `r length(PeerJ_data_R1$df_anonymous)` unique reviews (as each article is typically reviewed by multiple reviewers) for the initial submission.
+For all `r nrow(PeerJ_unique)` articles published in PeerJ where reviews were available we retrieved `r length(PeerJ_data_R1$df_anonymous)` unique reviews for the initial submission (as each article is typically reviewed by multiple reviewers).
 In total `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their review for the initial submission, and `r sum(PeerJ_data_R1$df_anonymous == 1)` reviewers did not.
@@
 
-```{r, TRSrec, fig.cap = "Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
+```{r, TRSrec, fig.cap = "Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
 
@@
 Based on the literature reviewed in the introduction we know researchers are hesitant to voice criticism when their identity will be known, and experimental evidence suggests that if identities are shared with authors, recommendations become somewhat more positive.
-Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-Although we had access to few 'reject' recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by @bravo_effect_2019 across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteer to disclose their identity.
+Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign more positive reviews.
+Although we had access to few 'reject' recommendations because we could only access reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by @bravo_effect_2019 across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteer to disclose their identity.
 This replication suggests that the difference in recommendations depending on whether reviews are signed or not is a rather reliable observation.
@@
 
-The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for RSOS and RSOB).
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for Royal Society).
 Through the DOI, researchers can link this data to other sources of information such as citation counts.
@@
 Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
-For the `r sum(table(rev_dif))` papers where te reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
+For the `r sum(table(rev_dif))` papers where the reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
 For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
@@
 
-Regrettably, neither PeerJ nor RSOS make peer reviews available for manuscripts that were rejected.
+Regrettably, neither PeerJ nor Royal Society make peer reviews available for manuscripts that were rejected.
 As a consequence, we have analyzed a biased sample of the literature.
-At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
+Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
 Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
 Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.
-Thus, even though the proportion of reject recommendations in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datasets that include rejected manuscripts.
 
@@
 Our analysis shows that when authors are given the choice to sign their reviews, signed reviews have more positive recommendations than unsigned reviews.
-This pattern is clearly present for reviews in Royal Society Open Science, a large multi-disciplinary journal that published across a wide range of scientific domains.
+This pattern is clearly present for reviews in Royal Society Open Science and Open Biology, a large multi-disciplinary journal that published across a wide range of scientific domains.
 The pattern is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
@@
 Lakens drafted the final version, and both authors revised the final version of the manuscript.
+
+# Competing interests
+
 The authors report no conflicts of interest.
@@
 ```{r, include = FALSE}
-# Reviewer 2 is not evil
+# Easter Egg: Reviewer 2 is not evil
 
@@
 
-#create plot data for accept, minor, major recommendations
+#create plot data for accept, minor, major, accept recommendations
 plot_data <- data.frame(factor(c("accept", "minor", "major", "reject", "accept", "minor", "major", "reject"), levels = c("accept", "minor", "major", "reject")),
@@
 
+# Is there a difference in recommendation between reviewer numbers? 
 prop_data <- cbind(TRS_reviewer1_recommendation[2:3], TRS_reviewer2_recommendation[2:3]) #bind as matrix
@@
 prop.test(prop_data) #perform test of proportions
-
 ```

### 2019-10-29 open_peer_review.tex
preprint done

@@
 \hypersetup{unicode=true,
-            pdftitle={Researchers Decision to Sign Reviews is Related to Their Recommendation},
+            pdftitle={Reviewers' Decision to Sign Reviews is Related to Their Recommendation},
             pdfauthor={Nino van Sambeek~\& Daniël Lakens},
-            pdfkeywords={Peer Review, Open Science, Transparency},
+            pdfkeywords={Peer Review, Open Reviews, Transparency, Open Science},
             pdfborder={0 0 0},
@@
 
-  \title{Researchers Decision to Sign Reviews is Related to Their Recommendation}
+  \title{Reviewers' Decision to Sign Reviews is Related to Their Recommendation}
     \author{Nino van Sambeek\textsuperscript{1}~\& Daniël Lakens\textsuperscript{1}}
@@
 
-\shorttitle{Researchers Decision to Sign Reviews is Related to Their Recommendation}
+\shorttitle{Signing Open Reviews}
 \affiliation{
@@
 \textsuperscript{1} Eindhoven University of Technology, The Netherlands}
-\keywords{Peer Review, Open Science, Transparency\newline\indent Word count: 2711}
+\keywords{Peer Review, Open Reviews, Transparency, Open Science\newline\indent Word count: 2711}
 \usepackage{csquotes}
@@
 \abstract{
-Surveys indicate that researchers are generally positive about making peer reviews available alongside published articles.
+Surveys indicate that researchers generally have a positive attitude towards open peer review when this consists of making reviews available alongside published articles.
 Researchers are more negative about revealing the identity of reviewers.
 They worry reviewers will be less likely to express criticism if their identity is known to authors.
-Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be made known to authors, than when they will remain anonymous.
-One recent study revealed reviewers in five journals gave more positive recommendations when during a peer review experiment their identity would be made available to authors.
+Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be communicated to authors, than when they will remain anonymous.
+One recent study revealed reviewers in five journals who voluntarily signed their reviews gave more positive recommendations than those who did not sign their reviews.
 We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews.
-These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers decision to sign is related to their recommendation.
+These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers' decision to sign is related to their recommendation.
 The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations.
@@
 As technology advances, science advances.
-The rise of the internet has made it possible to share all aspects of the scientific process.
+The rise of the internet has made it possible to transparently share all steps in the scientific process (Spellman, 2015).
 This includes opening up the peer review process.
@@
 One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, the Journal of Hydrology: Regional Studies, and the International Journal of Surgery (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
-Although only 8.1\% of reviewers choose to disclose their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not choose to sign.
+Although only 8.1\% of reviewers voluntarily disclosed their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not sign.
 
@@
 
-We examined the relationship between recommendations peer reviewer make and the probability that they signed their review in two large open access journals, PeerJ and Royal Society Open Science.
-In our analyses we reviews for PeerJ with reviews for PeerJ Computer Science, which started in 2015.
-We ignore more recently launched PeerJ journals in the field of Chemistry due to the small number of published articles in these journals.
-We combine reviews for Royal Society Open Biology (RSOB) in the analysis of reviews for the much larger Royal Society Open Science (RSOS).
-These journals publish across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
-To examine the pattern of recommendations as a function of whether reviewers signed their review or not we analyzed 7930 articles published in PeerJ, as well as 3576 articles published in The Royal Society.
-PeerJ launched in 2012 and provides reviewers the possibility to sign, and provides authors the possibility to make peer reviews available with the final publication.
-RSOS launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication, and made this mandatory in January 2019.
-RSOB made sharing reviews with the final publication mandatory in May 2017.
+We examined the relationship between recommendations peer reviewers make and the probability that they signed their review in two large open access journals, PeerJ (including reviews for PeerJ Computer Science) and Royal Society Open Science (including Royal Society Open Biology).
+We ignored more recently launched PeerJ journals in the field of Chemistry due to the small number of articles published to date in these journals.
+PeerJ and Royal Society publish articles across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
+PeerJ launched in 2012 and PeerJ Computer Science launched in 2015.
+PeerJ provides reviewers the possibility to sign, and authors the possibility to make peer reviews available with the final publication.
+Royal Society Open Science (RSOS) launched in 2014 and strongly encouraged authors to make the peer reviews available with the final publication, and made this mandatory in January 2019.
+Royal Society Open Biology (RSOB) made sharing reviews with the final publication mandatory in May 2017.
 Peer reviewers have the option to make their identity known when submitting their review to RSOS or RSOB.
-Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, these reviews provide insights into the peer review behavior of scientists across a wide range of disciplines.
+Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, the reviews for PeerJ and Royal Society provide insights into the peer review behavior of scientists across a wide range of disciplines.
 
@@
 Reviews are always accessible in html (i.e., reviews for the first article published in PeerJ are available at \url{https://peerj.com/articles/1/reviews}).
-For Royal Society Open Science reviews are published online as a PDF file.
+For Royal Society reviews are published online as a PDF file.
 A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
@@
 For Royal Society reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
-Because PeerJ and Royal Society only share reviews for published articles there are few \enquote{reject} recommendations reviews for Royal Scoiety and no \enquote{reject} recommendations by editors among PeerJ reviews.
+Because PeerJ and Royal Society only share reviews for published articles there are few \enquote{reject} recommendations for Royal Scoiety and no \enquote{reject} recommendations by editors among PeerJ reviews.
 Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 47 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
@@
 
-We examined 8155 articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as 3576 articles from Royal Society (2887 from RSOS, 689 from RSOB, 81 of which were editorials or errata) published up to October 2019.
+We examined 8155 articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as 3576 articles from Royal Society (2887 from RSOS, 689 from RSOB, 81 of which were editorials or errata without reviews) published up to October 2019.
 We retrieved all reviews when these were made available (the reviews were available for 5087 articles in PeerJ, and 1964 articles in Royal Society).
@@
 
-For all 5087 articles published in PeerJ where reviews were available we retrieved 12010 unique reviews (as each article is typically reviewed by multiple reviewers) for the initial submission.
+For all 5087 articles published in PeerJ where reviews were available we retrieved 12010 unique reviews for the initial submission (as each article is typically reviewed by multiple reviewers).
 In total 4592 reviewers signed their review for the initial submission, and 7418 reviewers did not.
@@
 \includegraphics{open_peer_review_files/figure-latex/TRSrec-1.pdf}
-\caption{\label{fig:TRSrec}Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society Open Science or Open Biology recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
+\caption{\label{fig:TRSrec}Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
 \end{figure}
@@
 Based on the literature reviewed in the introduction we know researchers are hesitant to voice criticism when their identity will be known, and experimental evidence suggests that if identities are shared with authors, recommendations become somewhat more positive.
-Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign their more positive reviews.
-Although we had access to few \enquote{reject} recommendations because we only analyzed reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by Bravo et al.
+Therefore, it seems plausible that at least part of the pattern we observed can be explained by reviewers being more likely to sign more positive reviews.
+Although we had access to few \enquote{reject} recommendations because we could only access reviews for published manuscripts, the difference between signed and unsigned reviews for major revisions, minor revisions, and accept recommendations replicates the findings by Bravo et al.
 (2019) across a larger range of research fields, based on a larger dataset, and in journals where a larger percentage of reviewers volunteer to disclose their identity.
@@
 
-The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for RSOS and RSOB).
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for Royal Society).
 Through the DOI, researchers can link this data to other sources of information such as citation counts.
@@
 Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
-For the 1963 papers where te reviews were published, all reviewers agreed on the recommendation for 830 articles (42.28\% of the time).
+For the 1963 papers where the reviews were published, all reviewers agreed on the recommendation for 830 articles (42.28\% of the time).
 For 41.72\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.37\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.63\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
@@
 
-Regrettably, neither PeerJ nor RSOS make peer reviews available for manuscripts that were rejected.
+Regrettably, neither PeerJ nor Royal Society make peer reviews available for manuscripts that were rejected.
 As a consequence, we have analyzed a biased sample of the literature.
-At the moment only very few scientific journals (e.g., Meta-Psychology, F1000) make peer reviews available for all submitted articles.
+Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
 Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
@@
 (2019) who had access to the reviews for accepted and rejected manuscripts.
-Thus, even though the proportion of reject recommendations in our dataset is small, the relative difference with which this recommendation is given in signed and unsigned reviews seems comparable to datasets that include rejected manuscripts.
 
@@
 Lakens drafted the final version, and both authors revised the final version of the manuscript.
+
+\hypertarget{competing-interests}{%
+\section{Competing interests}\label{competing-interests}}
+
 The authors report no conflicts of interest.
@@
 
+\leavevmode\hypertarget{ref-spellman_short_2015}{}%
+Spellman, B.
+A.
+(2015).
+A Short (Personal) Future History of Revolution 2.0.
+\emph{Perspectives on Psychological Science}, \emph{10}(6), 886--899.
+doi:\href{https://doi.org/10.1177/1745691615609918}{10.1177/1745691615609918}
+
 \leavevmode\hypertarget{ref-walsh_open_2000}{}%

### 2019-11-01 open_peer_review.Rmd
submit

@@
 author_note: |
- This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/9526a/
+ Submitted to Meta-Psychology.
+Click here to follow the fully transparent editorial process of this submission.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
+All data underlying this reproducible manuscript are available at https://osf.io/9526a/
 abstract: |
@@
 
-```{r, PeerJrec, fig.cap = "Proportion of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended 'minor revisions' or 'major revisions'."}
+```{r, PeerJrec, fig.cap = "Proportion of 'minor revisions' or 'major revisions' recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned."}
 
@@
                    c(PeerJ_anonymous_by_recommendation_proportion[2:3], PeerJ_notanonymous_by_recommendation_proportion[2:3]))
-colnames(plot_data) <- c("recommendation", "signed", "count")
+colnames(plot_data) <- c("recommendation", "signed", "proportion")
 
-ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) +
+ggplot(plot_data, aes(x = recommendation, y = proportion, fill = signed)) +
   geom_bar(position="dodge", stat="identity") +
@@
   coord_cartesian(ylim = c(0, 1)) +
-  geom_text(aes(label = sprintf('%.2f',count)), 
+  geom_text(aes(label = sprintf('%.2f',proportion)), 
               size = 6, 
@@
 
-```{r, TRSrec, fig.cap = "Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society recommended 'accept', 'minor revisions', 'major revisions', or 'reject'."}
+```{r, TRSrec, fig.cap = "Proportion of 'accept', 'minor revisions', 'major revisions', or 'reject' recommendations conditioned on whether reviews were signed or unsigned."}
 
@@
                    c(TRS_anonymous_by_recommendation_proportion, TRS_notanonymous_by_recommendation_proportion))
-colnames(plot_data) <- c("recommendation", "signed", "count")
+colnames(plot_data) <- c("recommendation", "signed", "proportion")
 
-ggplot(plot_data, aes(x = recommendation, y = count, fill = signed)) + 
+ggplot(plot_data, aes(x = recommendation, y = proportion, fill = signed)) + 
   geom_bar(position="dodge", stat="identity") +
@@
 It is also possible that people who sign their reviews generally give more positive recommendations, and therefore the distribution of signed reviews differs from non-signed reviews.
+These are just two of many possible explanations for the observed pattern.
 Based on the literature reviewed in the introduction we know researchers are hesitant to voice criticism when their identity will be known, and experimental evidence suggests that if identities are shared with authors, recommendations become somewhat more positive.
@@
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation [@bastian_signing_2018].
-Based on all available research is seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
+Based on all available research it seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
 Therefore, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their reviews, regardless of whether their recommendation is positive or negative.

### 2020-05-28 manuscript/revision_2/reply_to_reviews.Rmd
first draft revision

---
title: "Reply_to_reviews"
author: "Daniel Lakens"
date: "5/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## To do:

# Reviewer 1

1 & 2: A breakdown of their findings by discipline
3: Reviewers who gave more than 1 review. 
> We can show multiple signed reviews, but we do not know if people sign sometimes but not other times. We can see if there is a "always sign" comment? Otherwise, asked to discuss as a limitation, which it is. 
4: Changes of time. We did originally look at this, but there were none. However, this is an obvious question (since we explored it) and we should have included it. 
5: Do RSOS and PEERJ allow reviewers to recommend reviewers? 
6: Opening up the review process could also lead to showing how some researchers game the system by targeting colleagues likely to give positive reviews. Discuss this possibility.

7: Please ensure the manuscript is proofread for clerical/grammatical errors. The word
"individidual" is misspelt, "researchers decision" is missing an apostrophe
8: Please check the link to the following reference, it appears to be broken in the pdf I reviewed:
Bastian, H. (2018). Signing Critical Peer Reviews & the Fear of Retaliation: What Should We
Do? |Absolutely Maybe. https://blogs.plos.org/absolutely- maybe/2018/03/22/signing-criticalpeer-
reviews- the-fear-of-retaliation-what-should-we-do/.

## Reviewer 2

1: it would be helpful to add a one paragraph description of PeerJ and RSOS. It might
include their scope, reputation, or any other information that would allow the reader to
contextualize the sample. [I think we can combine this with point 5 above]

2: Add information to make the figures more distinct. Figure 2 can include the words “Royal
Society”. This will make clear using the figures alone that figures 1 and 2 represent entirely
separate samples.

3: *Under the subheading “Additional Analyses”, the authors offer some analysis regarding “how
often reviewers agree.” This is an interesting approach to a common-place but under-studied
phenomena in meta-science. That said, these analyses don’t contribute to the main theme of the
paper, are not referenced in any other part of the paper, are not situated in the reviewed literature,
and are not interpreted in any way. I suggest that this section be either removed or expanded and
incorporated into the larger theme. 
[I agree - it is more like a motivation for people to explore that data further. Maybe remove, maybe make clearer it is just to show the data is available]

4: Reputations could easily be damaged by this type of transparency if it became known one reviewed retracted papers. Combine with point 6 by reviewer 1.

5: The authors acknowledge that the causal relationship for the relationship they observe could run
two different ways. Given the (well-acknowledged) incomplete nature of the data, considering at
least one more counter-narrative would make for a more complete treatment of the issue.

Editor comments:

2: There are no quantitative analyses in the manuscript other than proportions. Why is this?
Maybe the authors think their findings are too exploratory to justify the presentation of p values, but some indication of the magnitude of the effects would surely be useful.

[There are no p-values, because the work is descriptive. We do not intend to make any claims - or do we? MAgnitude of effect can be seen in %, no?

3: I would be interested to see a short discussion of the possible consequences of the fact
that at PeerJ, readers do not get to see the individual reviewers’ recommendations.

4: “Our data support the idea that researchers [sic] decision to sign is related to their
recommendation across a wide range of scientific disciplines” (p. 4)—this language could
suggest that a robust effect has been shown for each of several disciplines. However, all that has actually been shown (I think) is that there is some effect (cf. my earlier remark about effect sizes) across a sample that encompasses a wide range of disciplines. It could be that the effect is
stronger for psychology and weaker or absent for biomedical sciences, for example. 
[Combine with point 1 and 2 of Reviewer 1]

5: “For positive recommendations, reviewers will get credit for their reviews, while for
negative reviews they do not run the risk of receiving any backlash from colleagues in their
field” (p. 4)—I’m not sure if “credit” is the right word. Reviewers who write a glowing report on
a manuscript can certainly expect to be liked by its author(s), but whether or not the rest of their
colleagues (and the field as a whole) will give them any sort of “credit” will depend on whether
the article later turns out to be flawed (and/or whether it upsets some powerful people); and the
same could apply in reverse for a negative review. So perhaps this comment should be rephrased
to emphasise that any “credit” is restricted to approval felt from the author(s) of the accepted
article. 
[True, combine with point 4 by reviewer 2]

6: I downloaded the code and data associated with the manuscript via the OSF link and was
able to reproduce the main numerical results and figures. However, the percentages in the first
paragraph on page 4 were printed with a lot more decimal places than in the PDF file (e.g., “For
41.7218543% of the manuscripts the maximum deviation was one category”). I wonder if your R
setup has a different global rounding option from mine? For best reproducibility, rounding
should probably be done explicitly in the code.

### 2020-05-28 manuscript/revision_1/open_peer_review.tex
first draft revision

--- 2019-10-29 open_peer_review.tex
@@
 
-\authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
+\authornote{Submitted to Meta-Psychology.
+Click here to follow the fully transparent editorial process of this submission.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
 All data underlying this reproducible manuscript are available at \url{https://osf.io/9526a/}
@@
 \includegraphics{open_peer_review_files/figure-latex/PeerJrec-1.pdf}
-\caption{\label{fig:PeerJrec}Proportion of signed and unsigned reviews as a function of whether the handling editor at PeerJ recommended \enquote{minor revisions} or \enquote{major revisions}.}
+\caption{\label{fig:PeerJrec}Proportion of \enquote{minor revisions} or \enquote{major revisions} recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned.}
 \end{figure}
@@
 \includegraphics{open_peer_review_files/figure-latex/TRSrec-1.pdf}
-\caption{\label{fig:TRSrec}Proportion of signed and unsigned reviews as a function of whether reviewers at Royal Society recommended \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.}
+\caption{\label{fig:TRSrec}Proportion of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject} recommendations conditioned on whether reviews were signed or unsigned.}
 \end{figure}
@@
 It is worthwhile to examine whether this fear of retaliation has an empirical basis, and if so, to consider developing guidelines to counteract such retaliation (Bastian, 2018).
-Based on all available research is seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
+Based on all available research it seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
 Therefore, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their reviews, regardless of whether their recommendation is positive or negative.

### 2020-05-28 manuscript/revision_2/open_peer_review.Rmd
first draft revision

--- 2019-11-01 open_peer_review.Rmd
@@
     affiliation   : "1"
-  - name          : "Daniël Lakens"
+  - name          : "Daniel Lakens"
     affiliation   : "1"
@@
 library(dplyr)
+library(tidyr)
 library(stringr)
@@
 # Read open science and open biology rds datafiles
-TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
-TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
+TRS_data_os <- readRDS(file = "../../royal_society_data_os.rds")
+TRS_data_ob <- readRDS(file = "../../royal_society_data_ob.rds")
 # Combine both datasets into one.
@@
 #Read in PeerJ data
-PeerJ_main_data <- readRDS(file = "peerj_data.rds")
-PeerJ_cs_data <- readRDS(file = "peerj_cs_data.rds")
+PeerJ_main_data <- readRDS(file = "../../peerj_data.rds")
+PeerJ_cs_data <- readRDS(file = "../../peerj_cs_data.rds")
 # Combine both datasets into one.
@@
 # We can see how many reviews are open in TRS by counting all doi in scopus, and seeing how many end up in our list of open reviews:
-OS_pdf_list <- readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r"))
+OS_pdf_list <- readLines(file("../../royal_society_pdf_files/OS_pdf_list.txt", open = "r"))
 
-open_review_TRS <- length(OS_pdf_list) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
+open_review_TRS <- length(OS_pdf_list) / length(read.csv("../../scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
 
 # How many entries in RSOS in total? Read in scopus datafile
-TRS_scopus_OS <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
+TRS_scopus_OS <- read.csv("../../scopus_export_rsos.csv", stringsAsFactors = FALSE)
 table(TRS_scopus_OS$Document.Type)
@@
 # How many entries in RSOS in total? Read in scopus datafile
-TRS_scopus_OB <- read.csv("scopus_export_rsob.csv", stringsAsFactors = FALSE)
+TRS_scopus_OB <- read.csv("../../scopus_export_rsob.csv", stringsAsFactors = FALSE)
 table(TRS_scopus_OB$Document.Type)
 errata_editorial <- errata_editorial + sum(table(TRS_scopus_OB$Document.Type)[c(2,3,5)])
-# Excude Errata and Editorial (that have no reviews)
+# Exclude Errata and Editorial (that have no reviews)
 TRS_scopus_OB <- TRS_scopus_OB[!TRS_scopus_OB$Document.Type == "Erratum" & !TRS_scopus_OB$Document.Type == "Editorial" & !TRS_scopus_OB$Document.Type == "Retracted",]
@@
 PeerJ_data_R1 <- group_by(PeerJ_data, df_link)
+# Make recommendation a factor
+PeerJ_data_R1$df_recommendation <-  recode_factor(PeerJ_data_R1$df_recommendation, `1` = "accept", `2` = "minor revision", `3` = "major revision")
+# Slightly shorten 1 label PeerJ section for plot
+PeerJ_data_R1$df_section <- recode(PeerJ_data_R1$df_section, "biochemistry, biophysics and molecular biology"="biochemistry biophysics molecular biology", "NA" = "no section assigned")
 PeerJ_data_R1 <- top_n(PeerJ_data_R1, 1, df_version)
@@
 
+PeerJ_data_R1$df_section[1]
 # Do the same for TRS
 TRS_data_R1 <- group_by(TRS_data, df_link)
+# Make recommendation a factor
+TRS_data_R1$df_recommendation <-  recode_factor(TRS_data_R1$df_recommendation, `1` = "accept", `2` = "minor revision", `3` = "major revision", `4` = "reject")
 TRS_data_R1 <- top_n(TRS_data_R1, 1, df_version)
@@
 This includes opening up the peer review process.
-An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve peer review [@bruce_impact_2016].
+An increasing number of journals have started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve peer review [@bruce_impact_2016].
 Open peer review can be implemented by making peer reviews available, but also by revealing the identity of reviewers during or after the peer review process.
@@
 This suggests that a causal effect exists between knowing your identity will be revealed, and the recommendation that is made during the peer review process.
-A meta-analysis by Bruce and colleagues (2016) supports the conclusion that across four studies reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
+Based on a small-scale meta-analysis of four studies Bruce and colleagues (2016) found support for the conclusion that reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
 
-Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
+Although the self-report studies and the experiments clearly suggest that reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
 The trade-off between the benefit of getting credit when performing peer reviews and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the more positive their recommendation is.
 If this strategic behavior occurs in practice, we should see a different pattern of recommendations for signed and unsigned reviews.
-One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, the Journal of Hydrology: Regional Studies, and the International Journal of Surgery [@bravo_effect_2019].
+One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal *Agricultural and Forest Meteorology*, *Annals of Medicine and Surgery*, *Engineering Fracture Mechanics*, the *Journal of Hydrology: Regional Studies*, and the *International Journal of Surgery* [@bravo_effect_2019].
 Although only 8.1% of reviewers voluntarily disclosed their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not sign.
@@
 
-We examined the relationship between recommendations peer reviewers make and the probability that they signed their review in two large open access journals, PeerJ (including reviews for PeerJ Computer Science) and Royal Society Open Science (including Royal Society Open Biology).
+We examined the relationship between the recommendations peer reviewers made and the proportion of signed reviews in two large open access journals, PeerJ (including reviews for PeerJ Computer Science) and Royal Society Open Science (including Royal Society Open Biology).
 We ignored more recently launched PeerJ journals in the field of Chemistry due to the small number of articles published to date in these journals.
-PeerJ and Royal Society publish articles across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
+PeerJ and Royal Society Open journals publish articles across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
 PeerJ launched in 2012 and PeerJ Computer Science launched in 2015.
@@
 Peer reviewers have the option to make their identity known when submitting their review to RSOS or RSOB.
-Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, the reviews for PeerJ and Royal Society provide insights into the peer review behavior of scientists across a wide range of disciplines.
+Because of their broad scope, the large number of publications in each journal, and their early focus on open reviews, the reviews for PeerJ and Royal Society Open journals provide insights into the peer review behavior of scientists across a wide range of disciplines.
 
@@
 PeerJ assigns all articles a number, increasing consecutively with each published manuscript.
-Reviews are always accessible in html (i.e., reviews for the first article published in PeerJ are available at https://peerj.com/articles/1/reviews).
-For Royal Society reviews are published online as a PDF file.
+Reviews are always accessible in HTML (e.g., reviews for the first article published in PeerJ are available at https://peerj.com/articles/1/reviews).
+For Royal Society Open journals reviews are published online as a PDF file.
 A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
@@
 Note that for PeerJ the editor makes the recommendation for each submission based on the reviews.
-We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
-For Royal Society reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
-Because PeerJ and Royal Society only share reviews for published articles there are few 'reject' recommendations for Royal Scoiety and no 'reject' recommendations by editors among PeerJ reviews.
+We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
+For Royal Society Open journals reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
+Because PeerJ and Royal Society Open journals only share reviews for published articles there are few 'reject' recommendations for Royal Society Open journals and no 'reject' recommendations by editors among PeerJ reviews.
 Searching all reviews for PeerJ for the words 'appealed on' revealed 47 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published.
@@
 
-We examined `r 7930+225` articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles from Royal Society (`r length(TRS_scopus_OS$DOI)` from RSOS, `r length(TRS_scopus_OB$DOI)` from RSOB, `r errata_editorial` of which were editorials or errata without reviews) published up to October 2019.
+We examined `r 7930+225` articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as `r length(TRS_scopus_OS$DOI)+length(TRS_scopus_OB$DOI)` articles from Royal Society Open journals (`r length(TRS_scopus_OS$DOI)` from RSOS, `r length(TRS_scopus_OB$DOI)` from RSOB, `r errata_editorial` of which were editorials or errata without reviews) published up to October 2019.
 We retrieved all reviews when these were made available (the reviews were available for `r nrow(PeerJ_unique)` articles in PeerJ, and `r nrow(TRS_unique)` articles in Royal Society).
-Articles can go through multiple rounds of review.
-We focus on the first review round in our analyses as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following @bravo_effect_2019.
+Articles can, of course, go through multiple rounds of review.
+However, we focus only on the first review round in our analyses as this review reflects the initial evaluation of reviewers, before the handling editor has made any decision, following @bravo_effect_2019.
 On average initial submissions at PeerJ received `r round(mean(count(PeerJ_data_R1, df_link)$n), 2)` reviews.
-Articles in the Royal Society journals received on average `r round(mean(count(TRS_data_R1, df_link)$n), 2)` reviews for the original submission.
+Articles in the Royal Society Open journals received on average `r round(mean(count(TRS_data_R1, df_link)$n), 2)` reviews for the original submission.
 
@@
 PeerJ_notanonymous_by_recommendation <- by(PeerJ_data_R1$df_anonymous == 0, PeerJ_data_R1$df_recommendation, sum)
+
+# Reviewers ask for overview per subfield
+PeerJ_notanonymous_by_recommendation_by_field <- by(PeerJ_data_R1$df_anonymous == 0, list(recommendation = PeerJ_data_R1$df_recommendation, section = PeerJ_data_R1$df_section), sum)
+
+PeerJ_data_R1 %>% 
+  group_by(df_recommendation) %>% 
+  summarise(unsigned = sum(df_anonymous == 0), signed = sum(df_anonymous == 1))
+
+# Reproducing proportions using dplyr
+PeerJ_data_R1 %>% 
+  group_by(df_recommendation) %>% 
+  summarise(signed = sum(df_anonymous == 0)/sum(PeerJ_notanonymous_by_recommendation), unsigned = sum(df_anonymous == 1)/sum(PeerJ_anonymous_by_recommendation))
+
+# Reproducing proportions using dplyr per field
+PeerJ_data_R1 %>% 
+  group_by(df_recommendation, df_section) %>% 
+  summarise(signed = sum(df_anonymous == 0)/sum(PeerJ_notanonymous_by_recommendation), unsigned = sum(df_anonymous == 1)/sum(PeerJ_anonymous_by_recommendation))
 
@@
 In total `r sum(PeerJ_data_R1$df_anonymous == 0)` reviewers signed their review for the initial submission, and `r sum(PeerJ_data_R1$df_anonymous == 1)` reviewers did not.
-In Royal Society journals we analyzed `r nrow(TRS_unique)` articles for which we retrieved `r length(TRS_data_R1$df_anonymous)` unique reviews for the first submission, where `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their review, and `r sum(TRS_data_R1$df_anonymous == 1)` did not.
-The percentages of people who sign (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for Royal Society) are slightly lower than the 43.23% reported by @wang_open_2016 who analyzed the first 1214 articles published in PeerJ.
+In Royal Society Open journals we analyzed `r nrow(TRS_unique)` articles for which we retrieved `r length(TRS_data_R1$df_anonymous)` unique reviews for the first submission, where `r sum(TRS_data_R1$df_anonymous == 0)` reviewers signed their review and `r sum(TRS_data_R1$df_anonymous == 1)` did not.
+The percentages of people who signed (`r 100*sum(PeerJ_data_R1$df_anonymous == 0)/(sum(PeerJ_data_R1$df_anonymous == 0)+sum(PeerJ_data_R1$df_anonymous == 1))`% for PeerJ, `r 100*sum(TRS_data_R1$df_anonymous == 0)/(sum(TRS_data_R1$df_anonymous == 0)+sum(TRS_data_R1$df_anonymous == 1))`% for Royal Society Open journals) are slightly lower than the 43.23% reported by @wang_open_2016 who analyzed the first 1214 articles published in PeerJ.
 
-To answer our main research question we plotted the signed an unsigned reviews for PeerJ as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
+To answer our main research question we plotted the signed and unsigned reviews for PeerJ as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
 Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer.
-For minor revisions, a greater proportion or reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
+For minor revisions, a greater proportion of reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
 Too few articles are immediately accepted after the first round of reviews in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to impact the proportions in the other two categories.
@@
               vjust = -.5)
+
 ```
@@
 We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}).
-The overal pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).
+The overall pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).
 
-```{r, TRSrec, fig.cap = "Proportion of 'accept', 'minor revisions', 'major revisions', or 'reject' recommendations conditioned on whether reviews were signed or unsigned."}
+```{r, TRSrec, fig.cap = "Proportion of 'accept', 'minor revisions', 'major revisions', or 'reject' recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned."}
 
@@
 
-We can not draw causal conclusions based on this correlational data.
+We cannot draw causal conclusions based on this correlational data.
 It is possible that reviewers are less likely to sign more negative reviews.
@@
 
+```{r, echo=FALSE, results='asis'}
+cat("\\onecolumn")
+```
+
+```{r, warning=FALSE, PeerJrecperfield, fig.width=15, fig.height=10, fig.cap = "Proportion of 'minor revisions' or 'major revisions' recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned."}
+
+# As asked by reviewers, how does this differ over subfields?
+
+# Reproducing proportions using dplyr per field
+plot_data_by_field <- PeerJ_data_R1 %>% 
+  group_by(df_recommendation, df_section) %>% 
+  summarise(signed = sum(df_anonymous == 0)/sum(PeerJ_notanonymous_by_recommendation), unsigned = sum(df_anonymous == 1)/sum(PeerJ_anonymous_by_recommendation))
+
+# Reproducing counts using dplyr per field
+plot_data_by_field <- PeerJ_data_R1 %>%
+  group_by(df_recommendation, df_section) %>%
+  summarise(signed = sum(df_anonymous == 0), unsigned = sum(df_anonymous == 1))
+
+# Filter NA and direct accepts
+plot_data_by_field <- plot_data_by_field %>% filter(as.integer(df_recommendation) > 1)
+
+plot_data_by_field_long <- gather(plot_data_by_field, signed, proportion, signed:unsigned, factor_key = TRUE)
+
+ggplot(plot_data_by_field_long, aes(x = df_recommendation, y = proportion, fill = signed)) +
+  geom_bar(position="dodge", stat="identity") +
+  theme_linedraw(base_size = 20) +  
+  theme(legend.position = "bottom",
+        legend.title=element_blank(),
+        panel.grid.major.x = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        axis.title.x=element_blank()) + 
+  scale_fill_manual(values = c("#000000", "#808080")) + 
+  coord_cartesian(ylim = c(0, 900)) +
+  geom_text(aes(label = proportion), # to add rounding: sprintf('%.2f',proportion)
+              size = 6, 
+              color = "black",
+              position = position_dodge(width = 0.9),
+              vjust = -.5) + 
+  ggtitle("PeerJ recommendations") +
+  facet_wrap(~df_section, ncol = 3)
+
+```
+
+```{r, TRSrecpergroup, fig.width=15, fig.height=4, fig.cap = "Proportion of 'accept', 'minor revisions', 'major revisions', or 'reject' recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned."}
+
+# Makes more sense to plot proportions
+TRS_anonymous_by_recommendation_proportion <- TRS_anonymous_by_recommendation/sum(TRS_anonymous_by_recommendation)
+TRS_notanonymous_by_recommendation_proportion <- TRS_notanonymous_by_recommendation/sum(TRS_notanonymous_by_recommendation)
+
+# As asked by reviewers, how does this differ over subfields?
+
+# Reproducing proportions using dplyr per field
+plot_data_by_field <- TRS_data_R1 %>% 
+  group_by(df_recommendation, df_section) %>% 
+  summarise(signed = sum(df_anonymous == 0)/sum(TRS_notanonymous_by_recommendation), unsigned = sum(df_anonymous == 1)/sum(TRS_anonymous_by_recommendation))
+
+# Reproducing counts using dplyr per field
+plot_data_by_field <- TRS_data_R1 %>%
+  group_by(df_recommendation, df_section) %>%
+  summarise(signed = sum(df_anonymous == 0), unsigned = sum(df_anonymous == 1))
+
+plot_data_by_field_long <- gather(plot_data_by_field, signed, proportion, signed:unsigned, factor_key = TRUE)
+
+ggplot(plot_data_by_field_long, aes(x = df_recommendation, y = proportion, fill = signed)) +
+  geom_bar(position="dodge", stat="identity") +
+  theme_linedraw(base_size = 20) +  
+  theme(legend.position = "bottom",
+        legend.title=element_blank(),
+        panel.grid.major.x = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        axis.title.x=element_blank()) + 
+  scale_fill_manual(values = c("#000000", "#808080")) + 
+  coord_cartesian(ylim = c(0, 1200)) +
+  geom_text(aes(label = proportion), # to add rounding: sprintf('%.2f',proportion)
+              size = 6, 
+              color = "black",
+              position = position_dodge(width = 0.9),
+              vjust = -.5) + 
+  ggtitle("Royal Society Open recommendations") +
+  facet_wrap(~df_section, ncol = 4)
+
+```
+
+```{r, echo=FALSE, results='asis'}
+cat("\\twocolumn")
+```
+
 # Additional Analyses
 
-The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for Royal Society).
-Through the DOI, researchers can link this data to other sources of information such as citation counts.
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for Royal Society Open journals).
+Using the DOI, researchers can link this data to other sources of information such as citation counts.
 Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
-Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
+Since we know the individual recommendation of each reviewer for Royal Society Open journals, one example of the insights that open reviews provide is how often reviewers agree.
 For the `r sum(table(rev_dif))` papers where the reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
@@
 
-Regrettably, neither PeerJ nor Royal Society make peer reviews available for manuscripts that were rejected.
+Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected.
 As a consequence, we have analyzed a biased sample of the literature.
@@
 Our analysis shows that when authors are given the choice to sign their reviews, signed reviews have more positive recommendations than unsigned reviews.
-This pattern is clearly present for reviews in Royal Society Open Science and Open Biology, a large multi-disciplinary journal that published across a wide range of scientific domains.
+This pattern is clearly present for reviews in Royal Society Open Science and Open Biology, a large multi-disciplinary journal that publishes articles across a wide range of scientific domains.
 The pattern is also visible in a second large multi-disciplinary journal, PeerJ, under the assumption that recommendations by editors at PeerJ are correlated with the recommendations by reviewers.
@@
 Open reviews allow researchers to examine meta-scientific questions that give insights into the peer review process.
-Our data support the idea that researchers decision to sign is related to their recommendation across a wide range of scientific disciplines.
-Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some researchers are more likely to sign if their recommendation is more positive.
+Our data supports the idea that reviewers' decisions to sign are related to their recommendation across a wide range of scientific disciplines.
+Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some reviewers are more likely to sign if their recommendation is more positive.
 This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs.
@@
 Based on all available research it seems plausible that at least some reviewers hesitate to sign if they believe doing so could have negative consequences, but will sign reviews with more positive recommendations to get credit for their work.
-Therefore, it seems worthwhile to explore ways in which reviewers feel comfortable to claim credit for all their reviews, regardless of whether their recommendation is positive or negative.
+Therefore, it seems worthwhile to explore ways in which reviewers could be enabled to feel comfortable to claim credit for all their reviews, regardless of whether their recommendation is positive or negative.
 
@@
 N.
-van Sambeek drafted the initial version of the manuscript as a Bachelor thesis, D.
+van Sambeek drafted the initial version of the manuscript as a Bachelor's thesis, D.
 Lakens drafted the final version, and both authors revised the final version of the manuscript.

### 2020-05-28 manuscript/revision_2/open_peer_review.tex
first draft revision

--- 2020-05-28 manuscript/revision_1/open_peer_review.tex
@@
-\documentclass[,jou, a4paper,floatsintext]{apa6}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  english,
+  ,jou, a4paper,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
   pdftitle={Reviewers' Decision to Sign Reviews is Related to Their Recommendation},
-            pdfauthor={Nino van Sambeek~\& Daniël Lakens},
+  pdflang={en-EN},
   pdfkeywords={Peer Review, Open Reviews, Transparency, Open Science},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
 \ifx\paragraph\undefined\else
@@
 \fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-  \title{Reviewers' Decision to Sign Reviews is Related to Their Recommendation}
-    \author{Nino van Sambeek\textsuperscript{1}~\& Daniël Lakens\textsuperscript{1}}
-    \date{}
-
-\shorttitle{Signing Open Reviews}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Eindhoven University of Technology, The Netherlands}
-\keywords{Peer Review, Open Reviews, Transparency, Open Science\newline\indent Word count: 2711}
-\usepackage{csquotes}
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
+\shorttitle{Signing Open Reviews}
+\author{Nino van Sambeek\textsuperscript{1}\ \& Daniel Lakens\textsuperscript{1}}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Eindhoven University of Technology, The Netherlands}
 \authornote{Submitted to Meta-Psychology.
@@
 This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All data underlying this reproducible manuscript are available at \url{https://osf.io/9526a/}
+All data underlying this reproducible manuscript are available at https://osf.io/9526a/
 
-Correspondence concerning this article should be addressed to Daniël Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
+Correspondence concerning this article should be addressed to Daniel Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: D.Lakens@tue.nl}
+\keywords{Peer Review, Open Reviews, Transparency, Open Science\newline\indent Word count: 2711}
+\usepackage{dblfloatfix}
+
+\usepackage{csquotes}
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[shorthands=off,main=english]{babel}
+\fi
+
+\title{Reviewers' Decision to Sign Reviews is Related to Their Recommendation}
+
+\date{}
 
@@
 We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
-
 }
@@
 This includes opening up the peer review process.
-An increasing number of journals has started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve peer review (Bruce, Chauvin, Trinquart, Ravaud, \& Boutron, 2016).
+An increasing number of journals have started to make peer review reports available alongside published articles as part of ongoing experiments that aim to improve peer review (Bruce, Chauvin, Trinquart, Ravaud, \& Boutron, 2016).
 Open peer review can be implemented by making peer reviews available, but also by revealing the identity of reviewers during or after the peer review process.
@@
 This suggests that a causal effect exists between knowing your identity will be revealed, and the recommendation that is made during the peer review process.
-A meta-analysis by Bruce and colleagues (2016) supports the conclusion that across four studies reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
+Based on a small-scale meta-analysis of four studies Bruce and colleagues (2016) found support for the conclusion that reviewers are somewhat less likely to recommend rejection when they have to sign their reviews.
 
-Although the self-report studies and the experiments clearly suggest reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
+Although the self-report studies and the experiments clearly suggest that reviewers worry about having their name attached to more critical reviews they write, so far little is known about what reviewers actually do when given the opportunity to sign their reviews.
 The trade-off between the benefit of getting credit when performing peer reviews and the risk of negative consequences when signing critical reviews might lead to strategic behavior where authors become more likely to sign reviews the more positive their recommendation is.
 If this strategic behavior occurs in practice, we should see a different pattern of recommendations for signed and unsigned reviews.
-One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal Agricultural and Forest Meteorology, Annals of Medicine and Surgery, Engineering Fracture Mechanics, the Journal of Hydrology: Regional Studies, and the International Journal of Surgery (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
+One recent study revealed such a pattern when analyzing data from an Elsevier trial on publishing peer review reports in the journal \emph{Agricultural and Forest Meteorology}, \emph{Annals of Medicine and Surgery}, \emph{Engineering Fracture Mechanics}, the \emph{Journal of Hydrology: Regional Studies}, and the \emph{International Journal of Surgery} (Bravo, Grimaldo, López-Iñesta, Mehmani, \& Squazzoni, 2019).
 Although only 8.1\% of reviewers voluntarily disclosed their identity in these reviews, the data revealed a clear difference between the recommendations by reviewers who chose to sign their reviews, compared to reviewers who did not sign.
@@
 PeerJ assigns all articles a number, increasing consecutively with each published manuscript.
-Reviews are always accessible in html (i.e., reviews for the first article published in PeerJ are available at \url{https://peerj.com/articles/1/reviews}).
-For Royal Society reviews are published online as a PDF file.
+Reviews are always accessible in HTML (e.g., reviews for the first article published in PeerJ are available at \url{https://peerj.com/articles/1/reviews}).
+For Royal Society Open journals reviews are published online as a PDF file.
 A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
@@
 Note that for PeerJ the editor makes the recommendation for each submission based on the reviews.
-We therefore do not directly know which recommendation each reviewer provided, but analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
-For Royal Society reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
-Because PeerJ and Royal Society only share reviews for published articles there are few \enquote{reject} recommendations for Royal Scoiety and no \enquote{reject} recommendations by editors among PeerJ reviews.
+We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
+For Royal Society Open journals reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
+Because PeerJ and Royal Society Open journals only share reviews for published articles there are few \enquote{reject} recommendations for Royal Society Open journals and no \enquote{reject} recommendations by editors among PeerJ reviews.
 Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 47 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published.
@@
 
-We examined 8155 articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as 3576 articles from Royal Society (2887 from RSOS, 689 from RSOB, 81 of which were editorials or errata without reviews) published up to October 2019.
+We examined 8155 articles published in PeerJ (7930 in PeerJ, 225 in PeerJ Computer Science), as well as 3576 articles from Royal Society Open journals (2887 from RSOS, 689 from RSOB, 81 of which were editorials or errata without reviews) published up to October 2019.
 We retrieved all reviews when these were made available (the reviews were available for 5087 articles in PeerJ, and 1964 articles in Royal Society).
-Articles can go through multiple rounds of review.
-We focus on the first review round in our analyses as this review reflects the initial evaluation of reviewers, before the handling editor has made a decision, following Bravo et al.
+Articles can, of course, go through multiple rounds of review.
+However, we focus only on the first review round in our analyses as this review reflects the initial evaluation of reviewers, before the handling editor has made any decision, following Bravo et al.
 (2019).
 On average initial submissions at PeerJ received 2.36 reviews.
-Articles in the Royal Society journals received on average 2.13 reviews for the original submission.
+Articles in the Royal Society Open journals received on average 2.13 reviews for the original submission.
 
@@
 In total 4592 reviewers signed their review for the initial submission, and 7418 reviewers did not.
-In Royal Society journals we analyzed 1964 articles for which we retrieved 4188 unique reviews for the first submission, where 1549 reviewers signed their review, and 2639 did not.
-The percentages of people who sign (38.23\% for PeerJ, 36.99\% for Royal Society) are slightly lower than the 43.23\% reported by Wang, You, Manasa, and Wolfram (2016) who analyzed the first 1214 articles published in PeerJ.
+In Royal Society Open journals we analyzed 1964 articles for which we retrieved 4188 unique reviews for the first submission, where 1549 reviewers signed their review and 2639 did not.
+The percentages of people who signed (38.23\% for PeerJ, 36.99\% for Royal Society Open journals) are slightly lower than the 43.23\% reported by Wang, You, Manasa, and Wolfram (2016) who analyzed the first 1214 articles published in PeerJ.
 
-To answer our main research question we plotted the signed an unsigned reviews for PeerJ as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
+To answer our main research question we plotted the signed and unsigned reviews for PeerJ as a function of the recommendation in the first review round (see Figure \ref{fig:PeerJrec}).
 Remember that for PeerJ these recommendations are made by the editor, and thus only indirectly capture the evaluation of the reviewer.
-For minor revisions, a greater proportion or reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
-Too few articles are immediately accepted after the first round of reviews in PeerJ (22 in total) to impact the proportions in the other two categories.
+For minor revisions, a greater proportion of reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
+Too few articles are immediately accepted after the first round of reviews in PeerJ (0 in total) to impact the proportions in the other two categories.
 
@@
 We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}).
-The overal pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).
+The overall pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).
 
@@
 \includegraphics{open_peer_review_files/figure-latex/TRSrec-1.pdf}
-\caption{\label{fig:TRSrec}Proportion of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject} recommendations conditioned on whether reviews were signed or unsigned.}
+\caption{\label{fig:TRSrec}Proportion of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject} recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned.}
 \end{figure}
 
-We can not draw causal conclusions based on this correlational data.
+We cannot draw causal conclusions based on this correlational data.
 It is possible that reviewers are less likely to sign more negative reviews.
@@
 
+\onecolumn
+
+\begin{figure}
+\centering
+\includegraphics{open_peer_review_files/figure-latex/PeerJrecperfield-1.pdf}
+\caption{\label{fig:PeerJrecperfield}Proportion of \enquote{minor revisions} or \enquote{major revisions} recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{open_peer_review_files/figure-latex/TRSrecpergroup-1.pdf}
+\caption{\label{fig:TRSrecpergroup}Proportion of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject} recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned.}
+\end{figure}
+
+\twocolumn
+
 \hypertarget{additional-analyses}{%
@@
 
-The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for Royal Society).
-Through the DOI, researchers can link this data to other sources of information such as citation counts.
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for Royal Society Open journals).
+Using the DOI, researchers can link this data to other sources of information such as citation counts.
 Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
-Since we know the individidual recommendation of each reviewer for Royal Society journals, one example of the insights open reviews provide is how often reviewers agree.
-For the 1963 papers where the reviews were published, all reviewers agreed on the recommendation for 830 articles (42.28\% of the time).
-For 41.72\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.37\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.63\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
+Since we know the individual recommendation of each reviewer for Royal Society Open journals, one example of the insights that open reviews provide is how often reviewers agree.
+For the 0 papers where the reviews were published, all reviewers agreed on the recommendation for NA articles (NA\% of the time).
+For NA\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for NA\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for NA\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
 There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
 
-Regrettably, neither PeerJ nor Royal Society make peer reviews available for manuscripts that were rejected.
+Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected.
 As a consequence, we have analyzed a biased sample of the literature.
@@
 \emph{Nature Communications}, \emph{10}(1), 1--8.
-doi:\href{https://doi.org/10.1038/s41467-018-08250-2}{10.1038/s41467-018-08250-2}
+\url{https://doi.org/10.1038/s41467-018-08250-2}
 
@@
 \emph{BMC Medicine}, \emph{14}.
-doi:\href{https://doi.org/10.1186/s12916-016-0631-5}{10.1186/s12916-016-0631-5}
+\url{https://doi.org/10.1186/s12916-016-0631-5}
 
 \leavevmode\hypertarget{ref-godlee_making_2002}{}%
-Godlee, F.
-(2002).
-Making Reviewers Visible: Openness, Accountability, and Credit.
-\emph{JAMA}, \emph{287}(21), 2762--2765.
-doi:\href{https://doi.org/10.1001/jama.287.21.2762}{10.1001/jama.287.21.2762}
+Godlee, F. (2002). Making Reviewers Visible: Openness, Accountability, and Credit. \emph{JAMA}, \emph{287}(21), 2762--2765. \url{https://doi.org/10.1001/jama.287.21.2762}
 
@@
 \emph{Journal of the American Society for Information Science and Technology}, \emph{64}(1), 132--161.
-doi:\href{https://doi.org/10.1002/asi.22798}{10.1002/asi.22798}
+\url{https://doi.org/10.1002/asi.22798}
 
@@
 \emph{PLOS ONE}, \emph{12}(12), e0189311.
-doi:\href{https://doi.org/10.1371/journal.pone.0189311}{10.1371/journal.pone.0189311}
+\url{https://doi.org/10.1371/journal.pone.0189311}
 
 \leavevmode\hypertarget{ref-spellman_short_2015}{}%
-Spellman, B.
-A.
-(2015).
-A Short (Personal) Future History of Revolution 2.0.
-\emph{Perspectives on Psychological Science}, \emph{10}(6), 886--899.
-doi:\href{https://doi.org/10.1177/1745691615609918}{10.1177/1745691615609918}
+Spellman, B. A. (2015). A Short (Personal) Future History of Revolution 2.0. \emph{Perspectives on Psychological Science}, \emph{10}(6), 886--899. \url{https://doi.org/10.1177/1745691615609918}
 
@@
 \emph{The British Journal of Psychiatry}, \emph{176}(1), 47--51.
-doi:\href{https://doi.org/10.1192/bjp.176.1.47}{10.1192/bjp.176.1.47}
+\url{https://doi.org/10.1192/bjp.176.1.47}
 

### 2020-05-30 manuscript/revision_2/reply_to_reviews.Rmd
revision 2

@@
 ---
-title: "Reply_to_reviews"
+title: "Reply to reviews"
 author: "Daniel Lakens"
 date: "5/24/2020"
-output: html_document
+output: pdf_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-## To do:
-
 # Reviewer 1
 
-1 & 2: A breakdown of their findings by discipline
-3: Reviewers who gave more than 1 review. 
-> We can show multiple signed reviews, but we do not know if people sign sometimes but not other times.
-We can see if there is a "always sign" comment?
-Otherwise, asked to discuss as a limitation, which it is.
-4: Changes of time. We did originally look at this, but there were none. However, this is an obvious question (since we explored it) and we should have included it. 
-5: Do RSOS and PEERJ allow reviewers to recommend reviewers? 
-6: Opening up the review process could also lead to showing how some researchers game the system by targeting colleagues likely to give positive reviews. Discuss this possibility.
+Comment #1 and #2
+I consider the following statement to be too strong: Our data support the idea that researchers decision to sign is related to their recommendations across a wide range of scientific disciplines.
+To justify this, I would like to see a breakdown of their findings by discipline.
+Have certain disciplines taken to sign peer review more so than others?
+Providing data on this would be informative for future researchers designing studies investigating the
+barriers/weaknesses to open peer-review. Addressing comment #1 would address this comment
+too.
 
-7: Please ensure the manuscript is proofread for clerical/grammatical errors. The word
-"individidual" is misspelt, "researchers decision" is missing an apostrophe
-8: Please check the link to the following reference, it appears to be broken in the pdf I reviewed:
-Bastian, H. (2018). Signing Critical Peer Reviews & the Fear of Retaliation: What Should We
-Do? |Absolutely Maybe. https://blogs.plos.org/absolutely- maybe/2018/03/22/signing-criticalpeer-
-reviews- the-fear-of-retaliation-what-should-we-do/.
+**Reviewer 1 notes how our statement that we found a pattern across 'across a wide range of scientific disciplines' was too strong.
+Although we simply meant to imply we found it when averaging over fields, we see the benefit of an analysis per subject area.**
 
-## Reviewer 2
+**We have added a plot the provides an overview of the data for different sections for PeerJ.
+Royal Society Open Science has different subjects that each have and editorial boar (https://royalsocietypublishing.org/rsos/editorial-board) and distinguishes "collections" as can be seen at https://royalsocietypublishing.org/rsos/collection.
+However, neither of these classifications are part of the meta-data in scopus, not are they in the reviews.
+Therefore, for Royal Society Open journals we can only split the analysis for Royal Society Open Science and Royal Society Open Biology, the latter of which has very few datapoints.
+The pattern is the same, but with 300 reviews, mostly unsigned, this analysis is not informative enough to be included in the manuscript (the code to generate the plot for Open Science and Open Biology is in the manuscript code, but commented out).
+The new figure that plots the data across sections in PeerJ also addresses the second comment by Reviewer 1, concerning whether some fields sign more than others.
+We note how in paleontology, signing is most frequent.
+The revised manuscript now reads, just above where we present the new figure plotting the result for each section:**
 
-1: it would be helpful to add a one paragraph description of PeerJ and RSOS. It might
+*In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned.
+Beyond this main effect, we see a clear interaction across all sections, where the probability that a ratio of signed versus unsigned reviews is greater for major revisions than for minor revisions.
+Across all fields covered by PeerJ, it is less likely to see a signed review for major revisions than for minor revisions, providing further support for the generalizability of the observed effect.*
+
+Comment #3
+
+Did the authors explore reviewers that have given more than one review for PeerJ or Royal Society Open Science?
+One would assume that these reviewers would always sign their reviewers, but what if this is not the case.
+If so, why did they review papers some of the time but not others?
+Was it because the one they signed was more positive?
+This is worth a mention.
+
+**We have access to reviewer names only when they signed.
+Therefore, we do not know how often the same person signed their review, and how often they did not.
+For example, in our dataset, we see that Daniel Lakens signed reviews 3 times for PeerJ, and once for Royal Society Open Science.
+But our data does not allow us to draw conclusions about how often Daniel Lakens did not sign, and if he selectively signed from some papers but not for others.
+We see most reviewers appear once, 275 appear twice, and a smaller set have 3 or more reviews.
+But again, there is no way to know if they always sign, or not.
+We have noted this in the discussion.**
+
+review_names_peer_j
+
+1 time: 3815
+
+2 times: 275
+
+3 times: 54
+
+4 times: 9
+
+5 times: 2
+
+6 times: 2
+
+7 times: 1
+
+review_names_royal_society
+
+1 time: 1410
+
+2 times: 54
+
+3 times: 5
+
+4 times: 4
+
+**We see most reviewers appear once in the first round of review of a manuscript, some appear twice, and a smaller set have 3 or more reviews.
+But again, there is no way to know if they always sign, or not.
+We have noted this in the discussion.**
+
+*It might be that some reviewers consistently sign their reviews, while others sign selectively.
+Some researchers have contributed multiple signed reviews to our dataset, but it is unknown whether they also contributed unsigned reviews.
+The confidentiality of peer review makes it impossible to retrieve whether reviewers selectively sign from open reviews, and this question will need to be studied by surveying researchers directly.*
+
+Comment #4
+The identified articles were published over several years.
+Surely the incidence of signed reviews has changed over time?
+People might have been hesitant/unaware at the time of their introduction, but persuaded by how normative/acceptable open criticism -- or its discussion-- has become.
+
+**Spoiler: People have not been pursueded.
+To address point 4 of reviewer 1, about changes over time, we updated our textmining script for PeerJ to also retrieve the date the paper was accepted for publication, as well as the manuscript script where we retrieved publication year from the scopus file for Royal Society Open journals.
+We have added a figure to the main article that shows the recommendations as a function of signed or non-signed reviews per year, because it seems at least some readers (such as Reviewer 1) would believe signed reviews are becoming more common.
+However, as the data shows, this is not the case.
+We already wrote in the previous version (and have not changed the sentence) that: "The percentages of people who signed (38.23% for PeerJ, 36.99% for Royal Society Open journals) are slightly lower than the 43.23% reported by Wang, You, Manasa, and Wolfram (2016) who analyzed the first 1214 articles published in PeerJ".
+In other words, there is actually a decline in the percentage of signed reviews, and the new figure makes this even more clear.
+One can only speculate why this is the case, but one reason might be that early adopters (those academics who reviewed for RSOS and PeerJ when the journals were new) were more likely to sign, but as the journal became wider known, and received more submissions, the journals relied on more the more average scientist, who might be less likely to sign than early adopters.
+Whatever the reason, it is informative to know progress is not as imminent as Reviewer 1 expects.
+We now write:**
+
+*In line with our earlier observation that the proportion of signed reviews reduced over time compared to earlier analyses by Wang et al., (2016), we see that this conclusion holds for both PeerJ and Royal Society Open journals.
+It seems that in the early years that these journals existed, more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews.
+We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts.
+As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science.*
+
+Comment #5
+
+Journals sometimes give the authors of a submitted manuscript the option to suggest reviewers.
+If authors can nominate negative reviewers, one might suspect that the rate of positive signed reviews would be an underestimate.
+The authors should report on whether PeerJ or Royal Society Open Science have this policy, and what it might mean for policies of open peer review.
+
+**Reviewer 1 notes that perhaps RSOS and PeerJ ask authors to recommend reviewers. We checked, and this is indeed the case.**
+
+**RSOS has in the submission portal the following instruction:**
+
+*You are required to supply at least 4 preferred referees, and are required to supply a reason for the preference.
+Enter the reviewer's information into the textboxes below and click the appropriate designation button.*
+
+*Royal Society Open Science is committed to increasing the diversity of its reviewer pool.
+When recommending reviewers, we would particularly appreciate suggestions of suitably qualified researchers from underrepresented groups (including women, ethnic minority scientists, scientists with disabilities and other underrepresented groups), early career researchers, and researchers from the global South.*
+
+*Your suggestions should:*
+
+*-- include an institutional email address (ie not a yahoo, gmail or equivalent commercial domain) to help us verify their identity;*
+
+*-- be experts in the field (ie at least a PhD and an established, verifiable publication record);*
+
+*-- not be someone with whom you have a financial, professional, or personal conflict of interest.
+Conflicts of interest include, but are not limited to working or having recently worked in the same institution or department as any of the authors and having recently (eg in the past 3 years) been a supervisor, mentor, mentee, close collaborator or joint grant holder with any of the authors.*
+
+*If you are indicating opposition to a possible referee, please provide a full reason for the opposition -- an explanation of the nature of the conflict is required if you state you have a conflict of interest with a specific referee.
+It is insufficient to simply state you have a conflict.*
+
+*To designate preferred and non-preferred editors, select them from the dropdown and click the appropriate designation button.*
+
+PeerJ has the following instructions in the submission portal:
+
+*2. Suggest at least 2 editors, and 3 reviewers for your article.*
+*Conflict of Interest checks:*
+
+*Reviewers must not have published with you or co-authors in last 5 years.*
+*Reviewers must not be at the same institution as you or co-authors.*
+*Your submission may be rejected if a Conflict of Interest is identified.*
+
+**There is no way to know which reviewers in our dataset were suggested and which were not, nor what the impact of this is on how often they sign.
+If anything, personally we would believe a main effect might be most plausible (more positive recommendations by suggested reviewers) but it is possible that suggested reviewers are more likely to not sign when giving negative recommendations than non-suggested reviewers.
+Therefore, we added a sentence indicating that 1) Royal Society Open journals and PeerJ allow authors to recommend reviewers, and 2) that we do not know if our findings will generalize to journals that have different policies:**
+
+*It is possible to indicate suggested and opposed reviewers when submitting a manuscript at PeerJ and RSOS.
+It is unknown how often suggested reviewers end up reviewing submissions, or whether suggested or non-suggested reviewers differ in how often they sign their reviews, depending on their recommendation.
+It therefore is unknown whether the current results will generalize to journals that do not ask authors to recommend reviewers.*
+
+Comment #6
+There is unlikely to be one reason why reviews go unsigned, and I think the authors pick the one most generalisable.
+However, backlash can come in different forms.
+A career-limiting critical peer review is one form of backlash, but another is revealing how peer review can be gamed.
+
+**Regarding comment 6, the reviewer raised a very good point about there being multiple reasons not to sign, and how we higlighted only one.
+Although we think negative backlash is a clear concern based on additional research, we have added a sentence in the discussion highlighting different reasons for not signing, which included the concern about CoI's raised by the reviewer:**
+
+*Reviewers might have different reasons to sign or not sign their reviews.
+They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission.
+Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
+Finally, reviewers might fear backlash from authors who receive their negative reviews.*
+
+We have corrected all spelling errors (also those kindly pointed out by the editor) and the link to the Bastian blog post should work now.
+
+# Reviewer 2
+
+1: It would be helpful to add a one paragraph description of PeerJ and RSOS. It might
 include their scope, reputation, or any other information that would allow the reader to
-contextualize the sample. [I think we can combine this with point 5 above]
+contextualize the sample.
+
+**We have added some information about the scope of PeerJ and Royal Society Open journals, in the section in the current study, which already contained important information about the journals:**
+
+*PeerJ and Royal Society Open journals publish articles across a wide range of scientific disciplines, including biology, chemistry, engineering, life sciences, mathematics, and medicine*
+
+**Concerning the reputation of these journals: We do not feel qualified to make a judgment on behalf of others.
+We think these are good journals, and have published in both, and reviewed for both.
+But researchers should make up their own mind, and the experiences researchers have might differ across scientific disciplines, so we stick with objective facts when describing the journal (e.g., how long it has had open reviews, how long the journals exist, and the topics they publish on).
+We also discuss the scope of journals in the new Figure plotting the data across sections in PeerJ.**
 
 2: Add information to make the figures more distinct. Figure 2 can include the words “Royal
-Society”. This will make clear using the figures alone that figures 1 and 2 represent entirely
-separate samples.
+Society”. This will make clear using the figures alone that figures 1 and 2 represent entirely separate samples.
 
-3: *Under the subheading “Additional Analyses”, the authors offer some analysis regarding “how
-often reviewers agree.” This is an interesting approach to a common-place but under-studied
-phenomena in meta-science. That said, these analyses don’t contribute to the main theme of the
-paper, are not referenced in any other part of the paper, are not situated in the reviewed literature,
-and are not interpreted in any way. I suggest that this section be either removed or expanded and
-incorporated into the larger theme. 
-[I agree - it is more like a motivation for people to explore that data further. Maybe remove, maybe make clearer it is just to show the data is available]
+**We have added titles to the figures to make the figures more distinct.**
 
-4: Reputations could easily be damaged by this type of transparency if it became known one reviewed retracted papers. Combine with point 6 by reviewer 1.
+3: *Under the subheading “Additional Analyses”, the authors offer some analysis regarding “how often reviewers agree.” This is an interesting approach to a common-place but under-studied phenomena in meta-science.
+That said, these analyses don’t contribute to the main theme of the paper, are not referenced in any other part of the paper, are not situated in the reviewed literature, and are not interpreted in any way.
+I suggest that this section be either removed or expanded and incorporated into the larger theme.
 
-5: The authors acknowledge that the causal relationship for the relationship they observe could run
-two different ways. Given the (well-acknowledged) incomplete nature of the data, considering at
-least one more counter-narrative would make for a more complete treatment of the issue.
+**We understand this comment by the reviewer, and agree the 'additional analyses' header immediately after the 'results' section was an unfortunate choice.
+What we wanted to achieve was to highlight the richness of the datafile we are sharing, and invite fellow meta-scientists to make use of this data.
+We also made this point in the general discussion, and have now removed the 'additional analyses' section, and instead discussed the variables in the dataset, including the analysis of agreement among reviewers as an example, in the discussion.
+The section now follows the sentence in the first version of the manuscript: "Open reviews allow researchers to examine meta-scientific questions that give insights into the peer review process." and is followed by "We hope the dataset we share with this manuscript will allow other meta-scientists to examine additional questions about the peer review process." We hope this makes the point of this section clearer (it is not presented as an analysis related to the main question in our manuscript, but an illustration of the kind of questions that could be answered in our data analysis).**
 
-Editor comments:
+Point 4: The reviewer raises a very important point how reputations could easily be damaged by this type of transparency if it became known one reviewed retracted papers.
+We have combined this with addressing point 6 by reviewer 1 and added the following to the discussion:
+
+*Reviewers might have different reasons to sign or not sign their reviews.
+They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission.
+Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
+Finally, reviewers might fear backlash from authors who receive their negative reviews.*
+
+5: The authors acknowledge that the causal relationship for the relationship they observe could run two different ways.
+Given the (well-acknowledged) incomplete nature of the data, considering at least one more counter-narrative would make for a more complete treatment of the issue.
+
+**We already raised a counter narrative in the results section, but perhaps the reviewer means we should also highlight the opposite relationship in the discussion, which is a fair comment that we incorporated in the revision.
+We have now added in the discussion:**
+
+*Due to the correlational nature of the data, this relationship could emerge because reviewers who are on average more likely to sign also give more positive recommendations, reviewers are more likely to sign more positive recommendations, or both these effects could be true at the same time.*
+
+# Editor comments:
 
@@
 
-[There are no p-values, because the work is descriptive. We do not intend to make any claims - or do we? MAgnitude of effect can be seen in %, no?
+**We do not present quantitative analyses because we have analyzed the entire population of open reviews in PeerJ and Royal Society Open journals, and are simply presenting and interpreting the descriptive statistics.
+Since our main results are presented as proportions, we doubt recalculating these as odds ratios adds much about the magnitude of the effect - we hope proportions are relatively straightforward to understand.
+We could add an odds ratio for the results for PeerJ (but remember we have excluded 22 directly accepted results, so there is a third category), but this would be more complex for Royal Society Open journals given the 4 recommendation categories.
+We also wouldn't know which effect sizes in the literature to compare the effect sizes with, and given main effects between journals (e.g., differences in the proportion of minor vs major revision recommendations) we  would not know what analyses to report, beyond providing researchers with the descriptives based on the entire population.
+We are happy to consider any specific suggestions.**
 
@@
 that at PeerJ, readers do not get to see the individual reviewers’ recommendations.
+
+**This is indeed an interesting point to mention.
+Reviewers do not see the recommendation (although reviewers make a recommendation).
+We have included this information in our discussion about how PeerJ and Royal Sociey Open journals work.
+We hesitate to discuss possible consequences of this.
+One might believe it would make reviewers more comfortable to recommend to reject, even while signing, because they can 'hide' behind the editor decision.
+Reviewers still get to read the reviews.
+It could be that the private decision differs from the publicly available review.
+But there is no way to know without having access to confidential information about the peer review process.
+We have added the following to the discussion:**
+
+*It is interesting to note that PeerJ asks reviewers for a recommendation, but only shares the reviews and the editor's decision with the authors.
+It would be interesting to examine whether this feature of the review process impacts reviewer's decision to sign.*
 
@@
 my earlier remark about effect sizes) across a sample that encompasses a wide range of disciplines.
-It could be that the effect is
-stronger for psychology and weaker or absent for biomedical sciences, for example. 
-[Combine with point 1 and 2 of Reviewer 1]
+It could be that the effect is stronger for psychology and weaker or absent for biomedical sciences, for example.
+
+*We agree - This comment aligns with that of Reviewer 1, point 1 and 2, and our new table for PeerJ which shows the same pattern across all disciplines suggest the pattern we have observed is not specific to any field, but surprisingly general.*
 
@@
 negative reviews they do not run the risk of receiving any backlash from colleagues in their
-field” (p. 4)—I’m not sure if “credit” is the right word. Reviewers who write a glowing report on
-a manuscript can certainly expect to be liked by its author(s), but whether or not the rest of their
-colleagues (and the field as a whole) will give them any sort of “credit” will depend on whether
-the article later turns out to be flawed (and/or whether it upsets some powerful people); and the
-same could apply in reverse for a negative review. So perhaps this comment should be rephrased
-to emphasise that any “credit” is restricted to approval felt from the author(s) of the accepted
-article. 
-[True, combine with point 4 by reviewer 2]
+field” (p.
+4)—I’m not sure if “credit” is the right word.
+Reviewers who write a glowing report on a manuscript can certainly expect to be liked by its author(s), but whether or not the rest of their colleagues (and the field as a whole) will give them any sort of “credit” will depend on whether the article later turns out to be flawed (and/or whether it upsets some powerful people); and the same could apply in reverse for a negative review.
+So perhaps this comment should be rephrased to emphasise that any “credit” is restricted to approval felt from the author(s) of the accepted article.
+
+**This is a good point that we missed, but which is echoed in comment point 4 by reviewer 2, and point 6 by Reviewer 1. We have addressed this in the new sentences in the discussion:**
+
+*They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission.
+Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
+Finally, reviewers might fear backlash from authors who receive their negative reviews.*
 
 6: I downloaded the code and data associated with the manuscript via the OSF link and was
-able to reproduce the main numerical results and figures. However, the percentages in the first
-paragraph on page 4 were printed with a lot more decimal places than in the PDF file (e.g., “For
-41.7218543% of the manuscripts the maximum deviation was one category”). I wonder if your R
-setup has a different global rounding option from mine? For best reproducibility, rounding
-should probably be done explicitly in the code.
+able to reproduce the main numerical results and figures.
+However, the percentages in the first paragraph on page 4 were printed with a lot more decimal places than in the PDF file (e.g., “For 41.7218543% of the manuscripts the maximum deviation was one category”).
+I wonder if your R setup has a different global rounding option from mine?
+For best reproducibility, rounding should probably be done explicitly in the code.
+
+**You probably ran the code, line by line.
+If you 'knit' the document, the papaja package will reproduce the submitted PDF exactly, including the rounding.
+We will make sure that our manuscript is available as a completely reproducible Code Ocean capsule, so that anyone can reproduce our results, without needing to install any software locally.**

### 2020-05-30 manuscript/revision_2/open_peer_review.Rmd
revision 2

@@
 keywords          : "Peer Review, Open Reviews, Transparency, Open Science"
-wordcount         : 2711
+wordcount         : 3282
 bibliography      : ["signing_open_peer_review_.bib"]
@@
 library(ggplot2)
-library(here)
+library(gridExtra)
 
-here::here()
+setwd("C:/Users/dlakens/surfdrive/R/open_peer_review")
 #### READ IN DATA
 # Read open science and open biology rds datafiles
-TRS_data_os <- readRDS(file = "../../royal_society_data_os.rds")
-TRS_data_ob <- readRDS(file = "../../royal_society_data_ob.rds")
+TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
+TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")
 # Combine both datasets into one.
@@
 #Read in PeerJ data
-PeerJ_main_data <- readRDS(file = "../../peerj_data.rds")
-PeerJ_cs_data <- readRDS(file = "../../peerj_cs_data.rds")
+PeerJ_main_data <- readRDS(file = "peerj_data.rds")
+PeerJ_cs_data <- readRDS(file = "peerj_cs_data.rds")
 # Combine both datasets into one.
@@
 # We can see how many reviews are open in TRS by counting all doi in scopus, and seeing how many end up in our list of open reviews:
-OS_pdf_list <- readLines(file("../../royal_society_pdf_files/OS_pdf_list.txt", open = "r"))
+OS_pdf_list <- readLines(file("royal_society_pdf_files/OS_pdf_list.txt", open = "r"))
 
-open_review_TRS <- length(OS_pdf_list) / length(read.csv("../../scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
+open_review_TRS <- length(OS_pdf_list) / length(read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)$DOI)
 
 # How many entries in RSOS in total? Read in scopus datafile
-TRS_scopus_OS <- read.csv("../../scopus_export_rsos.csv", stringsAsFactors = FALSE)
+TRS_scopus_OS <- read.csv("scopus_export_rsos.csv", stringsAsFactors = FALSE)
 table(TRS_scopus_OS$Document.Type)
@@
 # How many entries in RSOS in total? Read in scopus datafile
-TRS_scopus_OB <- read.csv("../../scopus_export_rsob.csv", stringsAsFactors = FALSE)
+TRS_scopus_OB <- read.csv("scopus_export_rsob.csv", stringsAsFactors = FALSE)
 table(TRS_scopus_OB$Document.Type)
@@
 
-# How many reviews in total in the traw txt files?
+# How many reviews in total in the raw txt files?
 length(TRS_data$df_anonymous)+length(PeerJ_data$df_anonymous)
+
+# Adding year from scopus to TRS data
+# First add doi column to merge on
+TRS_data$DOI <- gsub('http://dx.doi.org/','',TRS_data$df_link)
+# Create joint SCOPUS dataframe
+TRS_scopus <- rbind(TRS_scopus_OS, TRS_scopus_OB)
+# Merge datasets - we lose 1 row for missing DOI (figshare doi)
+TRS_data <- merge(TRS_data, TRS_scopus, by = 'DOI')
 
@@
 
-PeerJ_data_R1$df_section[1]
 # Do the same for TRS
@@
 #Select the top recommendation for each review
-TRS_data_R1_top <- top_n(TRS_data_R1, 1, df_recommendation) 
+TRS_data_R1_top <- top_n(TRS_data_R1, 1, as.numeric(df_recommendation)) 
 TRS_data_R1_top <- TRS_data_R1_top[!duplicated(TRS_data_R1_top$df_link),]
 #Select the bottom recommendation for each review
-TRS_data_R1_bottom <- top_n(TRS_data_R1, -1, df_recommendation) 
+TRS_data_R1_bottom <- top_n(TRS_data_R1, -1, as.numeric(df_recommendation)) 
 TRS_data_R1_bottom <- TRS_data_R1_bottom[!duplicated(TRS_data_R1_bottom$df_link),]
@@
 #Compute the difference between top and bottom
-rev_dif <- TRS_data_R1_top$df_recommendation - TRS_data_R1_bottom$df_recommendation
+rev_dif <- as.numeric(TRS_data_R1_top$df_recommendation) - as.numeric(TRS_data_R1_bottom$df_recommendation)
 #We table the difference - many are similar, many differ 1 category, some 2 few 3.
@@
 
-We examined the relationship between the recommendations peer reviewers made and the proportion of signed reviews in two large open access journals, PeerJ (including reviews for PeerJ Computer Science) and Royal Society Open Science (including Royal Society Open Biology).
+We examined the relationship between the recommendations peer reviewers made and the proportion of signed reviews in two large open access journals, PeerJ (including reviews for PeerJ Computer Science) and Royal Society Open journals (Royal Society Open Science and Royal Society Open Biology).
 We ignored more recently launched PeerJ journals in the field of Chemistry due to the small number of articles published to date in these journals.
-PeerJ and Royal Society Open journals publish articles across a wide range of scientific disciplines, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
+PeerJ and Royal Society Open journals publish articles across a wide range of scientific disciplines, including biology, chemistry, engineering, life sciences, mathematics, and medicine, thus allowing us to replicate and extend the analysis by Bravo and colleagues (2019).
 PeerJ launched in 2012 and PeerJ Computer Science launched in 2015.
@@
 For minor revisions, a greater proportion of reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
-Too few articles are immediately accepted after the first round of reviews in PeerJ (`r sum(PeerJ_data_R1$df_recommendation == 1, na.rm = TRUE)` in total) to impact the proportions in the other two categories.
+Too few articles are immediately accepted after the first round of reviews in PeerJ (`r sum(as.numeric(PeerJ_data_R1$df_recommendation) == 1, na.rm = TRUE)` in total) to impact the proportions in the other two categories.
 
@@
   theme_linedraw(base_size = 20) +  
-  theme(legend.position = "top",
+  theme(legend.position = "bottom",
         legend.title=element_blank(),
+        plot.title = element_text(hjust = 0.5),
         panel.grid.major.x = element_blank()) + 
@@
   coord_cartesian(ylim = c(0, 1)) +
+  ggtitle("PeerJ recommendations") +
   geom_text(aes(label = sprintf('%.2f',proportion)), 
@@
   theme_linedraw(base_size = 20) + 
-  theme(legend.position = "top",
+  theme(legend.position = "bottom",
         legend.title=element_blank(),
+        plot.title = element_text(hjust = 0.5),
         panel.grid.major.x = element_blank()) + 
@@
   coord_cartesian(ylim = c(0, 1)) +
+  ggtitle("Royal Society recommendations") +  
   geom_text(aes(label = sprintf('%.2f',proportion)), 
@@
 
+Both PeerJ as Royal Society Open journals publish articles in a wide range of disciplines, including astronomy, biochemistry, chemistry, computer science, earth science, ecology, engineering, genomics, mathematics, evolutionary biology, paleontology, physics, psychology, and zoological science.
+The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available for Royal Society Open journals.
+
 ```{r, echo=FALSE, results='asis'}
@@
 
-```{r, warning=FALSE, PeerJrecperfield, fig.width=15, fig.height=10, fig.cap = "Proportion of 'minor revisions' or 'major revisions' recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned."}
+```{r, warning=FALSE, PeerJrecperfield, fig.width=15, fig.height=16, fig.cap = "Total number of 'minor revisions' or 'major revisions' recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned across different scientific disciplines."}
 
@@
 
-plot_data_by_field_long <- gather(plot_data_by_field, signed, proportion, signed:unsigned, factor_key = TRUE)
+plot_data_by_field_long <- gather(plot_data_by_field, signed, count, signed:unsigned, factor_key = TRUE)
 
-ggplot(plot_data_by_field_long, aes(x = df_recommendation, y = proportion, fill = signed)) +
+ggplot(plot_data_by_field_long, aes(x = df_recommendation, y = count, fill = signed)) +
   geom_bar(position="dodge", stat="identity") +
@@
   coord_cartesian(ylim = c(0, 900)) +
-  geom_text(aes(label = proportion), # to add rounding: sprintf('%.2f',proportion)
+  geom_text(aes(label = count), # to add rounding: sprintf('%.2f',proportion)
               size = 6, 
@@
 
-```{r, TRSrecpergroup, fig.width=15, fig.height=4, fig.cap = "Proportion of 'accept', 'minor revisions', 'major revisions', or 'reject' recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned."}
+<!-- ```{r, TRSrecpergroup, fig.width=15, fig.height=4, fig.cap = "Proportion of 'accept', 'minor revisions', 'major revisions', or 'reject' recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned."} -->
 
-# Makes more sense to plot proportions
-TRS_anonymous_by_recommendation_proportion <- TRS_anonymous_by_recommendation/sum(TRS_anonymous_by_recommendation)
-TRS_notanonymous_by_recommendation_proportion <- TRS_notanonymous_by_recommendation/sum(TRS_notanonymous_by_recommendation)
+<!-- # Makes more sense to plot proportions -->
+<!-- TRS_anonymous_by_recommendation_proportion <- TRS_anonymous_by_recommendation/sum(TRS_anonymous_by_recommendation) -->
+<!-- TRS_notanonymous_by_recommendation_proportion <- TRS_notanonymous_by_recommendation/sum(TRS_notanonymous_by_recommendation) -->
 
-# As asked by reviewers, how does this differ over subfields?
+<!-- # As asked by reviewers, how does this differ over subfields? -->
 
-# Reproducing proportions using dplyr per field
-plot_data_by_field <- TRS_data_R1 %>% 
-  group_by(df_recommendation, df_section) %>% 
-  summarise(signed = sum(df_anonymous == 0)/sum(TRS_notanonymous_by_recommendation), unsigned = sum(df_anonymous == 1)/sum(TRS_anonymous_by_recommendation))
+<!-- # Reproducing proportions using dplyr per field -->
+<!-- plot_data_by_field <- TRS_data_R1 %>%  -->
+<!--   group_by(df_recommendation, df_section) %>%  -->
+<!--   summarise(signed = sum(df_anonymous == 0)/sum(TRS_notanonymous_by_recommendation), unsigned = sum(df_anonymous == 1)/sum(TRS_anonymous_by_recommendation)) -->
+
+<!-- # Reproducing counts using dplyr per field -->
+<!-- plot_data_by_field <- TRS_data_R1 %>% -->
+<!--   group_by(df_recommendation, df_section) %>% -->
+<!--   summarise(signed = sum(df_anonymous == 0), unsigned = sum(df_anonymous == 1)) -->
+
+<!-- plot_data_by_field_long <- gather(plot_data_by_field, signed, proportion, signed:unsigned, factor_key = TRUE) -->
+
+<!-- ggplot(plot_data_by_field_long, aes(x = df_recommendation, y = proportion, fill = signed)) + -->
+<!--   geom_bar(position="dodge", stat="identity") + -->
+<!--   theme_linedraw(base_size = 20) +   -->
+<!--   theme(legend.position = "bottom", -->
+<!--         legend.title=element_blank(), -->
+<!--         panel.grid.major.x = element_blank(), -->
+<!--         plot.title = element_text(hjust = 0.5), -->
+<!--         axis.title.x=element_blank()) +  -->
+<!--   scale_fill_manual(values = c("#000000", "#808080")) +  -->
+<!--   coord_cartesian(ylim = c(0, 1200)) + -->
+<!--   geom_text(aes(label = proportion), # to add rounding: sprintf('%.2f',proportion) -->
+<!--               size = 6,  -->
+<!--               color = "black", -->
+<!--               position = position_dodge(width = 0.9), -->
+<!--               vjust = -.5) +  -->
+<!--   ggtitle("Royal Society Open recommendations") + -->
+<!--   facet_wrap(~df_section, ncol = 4) -->
+
+<!-- ``` -->
+
+```{r, warning=FALSE, recperyear, fig.width=15, fig.height=17, fig.cap = "Total number of signed and unsigned reviews for each of the different possible recommendations for PeerJ and Royal Society Open journals per year."}
+
+#As requested by reviewers, show pattern over time.
 
 # Reproducing counts using dplyr per field
-plot_data_by_field <- TRS_data_R1 %>%
-  group_by(df_recommendation, df_section) %>%
+plot_data_by_year <- PeerJ_data_R1 %>%
+  group_by(df_recommendation, df_year) %>%
   summarise(signed = sum(df_anonymous == 0), unsigned = sum(df_anonymous == 1))
 
-plot_data_by_field_long <- gather(plot_data_by_field, signed, proportion, signed:unsigned, factor_key = TRUE)
+# Filter NA and direct accepts
+plot_data_by_year <- plot_data_by_year %>% filter(as.integer(df_year) > 1, as.integer(df_recommendation) > 1)
 
-ggplot(plot_data_by_field_long, aes(x = df_recommendation, y = proportion, fill = signed)) +
+plot_data_by_year_long <- gather(plot_data_by_year, signed, count, signed:unsigned, factor_key = TRUE)
+
+p1 <- ggplot(plot_data_by_year_long, aes(x = df_recommendation, y = count, fill = signed)) +
   geom_bar(position="dodge", stat="identity") +
@@
   scale_fill_manual(values = c("#000000", "#808080")) + 
-  coord_cartesian(ylim = c(0, 1200)) +
-  geom_text(aes(label = proportion), # to add rounding: sprintf('%.2f',proportion)
+  coord_cartesian(ylim = c(0, 1500)) +
+  geom_text(aes(label = count), # to add rounding: sprintf('%.2f',proportion)
               size = 6, 
@@
               vjust = -.5) + 
-  ggtitle("Royal Society Open recommendations") +
-  facet_wrap(~df_section, ncol = 4)
+  ggtitle("PeerJ recommendations per year") +
+  facet_wrap(~df_year, ncol = 4)
+
+# Reproducing counts using dplyr per field
+plot_data_by_year <- TRS_data_R1 %>%
+  group_by(df_recommendation, Year) %>%
+  summarise(signed = sum(df_anonymous == 0), unsigned = sum(df_anonymous == 1))
+
+# Filter NA and direct accepts
+plot_data_by_year <- plot_data_by_year %>% filter(as.integer(Year) > 1, as.integer(df_recommendation) > 1)
+
+plot_data_by_year_long <- gather(plot_data_by_year, signed, count, signed:unsigned, factor_key = TRUE)
+
+p2 <- ggplot(plot_data_by_year_long, aes(x = df_recommendation, y = count, fill = signed)) +
+  geom_bar(position="dodge", stat="identity") +
+  theme_linedraw(base_size = 20) +  
+  theme(legend.position = "bottom",
+        legend.title=element_blank(),
+        panel.grid.major.x = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        axis.title.x=element_blank()) + 
+  scale_fill_manual(values = c("#000000", "#808080")) + 
+  coord_cartesian(ylim = c(0, 500)) +
+  geom_text(aes(label = count), # to add rounding: sprintf('%.2f',proportion)
+              size = 6, 
+              color = "black",
+              position = position_dodge(width = 0.9),
+              vjust = -.5) + 
+  ggtitle("Royal Society Open recommendations per year") +
+  facet_wrap(~Year, ncol = 3)
+
+grid.arrange(p1, p2, ncol = 1)
 
@@
 
-# Additional Analyses
+To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section).
+We see the general pattern holds across all fields.
+In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned.
+Beyond this main effect, we see a clear interaction across all sections, where the ratio of signed versus unsigned reviews is consistently greater for major revisions than for minor revisions.
+Across all fields covered by PeerJ, it is relatively less likely to see a signed review for major revisions than for minor revisions, suggesting that the observed effect is present across disciplines.
 
-The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review  (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for Royal Society Open journals).
-Using the DOI, researchers can link this data to other sources of information such as citation counts.
-Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
-Since we know the individual recommendation of each reviewer for Royal Society Open journals, one example of the insights that open reviews provide is how often reviewers agree.
-For the `r sum(table(rev_dif))` papers where the reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
-For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
-There were `r sum(TRS_review_agree$df_unique == 4)` articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
-
-Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected.
-As a consequence, we have analyzed a biased sample of the literature.
-Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
-Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
-Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.
+Figure \ref{fig:recperyear} shows the number of signed and unsigned reviews as a function of the recommendation for each year in which articles were published (since 2012 for PeerJ, and since 2014 for Royal Society Open journals).
+As already noted, the proportion of signed reviews reduced over time compared to earlier analyses by @wang_open_2016.
+Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals.
+It seems that in the early years that these journals existed, more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews.
+We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts.
+As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science, to include reviewers less likely to sign their reviews.
 
@@
 
+It might be that some reviewers consistently sign their reviews, while others sign selectively.
+Some researchers have contributed multiple signed reviews to our dataset, but it is unknown whether they also contributed unsigned reviews.
+The confidentiality of peer review makes it impossible to retrieve whether reviewers selectively sign from open reviews, and this question will need to be studied by surveying researchers directly.
+It is possible to indicate suggested and opposed reviewers when submitting a manuscript at PeerJ and RSOS.
+It is unknown how often suggested reviewers end up reviewing submissions, or whether suggested or non-suggested reviewers differ in how often they sign their reviews, depending on their recommendation.
+It therefore is unknown whether the current results will generalize to journals that do not ask authors to recommend reviewers.
+It is interesting to note that PeerJ asks reviewers for a recommendation, but only shares the reviews and the editor's decision with the authors.
+It would be interesting to examine whether this feature of the review process impacts reviewer's decision to sign.
+
+Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected.
+As a consequence, we have analyzed a biased sample of the literature.
+Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
+Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
+Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.
+
 Peer review is generally seen as an important quality control mechanism in science, yet researchers can rarely evaluate the quality of peer review at journals.
 Open reviews allow researchers to examine meta-scientific questions that give insights into the peer review process.
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (`r round(mean(PeerJ_unique$df_days, na.rm = TRUE),0)` days for PeerJ, `r round(mean(TRS_unique$df_days, na.rm = TRUE),0)` days for Royal Society Open journals).
+Using the DOI, researchers can link this data to other sources of information such as citation counts.
+Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
+Since we know the individual recommendation of each reviewer for Royal Society Open journals, one example of the insights that open reviews provide is how often reviewers agree.
+For the `r sum(table(rev_dif))` papers where the reviews were published, all reviewers agreed on the recommendation for `r table(rev_dif)[1]` articles (`r 100 * table(rev_dif)[1]/sum(table(rev_dif))`% of the time).
+For `r 100 *  table(rev_dif)[2]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for `r 100 *  table(rev_dif)[3]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for `r 100 *  table(rev_dif)[4]/sum(table(rev_dif))`% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
+There were `r sum(TRS_review_agree$df_unique == 4)` articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
+We hope the dataset we share with this manuscript will allow other meta-scientists to examine additional questions about the peer review process.
+
+Reviewers might have different reasons to sign or not sign their reviews.
+They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission.
+Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
+Finally, reviewers might fear backlash from authors who receive their negative reviews.
 Our data supports the idea that reviewers' decisions to sign are related to their recommendation across a wide range of scientific disciplines.
+Due to the correlational nature of the data, this relationship could emerge because reviewers who are on average more likely to sign also give more positive recommendations, reviewers are more likely to sign more positive recommendations, or both these effects could be true at the same time.
 Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some reviewers are more likely to sign if their recommendation is more positive.
@@
 
-# Author Contributions
+## Author Contributions
 
@@
 
-# Competing interests
+## Conflict of Interest Statement
 
-The authors report no conflicts of interest.
+The authors report no conflict of interest.
+
+## Funding
+
+This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
+
+## ORCID iD
+
+Daniel Lakens ![](orcid.png) https://orcid.org/0000-0002-0247-239X
 

### 2020-05-30 manuscript/revision_2/open_peer_review.tex
revision 2

@@
 Correspondence concerning this article should be addressed to Daniel Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: D.Lakens@tue.nl}
-\keywords{Peer Review, Open Reviews, Transparency, Open Science\newline\indent Word count: 2711}
+\keywords{Peer Review, Open Reviews, Transparency, Open Science\newline\indent Word count: 3282}
 \usepackage{dblfloatfix}
@@
 In total 4592 reviewers signed their review for the initial submission, and 7418 reviewers did not.
-In Royal Society Open journals we analyzed 1964 articles for which we retrieved 4188 unique reviews for the first submission, where 1549 reviewers signed their review and 2639 did not.
-The percentages of people who signed (38.23\% for PeerJ, 36.99\% for Royal Society Open journals) are slightly lower than the 43.23\% reported by Wang, You, Manasa, and Wolfram (2016) who analyzed the first 1214 articles published in PeerJ.
+In Royal Society Open journals we analyzed 1964 articles for which we retrieved 4186 unique reviews for the first submission, where 1547 reviewers signed their review and 2639 did not.
+The percentages of people who signed (38.23\% for PeerJ, 36.96\% for Royal Society Open journals) are slightly lower than the 43.23\% reported by Wang, You, Manasa, and Wolfram (2016) who analyzed the first 1214 articles published in PeerJ.
 
@@
 For minor revisions, a greater proportion of reviews was signed than unsigned, but for major revisions, more reviews were unsigned than signed.
-Too few articles are immediately accepted after the first round of reviews in PeerJ (0 in total) to impact the proportions in the other two categories.
+Too few articles are immediately accepted after the first round of reviews in PeerJ (22 in total) to impact the proportions in the other two categories.
 
@@
 
+Both PeerJ as Royal Society Open journals publish articles in a wide range of disciplines, including astronomy, biochemistry, chemistry, computer science, earth science, ecology, engineering, genomics, mathematics, evolutionary biology, paleontology, physics, psychology, and zoological science.
+The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available for Royal Society Open journals.
+
 \onecolumn
@@
 \includegraphics{open_peer_review_files/figure-latex/PeerJrecperfield-1.pdf}
-\caption{\label{fig:PeerJrecperfield}Proportion of \enquote{minor revisions} or \enquote{major revisions} recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned.}
+\caption{\label{fig:PeerJrecperfield}Total number of \enquote{minor revisions} or \enquote{major revisions} recommendations by the handling editor at PeerJ conditioned on whether reviews were signed or unsigned across different scientific disciplines.}
 \end{figure}
@@
 \centering
-\includegraphics{open_peer_review_files/figure-latex/TRSrecpergroup-1.pdf}
-\caption{\label{fig:TRSrecpergroup}Proportion of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject} recommendations by reviewers of Royal Society Open journals conditioned on whether reviews were signed or unsigned.}
+\includegraphics{open_peer_review_files/figure-latex/recperyear-1.pdf}
+\caption{\label{fig:recperyear}Total number of signed and unsigned reviews for each of the different possible recommendations for PeerJ and Royal Society Open journals per year.}
 \end{figure}
@@
 
-\hypertarget{additional-analyses}{%
-\section{Additional Analyses}\label{additional-analyses}}
+To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section).
+We see the general pattern holds across all fields.
+In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned.
+Beyond this main effect, we see a clear interaction across all sections, where the ratio of signed versus unsigned reviews is consistently greater for major revisions than for minor revisions.
+Across all fields covered by PeerJ, it is relatively less likely to see a signed review for major revisions than for minor revisions, suggesting that the observed effect is present across disciplines.
 
-The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for Royal Society Open journals).
-Using the DOI, researchers can link this data to other sources of information such as citation counts.
-Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
-Since we know the individual recommendation of each reviewer for Royal Society Open journals, one example of the insights that open reviews provide is how often reviewers agree.
-For the 0 papers where the reviews were published, all reviewers agreed on the recommendation for NA articles (NA\% of the time).
-For NA\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for NA\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for NA\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
-There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
-
-Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected.
-As a consequence, we have analyzed a biased sample of the literature.
-Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
-Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
-Despite this limitation, the pattern of results we observe is very similar to that reported by Bravo et al.
-(2019) who had access to the reviews for accepted and rejected manuscripts.
+Figure \ref{fig:recperyear} shows the number of signed and unsigned reviews as a function of the recommendation for each year in which articles were published (since 2012 for PeerJ, and since 2014 for Royal Society Open journals).
+As already noted, the proportion of signed reviews reduced over time compared to earlier analyses by Wang et al.
+(2016).
+Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals.
+It seems that in the early years that these journals existed, more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews.
+We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts.
+As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science, to include reviewers less likely to sign their reviews.
 
@@
 
+It might be that some reviewers consistently sign their reviews, while others sign selectively.
+Some researchers have contributed multiple signed reviews to our dataset, but it is unknown whether they also contributed unsigned reviews.
+The confidentiality of peer review makes it impossible to retrieve whether reviewers selectively sign from open reviews, and this question will need to be studied by surveying researchers directly.
+It is possible to indicate suggested and opposed reviewers when submitting a manuscript at PeerJ and RSOS.
+It is unknown how often suggested reviewers end up reviewing submissions, or whether suggested or non-suggested reviewers differ in how often they sign their reviews, depending on their recommendation.
+It therefore is unknown whether the current results will generalize to journals that do not ask authors to recommend reviewers.
+It is interesting to note that PeerJ asks reviewers for a recommendation, but only shares the reviews and the editor's decision with the authors.
+It would be interesting to examine whether this feature of the review process impacts reviewer's decision to sign.
+
+Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected.
+As a consequence, we have analyzed a biased sample of the literature.
+Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
+Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
+Despite this limitation, the pattern of results we observe is very similar to that reported by Bravo et al.
+(2019) who had access to the reviews for accepted and rejected manuscripts.
+
 Peer review is generally seen as an important quality control mechanism in science, yet researchers can rarely evaluate the quality of peer review at journals.
 Open reviews allow researchers to examine meta-scientific questions that give insights into the peer review process.
+The dataset we are sharing has information about the recommendations of reviewers (RSOS and RSOB) or editors (PeerJ) after each round of peer review, the names of reviewers who signed their review, and the time in review (114 days for PeerJ, 132 days for Royal Society Open journals).
+Using the DOI, researchers can link this data to other sources of information such as citation counts.
+Because the reviews themselves are included in our dataset, researchers can use the text files to answer more detailed questions about the content of peer reviews across different domains.
+Since we know the individual recommendation of each reviewer for Royal Society Open journals, one example of the insights that open reviews provide is how often reviewers agree.
+For the 1961 papers where the reviews were published, all reviewers agreed on the recommendation for 829 articles (42.27\% of the time).
+For 41.71\% of the manuscripts the maximum deviation was one category (e.g., minor and major revisions), for 14.38\% of the manuscripts the maximum deviation was two categories (e.g., accept and major revision), and for 1.63\% of the manuscripts the maximum deviation was three categories (i.e., accept and reject).
+There were 3 articles where researchers received all four possible recommendations (accept, minor revisions, major revisions, reject) from at least four different reviewers.
+We hope the dataset we share with this manuscript will allow other meta-scientists to examine additional questions about the peer review process.
+
+Reviewers might have different reasons to sign or not sign their reviews.
+They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission.
+Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
+Finally, reviewers might fear backlash from authors who receive their negative reviews.
 Our data supports the idea that reviewers' decisions to sign are related to their recommendation across a wide range of scientific disciplines.
+Due to the correlational nature of the data, this relationship could emerge because reviewers who are on average more likely to sign also give more positive recommendations, reviewers are more likely to sign more positive recommendations, or both these effects could be true at the same time.
 Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some reviewers are more likely to sign if their recommendation is more positive.
@@
 
-\hypertarget{competing-interests}{%
-\section{Competing interests}\label{competing-interests}}
+\hypertarget{conflict-of-interest-statement}{%
+\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
 
-The authors report no conflicts of interest.
+The authors report no conflict of interest.
+
+\hypertarget{funding}{%
+\section{Funding}\label{funding}}
+
+This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research.
+
+\hypertarget{orcid-ids}{%
+\subsection{ORCID iD's}\label{orcid-ids}}
+
+Daniel Lakens \includegraphics{orcid.png} \url{https://orcid.org/0000-0002-0247-239X}
 

### 2020-05-30 textmining_peerj.R

@@ -4,12 +4,14 @@ library(pdftools)
 library(tm)
 library(stringr)
 library(here)
+library(lubridate)
 
 here()
 
 #########################################variables used to create the dataframe#################################
 df_link <- c()
 df_section <- c()
+df_year <- c()
 df_days <- c()
 df_version <- c()
 df_recommendation <- c()
@@ -112,7 +114,6 @@ for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 Peer
         recommendation_count = recommendation_count +1
       }
       
-      
       if (lines[i] == paste("label_version_", version_count, sep="")){
         version_count <- version_count +1
         total_version <- total_version +1
@@ -182,12 +183,14 @@ for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 Peer
     
     days <- as.numeric(dates[1])-as.numeric(dates[2])
     
+    pub_year <- year(as.Date(timelapse[1], "%b %d %Y"))
     ############################################Creating df vectors################################################
     
     for (i in 1:length(word_count+1)){
       if (author_count > 1){
         df_link <- append(df_link, link)
         df_section <- append(df_section, section)
+        df_year <- append(df_year, pub_year)
         df_days <- append(df_days, days)
         df_version <- append(df_version, version[i])
         df_recommendation <- append(df_recommendation, recommendation[i])
@@ -199,10 +202,10 @@ for (r in 1:7930){ #starting the loop to create the dataframe from the 6800 Peer
     
   } else {
     closed_reviews = closed_reviews + 1
-  } # end open/closed acces loop
+  } # end open/closed access loop
 } # end all_loop
 
 #################################Creating dataframe and csv file#################################################
-df <- data.frame(df_link, df_section, df_days, df_version, df_recommendation, df_word_count, df_anonymous, df_reviewer_name)
+df <- data.frame(df_link, df_section, df_year, df_days, df_version, df_recommendation, df_word_count, df_anonymous, df_reviewer_name)
 
 saveRDS(df, file = "peerj_data.rds")             #used to create the rds file

### 2020-05-30 textmining_peerj_cs.R

@@ -4,12 +4,14 @@ library(pdftools)
 library(tm)
 library(stringr)
 library(here)
+library(lubridate)
 
 here()
 
 #########################################variables used to create the dataframe#################################
 df_link <- c()
 df_section <- c()
+df_year <- c()
 df_days <- c()
 df_version <- c()
 df_recommendation <- c()
@@ -182,12 +184,15 @@ for (r in 1:225){ #starting the loop to create the dataframe from the 6800 PeerJ
     
     days <- as.numeric(dates[1])-as.numeric(dates[2])
     
+    pub_year <- year(as.Date(timelapse[1], "%b %d %Y"))
+    
     ############################################Creating df vectors################################################
     
     for (i in 1:length(word_count+1)){
       if (author_count > 1){
         df_link <- append(df_link, link)
         df_section <- append(df_section, section)
+        df_year <- append(df_year, pub_year)
         df_days <- append(df_days, days)
         df_version <- append(df_version, version[i])
         df_recommendation <- append(df_recommendation, recommendation[i])
@@ -203,6 +208,6 @@ for (r in 1:225){ #starting the loop to create the dataframe from the 6800 PeerJ
 } # end all_loop
 
 #################################Creating dataframe and csv file#################################################
-df <- data.frame(df_link, df_section, df_days, df_version, df_recommendation, df_word_count, df_anonymous, df_reviewer_name)
+df <- data.frame(df_link, df_section, df_year, df_days, df_version, df_recommendation, df_word_count, df_anonymous, df_reviewer_name)
 
 saveRDS(df, file = "peerj_cs_data.rds")             #used to create the rds file

### 2020-06-04 manuscript/revision_2/open_peer_review.Rmd
accepted version of the manuscript

@@
 author_note: |
- Submitted to Meta-Psychology.
-Click here to follow the fully transparent editorial process of this submission.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.
+ Accepted for publication at Meta-Psychology.
 This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All data underlying this reproducible manuscript are available at https://osf.io/9526a/
+All data underlying this reproducible manuscript are available at https://osf.io/9526a/.
+A Code Ocean capsule that computationally reproduces this manuscript is available at https://codeocean.com/capsule/6067104.
 abstract: |
@@
 The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations.
-We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
+We also share all 23649 text-mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
 
@@
 We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
-For Royal Society Open journals reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
+For Royal Society Open journals reviewers make a recommendation, which may be to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'.
 Because PeerJ and Royal Society Open journals only share reviews for published articles there are few 'reject' recommendations for Royal Society Open journals and no 'reject' recommendations by editors among PeerJ reviews.
@@
 
-Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of 'accept', 'minor revisions', 'major revisions', or 'reject'.
+Analyzing the reviews at Royal Society Open journals provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of 'accept', 'minor revisions', 'major revisions', or 'reject'.
 We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}).
@@
 
-Both PeerJ as Royal Society Open journals publish articles in a wide range of disciplines, including astronomy, biochemistry, chemistry, computer science, earth science, ecology, engineering, genomics, mathematics, evolutionary biology, paleontology, physics, psychology, and zoological science.
-The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available for Royal Society Open journals.
+Both PeerJ and Royal Society Open journals publish articles in a wide range of disciplines.
+The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available from meta-data or the bibliographic record for Royal Society Open journals.
 
-```{r, echo=FALSE, results='asis'}
-cat("\\onecolumn")
-```
+\onecolumn
 
@@
 
-```{r, echo=FALSE, results='asis'}
-cat("\\twocolumn")
-```
+\twocolumn
 
 To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section).
-We see the general pattern holds across all fields.
+We see that the general pattern holds across all fields.
 In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned.
@@
 Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals.
-It seems that in the early years that these journals existed, more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews.
+It seems that in the early years of their existence more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews.
 We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts.
@@
 As a consequence, we have analyzed a biased sample of the literature.
-Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000).
+Few scientific journals make peer reviews available for all submitted articles (two notable exceptions are Meta-Psychology and F1000).
 Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal.
@@
 They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission.
-Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
+Reviewers might not want to reveal that their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest.
 Finally, reviewers might fear backlash from authors who receive their negative reviews.
@@
 
-## ORCID iD
+## ORCID ID
 

### 2020-06-04 manuscript/revision_2/open_peer_review.tex
accepted version of the manuscript

@@
 \textsuperscript{1} Eindhoven University of Technology, The Netherlands}
-\authornote{Submitted to Meta-Psychology.
-Click here to follow the fully transparent editorial process of this submission.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.
+\authornote{Accepted for publication at Meta-Psychology.
 This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All data underlying this reproducible manuscript are available at https://osf.io/9526a/
+All data underlying this reproducible manuscript are available at https://osf.io/9526a/.
+A Code Ocean capsule that computationally reproduces this manuscript is available at https://codeocean.com/capsule/6067104.
 
@@
 The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations.
-We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
+We also share all 23649 text-mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
 }
@@
 A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus.
-All available reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2019; R Core Team, 2013).
+All available reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2020; R Core Team, 2013).
 These text files were mined for recommendations, reviewer names, submission and acceptance dates, and the review content, using the stringr package in R (Wickham, 2019).
@@
 We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews.
-For Royal Society Open journals reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
+For Royal Society Open journals reviewers make a recommendation, which may be to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}.
 Because PeerJ and Royal Society Open journals only share reviews for published articles there are few \enquote{reject} recommendations for Royal Society Open journals and no \enquote{reject} recommendations by editors among PeerJ reviews.
@@
 
-Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.
+Analyzing the reviews at Royal Society Open journals provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}.
 We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}).
@@
 
-Both PeerJ as Royal Society Open journals publish articles in a wide range of disciplines, including astronomy, biochemistry, chemistry, computer science, earth science, ecology, engineering, genomics, mathematics, evolutionary biology, paleontology, physics, psychology, and zoological science.
-The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available for Royal Society Open journals.
+Both PeerJ and Royal Society Open journals publish articles in a wide range of disciplines.
+The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available from meta-data or the bibliographic record for Royal Society Open journals.
 
@@
 To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section).
-We see the general pattern holds across all fields.
+We see that the general pattern holds across all fields.
 In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned.
@@
 \hypertarget{author-contributions}{%
-\section{Author Contributions}\label{author-contributions}}
+\subsection{Author Contributions}\label{author-contributions}}
 
@@
 \hypertarget{conflict-of-interest-statement}{%
-\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
+\subsection{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
 
@@
 \hypertarget{funding}{%
-\section{Funding}\label{funding}}
+\subsection{Funding}\label{funding}}
 
@@
 
-\hypertarget{orcid-ids}{%
-\subsection{ORCID iD's}\label{orcid-ids}}
+\hypertarget{orcid-id}{%
+\subsection{ORCID ID}\label{orcid-id}}
 
@@
 (2018).
-Signing Critical Peer Reviews \& the Fear of Retaliation: What Should We Do?
+Signing critical peer reviews and the fear of retaliation: What should we do?
 \textbar{} Absolutely Maybe.
@@
 \leavevmode\hypertarget{ref-ooms_pdftools_2019}{}%
-Ooms, J. (2019). \emph{Pdftools: Text extraction, rendering and converting of PDF documents}.
+Ooms, J. (2020). \emph{Pdftools: Text extraction, rendering and converting of pdf documents}. Retrieved from \url{https://CRAN.R-project.org/package=pdftools}
 
@@
 \leavevmode\hypertarget{ref-wickham_stringr_2019}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}.
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
